### 2023-07-25 SI.tex
Initial commit

% ****** Start of file apssamp.tex ******
%
%   This file is part of the APS files in the REVTeX 4.2 distribution.
%   Version 4.2a of REVTeX, December 2014
%
%   Copyright (c) 2014 The American Physical Society.
%
%   See the REVTeX 4 README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.2
%
% See the REVTeX 4 README file
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex apssamp.tex
%  2)  bibtex apssamp
%  3)  latex apssamp.tex
%  4)  latex apssamp.tex
%
\documentclass[%
 reprint,
superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-2}
\usepackage[dvipsnames]{xcolor}
\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines
\newcommand{\ket}[1]{|#1\rangle}
\newcommand{\vvv}[1]{\textcolor{blue}{#1}}
%\usepackage[showframe,%Uncomment any one of the following lines to test 
%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
%%text={7in,10in},centering,
%%margin=1.5in,
%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
%%height=10in,a5paper,hmargin={3cm,0.8in},
%]{geometry}
\begin{document}

\preprint{APS/123-QED}

\title{Supplementary materials for "On readout and initialisation fidelity by finite demolition single shot readout"}% Force line breaks with \\
%\thanks{A footnote to the article title}%

\author{Majid Zahedian}
 \affiliation{3rd physical institute University of Stuttgart, Germany}
  \affiliation{\vvv{@Majid, please fill here} FAU, Erlangen, Germany}%Lines b%Lines break automatically or can be forced with \\

\author{Max Keller}
 \affiliation{3rd physical institute University of Stuttgart, Germany}%Lines break automatically or can be forced with \\

\author{Minsik Kwon}
 \affiliation{3rd physical institute University of Stuttgart, Germany}%Lines break 
  \affiliation{Max Planck Institute for solid state physics, Stuttgart, Germany}%Lines break automatically or can be forced with \\

 \author{Javid Javadzade}
 \affiliation{3rd physical institute University of Stuttgart, Germany}%Lines break automatically or can be forced with \\

\author{Jonas Meinel}
 \affiliation{3rd physical institute University of Stuttgart, Germany}%Lines break 
  \affiliation{Max Planck Institute for solid state physics, Stuttgart, Germany}%Lines break automatically or can be forced with \\

\author{Vadim Vorobyov}
 \affiliation{3rd physical institute University of Stuttgart, Germany}%Lines break automatically or can be forced 
  \email{v.vorobyov@pi3.uni-stuttgart.de}
% with \\

\author{Jörg Wrachtrup}
 \affiliation{3rd physical institute University of Stuttgart, Germany}%Lines break 
 \affiliation{Max Planck Institute for solid state physics, Stuttgart, Germany}%Lines break 
 %automatically or can be forced with \\ Third institution, the second for Charlie Author

%\date{\today}% It is always \today, today,
             %  but any date may be explicitly specified

%\keywords{Suggested keywords}%Use showkeys class option if keyword
                              %display desired
\maketitle
%\tableofcontents

\section{Data for deriving the charge state rates and photon counts data}
\label{app:charge}
\vvv{TO SI}
gamma and lambda
\section{Calculation of fidelities and preparation times for charge state}
\label{app:charge_results}
\vvv{TO SI}
\vvv{all pictures from @Majid, for various fidelities.}
\section{Calibration of nuclear spin data}
\label{app:nuclear}
\vvv{all pictures from @Majid, for various fidelities.}
\vvv{TO SI}
nuclear spin counts, gamma
%\section{Filter function calculations}
%pass
\bibliography{references}% Produces the bibliography via BibTeX.

% The \nocite command causes all entries in a bibliography to be printed out
% whether or not they are actually referenced in the text. This is appropriate
% for the sample file to show the different styles of references, but authors
% most likely will not want to use it.
%\nocite{*}
\end{document}
%
% ****** End of file apssamp.tex ******

### 2023-07-25 article.tex
Initial commit

% ****** Start of file apssamp.tex ******
%
%   This file is part of the APS files in the REVTeX 4.2 distribution.
%   Version 4.2a of REVTeX, December 2014
%
%   Copyright (c) 2014 The American Physical Society.
%
%   See the REVTeX 4 README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.2
%
% See the REVTeX 4 README file
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex apssamp.tex
%  2)  bibtex apssamp
%  3)  latex apssamp.tex
%  4)  latex apssamp.tex
%
\documentclass[%
 reprint,
superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-2}
\usepackage{physics}
\usepackage[dvipsnames]{xcolor}
\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines
\newcommand{\vvv}[1]{\textcolor{blue}{#1}}
%\usepackage[showframe,%Uncomment any one of the following lines to test 
%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
%%text={7in,10in},centering,
%%margin=1.5in,
%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
%%height=10in,a5paper,hmargin={3cm,0.8in},
%]{geometry}
\begin{document}

\preprint{APS/123-QED}

\title{Blueprint for nuclear spin characterization in color centers}% Force line breaks with \\
%\thanks{A footnote to the article title}%

\author{Majid Zahedian}
 \affiliation{3rd physical institute University of Stuttgart, Germany}
  \affiliation{Max Planck School of Photonics, Germany}%Lines b%Lines break automatically or can be forced with \\

\author{Vadim Vorobyov}
\email[]{v.vorobyov@pi3.uni-stuttgart.de}
 \affiliation{3rd physical institute University of Stuttgart, Germany}  
% with \\

\author{J\"org Wrachtrup}
 \affiliation{3rd physical institute University of Stuttgart, Germany}%Lines break 
 \affiliation{Max Planck Institute for solid state physics, Stuttgart, Germany}%Lines break 
 %automatically or can be forced with \\ Third institution, the second for Charlie Author

\date{\today}% It is always \today, today,
             %  but any date may be explicitly specified

\begin{abstract}
Color centers are one of the promising platform for implementing quantum applications, using the nuclear spins around the electron spin as qubits with relatively long coherence time. However, characterizing each nuclear spin is quite cumbersome as the characterization protocol may differ depending on the strength of the hyperfine coupling. Here, we present a more straight forward method to obtain hyperfine interaction among nuclear spins and the electron spin. This method can be used for a variety of platform including group IV defects in diamond or Silicon vacancy in Silicon Carbide.
\end{abstract}

%\keywords{Suggested keywords}%Use showkeys class option if keyword
                              %display desired
\maketitle
%\tableofcontents
\section{Introduction and background}
Optically active defects in solids, color centers, has been applied for realizing different quantum applications \cite{awschalom2018quantum}, such as a quantum network \cite{pompili2021realization}, quantum sensing \cite{degen2017quantum}, and quantum register \cite{bradley2019ten}. Each center contains an electron spin that can be controlled directly with microwaves and optics and many nuclear spins that can be manipulated through the electron spin. Characterizing nuclear spins is necessary for enlarging the quantum register and precise description of the electron spin dynamics. Traditionally, nuclear spin characterization is done with Opticall Detected Magnetic Resonance (ODMR) (ref to Phillip Neumann's works), however the spectroscopic resolution is limited to the $T_2^\ast$ of the electron spin. Hence, some sequence is needed to increase the resolution. People have used Hahn Echo sequence to refocus the electron spin and enhance the coherence time of the electron spin \cite{childress2006coherent}. But this method only works for defects with a specific nuclear spins configuration. Depending on the applied protocol for nuclear spins characterization, the number of accessible nuclear spin can increase. Electron Spin Echo Envelop Modulation (ESEEM) types of sequences allow us to access the highest number of nuclear spins since the spectroscopy resolution is limited to the longitudinal relaxation time (T1) of the system (see fig. \ref{fig:1}). 
\begin{figure*}%[htbp]
	\begin{center}
		\includegraphics[width=0.7\textwidth]{pict/fig1.png}
		\caption{a. nuclear spins that can be characterized using each sequence. b. number of nuclear spins as a function of distance for the defect. The dashed line shows having T1 = 1s limitation, how many nuclear spins are accessible in diamond. }
		\label{fig:1}
	\end{center}
\end{figure*}

%%%%%%%%%%%%%%%%%%%================= %THEORY
\section{Methods}
\label{sec:theory}
%%%%%%%%%%%%%%%Í%%%%=================
In this section, we provide the theoretical formulas for. In a central electron spin with the electron spin $\boldmath{S}$, we only apply pulses resonant with two of the electron spin sublevels, denoted as $m_s=s_0$ and $m_s = s_1$. These two spin sublevels are separated, due to Zeeman effect or zero field splitting, and form an artificial two-level system with energy splitting of $\omega_a$. Now, we add spin $\frac{1}{2}$nuclear spins to the system (for considering P1 centers, one has to add nuclear quadrupole to the presented Hamiltonian.). The Hamiltonian of a central electron spins system surrounded by nuclear spins in the secular approximation in the rotating frame of the applied microwave $\omega_{mw}$ (considering rotating wave approximation) can be written as:
\begin{align}
	H = \Delta S_z + \sum_k (\omega_L^{(k)}  + A_{zz}^{(k)} S_z) I_z^{(k)} + A_{zx}^{(k)} S_z I_x^{(k)}
	\label{eq:H}
\end{align}
Where $\Delta = \omega_a - \omega_{mw}$ is the detuning, $\omega_L^{(k)} =\gamma_n^{(k)} B$ is nuclear Rabi frequency with $\gamma_n^{(k)}$ nuclear spin gyromagnetic ratio and $B$ external magnetic field, $A_{zz}, A_{zx}$ parallel and perpendicular secular component of hyperfine tensor. This Hamiltonian results that depending on the electron spin sublevel $s_i$ ($i=0,1$), the nuclear spin rotate with the resonance frequency of $\omega_i = \sqrt{(\omega_L + s_i A_{zz})^2+ (s_i A_{zx})^2}$, $i=0,1$ along the axes $\vec{n}_i =(\frac{s_i A_{zx}}{\omega_i}, 0, \frac{\omega_L + s_i A_{zz}} {\omega_i})$. It is assumed that the pulse duration $t_p$ are short enough ($\omega_L t_p \ll 1$) that the nuclear spin dynamics during this time is negligible. The most simplest characterization sequence is Ramsey. \\ The Ramsey signal can be obtained as follows:
\begin{gather}
	\expval{\sigma_z}_{Ram} = \cos(\Delta \tau) \prod_{k=1}^{n} \Big[ \cos(\frac{\omega_0 \tau}{2}) \cos(\frac{\omega_1 \tau}{2})+ \notag \\
	(\vec{n_0}\cdot \vec{n_1})\sin(\frac{\omega_0 \tau}{2}) \sin(\frac{\omega_1 \tau}{2}) \Big]^{(k)}
	\textcolor{gray}{e^{-\frac{\tau}{T_2^\ast}}}
\end{gather} 
We do not take any relaxation process into account and the gray exponential decay is put by hand to remember the relaxation time scale. Ramsey signal decay with electron spin $T_2^\ast$, so it can be used to observe the core of the defect. Ramsey sequence is sensitive to detuning since the electron spin is not refocused, however it is possible to sense nuclear spins with vanishing perpendicular hyperfine coupling.\\
\begin{figure}%[htbp]
	\begin{center}
		\includegraphics[width=0.9\columnwidth]{pict/seqs.png}
		\caption{Pulse sequences a. Ramsey b. Hahn Echo c. Dynamical Decoupling d. DDESEEM}
		\label{fig:seqs}
	\end{center}
\end{figure} 
To enhance the relaxation time and have access to more nuclei, one can add a $\pi$ pulse in between the Ramsey sequence and create Hahn-echo sequence and obtain the following signal:
\begin{gather}
	\expval{\sigma_z}_{HE} = \prod_{j=1}^n \Big[1 - 2 k^2 
	\sin^2(\frac{\omega_0 \tau}{2}) \sin^2(\frac{\omega_1 \tau}{2})\Big]^{(j)} \textcolor{gray}{ e^{-\frac{2\tau}{T_2}}}
\end{gather}
Where $k = \frac{(s_1-s_0)\omega_L A_{zx}}{\omega_0 \omega_1}$ is the modulation amplitude of each nuclear spin. We know that without any nuclear spin, Hahn Echo sequence creates the electron spin echo signal with the envelope of exponential decay with $T_2^{HE}$. However in the presence of nuclear spins, the electron spin echo envelope will be modulated due to interaction with nuclei. Hence, this sequence also called Electron Spin Echo Envelope Modulation or shortly ESEEM. Even though the coherence time is increased, distinguishing the effect of different nuclear spins in the total signal is very complicated. Hahn Echo sequence can be used for defects that contain a few strongly coupled nuclei. In order to differentiate the resonance frequency of each nuclear spin or make the oscillation sharper, one has to add more $\pi$ pulses and for the so-called Dynamical Decoupling sequence:
Finally, the signal for dynamical decoupling is obtained:
\begin{gather}
	\expval{\sigma_z}_{DD} =
	\prod_{j=1}^n \Big[1- 2 k^2  
	\sin^2(\frac{\omega_0 \tau}{2}) \sin^2(\frac{\omega_1 \tau}{2}) \frac{\sin^2(\frac{N}{2} \theta)}{\cos^2(\frac{1}{2}\theta)}  \Big]^{(j)} \textcolor{gray}{ e^{-\frac{2N\tau}{T_2(N)}}} 
\end{gather}
Where
\begin{gather}
	\theta=  \arccos\Big[\cos(\omega_0 \tau) \cos(\omega_1 \tau)- \vec{n}_0 \cdot \vec{n}_1 sin(\omega_0 \tau) \sin(\omega_1 \tau) \Big]
\end{gather}
$\vec{n}_0 \cdot \vec{n}_1 = \frac{\omega_L^2+(s_0+s_1)A_{zz}+s_0 s_1 (A_{zz}^2+A_{zx}^2)}{\omega_0 \omega_1}$ and $N$ is the number of $\pi$ pulses that must be an even. Each nuclear 
If the magnetic field is high or all nuclear spins are weakly coupled such that $\omega_L \gg A_{zz}, A_{zx}$, the multiplication rule can be approximated by a summation rule, which makes the higher order resonance disappear:
\begin{gather}
	\expval{\sigma_z}_{DD} \approx 1 -2
	\sum_{j=1}^n \Big[ k^2 	 \sin^2(\frac{\omega_0 \tau}{2}) \sin^2(\frac{\omega_1 \tau}{2}) \frac{\sin^2(\frac{N}{2} \theta)}{\cos^2(\frac{1}{2}\theta)}  \Big]^{(j)} \textcolor{gray}{ e^{-\frac{2N\tau}{T_2(N)}}} 
\end{gather}
The parallel component of the hyperfine interaction can be obtained from the resonance time of each nuclear spin:
\begin{gather}
	\tau_p \approx  \frac{(2p+1) \pi}{\omega_0 + \omega_1} \approx \frac{(2p+1)\pi}{2\omega_L(1+\frac{s_0+s_1}{2} \frac{A_{zz}}{\omega_L}+ \frac{s_0^2+s_1^2}{4}\frac{A_{zx}^2}{\omega_L^2})}
\end{gather}
The perpendicular part of hyperfine interaction can be obtained from a fit to the Lorentzian dip with the width of $\frac{(s_1-s_0)\omega_L A_{zx}}{(2p+1)\pi\omega_0 \omega_1}$ or varying the number of pulses and fitting the minima position to the formula $\expval{\sigma_z}_{DD}^{(k)} \approx 1- 2 \sin^2\big(\frac{N}{2}\frac{(s_1-s_0)\omega_L A_{zx}}{\omega_0 \omega_1}\big) $. Although Dynamical Decoupling (DD) sequence is well understood and used to characterize nuclear spins, it is not applicable for any system. First, DD only works for defects with high magnetic field and low hyperfine coupling ($\omega_L \gg A_{zz}, A_{zx}$). Second, the signal is limited to electron spin $T_2$, which is difficult to make it equal to $T_1$. Third, the signal analysis is rather complicated and time-consuming. (Maybe AI solves this problem in the future?) one has to collect enough data to make sure no two nuclear spin overlap in the signal. Forth, this sequence does not work for spin one half system, e.g., group IV defect in diamond, since parallel component of hyperfine coupling cancels their effect in the resonance time up to the first and second order. Hence, the resonance time depends on the second order of perpendicular component. In this work, we take 23 nuclear spin characterized in paper \cite{abobeih2019atomic} as a realistic case. 
\begin{figure*}%[htbp]
	\begin{center}
		\includegraphics[width=0.8\textwidth]{pict/fig3.png}
		\caption{a. DD for NV in diamond b. DD for group IV defect in diamond }
		\label{fig:3}
	\end{center}
\end{figure*}
Fig \ref{fig:3} compares DD signal for the same nuclear spin register but different defects in diamond. We present a handwavy definition for the sensitivity of a sequence to the variation of hyperfine coupling. First, we consider the case of NV center in diamond. By knowing the width of a dip $\delta \tau = \frac{A_{zx}}{\omega_L^2}$  and taking the derivative of the resonance time, we define the sensitivity of longitudinal hyperfine coupling as follows:
\begin{gather}
	\delta A_{zz} = \frac{\delta \tau}{\abs{\frac{\partial \tau_k}{\partial A_{zz}}}} = \frac{2}{\tau_k} \frac{A_{zx}}{\omega_L} \ge \frac{4}{T_2^{HE}} \frac{A_{zx}}{\omega_L}
\end{gather}
If we assume the typical values of $T_2^{HE} = 100 $ $\mu$s and $\omega_L=500 $ kHz, a weakly coupled nuclear spin $A_{zx}=5$ kHz can be distinguished from another weakly coupled nuclear spin with $\delta A_{zz} = 400$ Hz. On the other hand, for group IV detects in diamond, The resonance times is sensitive to the second order of $A_{zx}$ and no sensitivity to $A_{zz}$. Hence, even at large $\tau$ the nuclear spin not separated well. We define the sensitivity for the spin one half system as follows:
\begin{gather}
	\delta A_{zx} = \frac{\delta \tau}{\abs{\frac{\partial \tau_k}{\partial A_{zx}}}} = \frac{4}{\tau_k} \ge \frac{8}{T_2^{HE}}
\end{gather}
Assuming the typical values of $T_2^{HE} = 100 $ $\mu$s, a nuclear spin can be distinguished from another one if their transverse hyperfine coupling is separated by $\delta A_{zx} = 80$ kHz, which is quite inaccurate.\\

We want to make a sequence that is limited by T1 instead of T2. The idea of 5-pulse ESEEM \cite{kasumaj20085} is that to create an entanglement (Hahn-echo) before the free evolution (Ramsey). In other words, change the initial density matrix for the Ramsey sequence from such that entanglement already exist in the electron polarization terms of the density matrix. Fig \ref{fig:seqs} shows the sequence, which can be interpreted as two Hahn Echos that are separated by a long free evolution $T\gg T_2^\ast$ such that the coherence of the electron spin vanishes. The analytical formula to this sequence is provided in the appendix \ref{app:5pESEEM}. During the free evolution time, each nuclear spins oscillates with either of two resonance frequencies obtained from eq. \ref{eq:H}.
\begin{figure*}%[htbp]
	\begin{center}
		\includegraphics[width=0.9\textwidth]{pict/fig4.png}
		\caption{a. FFT of ESEEM signal b. a zoom into weakly coupled nuclear spins c. Enhancing weakly coupled nuclear spins by having 72 pulses in each entangling period. $\tau$ is set to the Larmor bright spot.}
		\label{fig:4}
	\end{center}
\end{figure*}
Fig \ref{fig:4} shows the furrier transform of the signal. Zooming into area close to the Larmor frequency reveals the weakly coupled nuclei. Each nuclear spins have two peaks in the spectrum. Expanding the resonance frequencies up to first order with respect to hyperfine coupling results that the weakly coupled nuclei keep their order as they go further away from the nuclei. This fact makes their characterization rather straight forward. To observe the weakly coupled nuclei more pronouncedly, one can use DDESEEM sequence by adding more $\pi$ pulses in the entangling periods. To distinguish other nuclei, extra measurements is required. One method is to use two dimensional hyperfine correlation spectroscopy (2D Hyscore)  \ref{vorobyov2022addressing}. However, this method is rather time-consuming as two time variables has to be swept. We suggest sweeping $\tau$ parameter and keep the track of frequency amplitude as a function of $\tau$. Two frequencies that belong to the same nuclear are correlated because the modulation depth oscillates with blind spot terms of both frequencies $\sin^2(\frac{\omega_0 \tau}{2}) \sin^2(\frac{\omega_1 \tau}{2})$. Fig. \ref{fig:5} shows two frequencies goes to bright and blind spots simultaneously. Hence, taking two dimensional correlation of the spectrum, one can deduce which two frequencies are correlated and belong to the same nuclear. \\

Here, we try to simulate the realistic situation. First, the electron spin state is projected to 0 and 1 with a binomial distribution, the probability determined by the theoretical signal. Then, we assume the bright (dark) state emits 3 (0.1) photons on average with a Poissonian distribution. We repeat the measurement at each point for 10000 times to reduce classical noise.\\
How many nuclear spin is identifiable with this method? It depends on the duration of free evolution time and the choice of inter-pulse timing $\tau$.

\begin{figure*}%[htbp]
	\begin{center}
		\includegraphics[width=0.9\textwidth]{pict/fig5.png}
		\caption{a. FFT of ESEEM signal for $\tau$ from 10 $\mu$s to 500 $\mu$s with the step of 10 $\mu$s b. 2D correlation of each frequency for different $\tau$.}
		\label{fig:5}
	\end{center}
\end{figure*}

\section{Conclusion}
\label{sec:discussion}
%\subsection{Advanced filters}
Here is the concise conclusion @Vadim

\section*{Acknowledgments}
We acknowledge financial support by European Union's Horizon 2020 research and innovation program ASTERIQS under grant No. 820394, European Research Council advanced grant No. 742610, SMel, Federal Ministry of Education and Research (BMBF) project MiLiQuant and Quamapolis, the DFG (FOR 2724), the Max Planck Society, and the Volkswagentiftung. M.Z. thanks Max Planck School of Photonics for financial support.

%%%%%%%%%%%%%=========
\appendix
%%%%%%%%%%%%%=========
\section{5pESEEM formula}
\label{app:5pESEEM}
Here we need to define a few unitary operators/ The evolution in the first Hahn-echo is given by V operators, the middle free evolution is given by F operators, and the second Hahn-echo is given by W operators:
\begin{gather}
	V_0 = U_0 (\tau_1) U_1 (\tau_1),\,\,  V_1 = U_1 (\tau_1) U_0 (\tau_1) \\
	F_0 = U_0 (T), \,\, F_1 = U_1 (T) U_0 \\
	W_0 = U_0 (\tau_2) U_1 (\tau_2), \,\, W_1 = U_1 (\tau_2) U_0 (\tau_2)
\end{gather}
The signal can be obtained from four different types of trajectories that the electron spin can take. We use the fact that multiplication of unitary operators is also a unitary operator and every unitary in spin one half space can be written in terms of a rotation angle, axis, and Pauli Matrices $\vec{\sigma}$. We denote the unitary operator $U = \exp(-i \theta_U \hat{n}_U\cdot\vec{\sigma}) = M\cos(\theta_U) \mathbf{I}- i \sin(\theta_U) \hat{n}_U\cdot\vec{\sigma}$. The signal for 5-pulse ESEEM can be obtained as follows:
\begin{gather}
		\expval{\sigma_z}_{5p} =\frac{1}{4}\Big( \prod_{j=1}^n [\cos(\theta_{W_1 F_1 V_0 V_1^\dagger F_1^\dagger W_0^\dagger})]^{(j)}  \notag \\
		-\prod_{j=1}^n [\cos(\theta_{W_1 F_1 V_1 V_0^\dagger F_1^\dagger W_0^\dagger})]^{(j)}  \notag \\
		+ \prod_{j=1}^n [\cos(\theta_{W_1 F_0 V_0 V_1^\dagger F_0^\dagger W_0^\dagger})]^{(j)}  \notag \\
		-\prod_{j=1}^n [\cos(\theta_{W_1 F_0 V_1 V_0^\dagger F_0^\dagger W_0^\dagger})]^{(j)} \Big) \textcolor{gray}{e^{-\frac{2\tau_1+2\tau_2}{T_2}- \frac{T}{T_1}}}
\end{gather}
Multiplying the matrices and finding the rotation angles gives the expectation value of $\sigma_z$ for 5pESEEM sequence as it can be found in this article \cite{kasumaj20085}:
\begin{gather}
	\expval{\sigma_z}_{5p} = \frac{1}{4}\Big( \prod_{j=1}^n E_{\alpha_+}^{(j)} - \prod_{j=1}^n E_{\alpha_-}^{(j)} + \prod_{j=1}^n E_{\beta_+}^{(j)}- \prod_{j=1}^n E_{\beta_-}^{(j)}\Big)
\end{gather}
Where each term can be calculated as follows:
\small   
\begin{gather} 
	E_{\alpha_\pm}^{(k)} = E_{2p}(\tau_1) E_{2p}(\tau_2) \mp B \Big(-4k^2C_\alpha \notag \\
	+4k\cos^4(\eta) \cos(\omega_\alpha T + \phi_{\alpha_+} +\phi_{\beta_+}) 
	+2 k^2 \cos(\phi_{\beta_-}) \cos(\omega_\alpha T+\phi_{\alpha_+}) \notag \\
	+ 4k \sin^4(\eta) \cos(\omega_\alpha T +\phi_{\alpha_+} -\phi_{\beta_+} )\Big)
	\label{eq:eseem}
\end{gather}
\normalsize
$ E_{2p} $ is 2-pulse ESEEM sequence signal:
\begin{gather}
	E_{2p}(t)  = (1 - \frac{k}{2}) + \frac{k}{2} \Big(\cos(\omega_\alpha t)+\cos(\omega_\beta t) \notag \\
	-\frac{1}{2} \cos(\omega_{-}t)  -\frac{1}{2} \cos(\omega_{+}t)   \Big)
\end{gather}
With $\omega_{\pm} = \omega_\alpha \pm \omega_\beta$,  B is the blind spot term and $C_\alpha$ is a constant term:
\begin{gather}
	B = \sin(\frac{\omega_\alpha \tau_1}{2}) \sin(\frac{\omega_\alpha \tau_2}{2}) \sin(\frac{\omega_\beta \tau_1}{2}) \sin(\frac{\omega_\beta \tau_2}{2})
	\label{eq:BS}\\
	C_\alpha =\cos(\frac{\omega_\alpha \tau_1}{2}) \cos(\frac{\omega_\alpha \tau_2}{2}) \sin(\frac{\omega_\beta \tau_1}{2}) \sin(\frac{\omega_\beta \tau_2}{2}) \label{eq:Cterms}
\end{gather}
The resonance frequencies are $\omega_{\alpha(\beta)} = \sqrt{(\omega_L +s_{0(1)} A_{zz} )^2 +(s_{0(1)} A_{zx})^2}$. The quantization axis of nuclear spins is tilted by $\eta_{\alpha(\beta)} = \arctan(\frac{s_{0(1)}A_{zx}}{\omega_L+ s_{0(1)}A_{zz}})$, which gives the parameter $\eta=\frac{\eta_\alpha - \eta_\beta}{2}$. The modulation depth of each nuclear spin is $k=\sin^2(2\eta)=(\frac{(s_1-s_0)\omega_L A_{zx}}{\omega_\alpha \omega_\beta})^2$, the phase shifts are $\phi_{\alpha_\pm} = \frac{\omega_\alpha (\tau_1 \pm \tau_2)}{2}$ and $\phi_{\beta_\pm} = \frac{\omega_\beta (\tau_1 \pm \tau_2)}{2}$. The two expression for the $\beta$ pathways can be obtained by exchanging $\alpha$ and $\beta$ in equation \ref{eq:eseem}, \ref{eq:BS}, and \ref{eq:Cterms}.\\

As we have shown, the signal from the register comes from the multiplication of signals from individual nuclear spins. Hence, if the modulation depth is not low (low magnetic field condition), the second or higher order frequencies will appear in the spectrum. So, the product rule lead to the creation of inter-nuclear peaks at multi-quantum frequencies that can be sums or subtraction of single quantum frequencies of various nuclei. Nevertheless, the multiple quantum resonance peaks are informative for the electron spin one half system because one can deduce that two peaks that are added or subtracted belong to the same electron spin manifold; Hence it is possible to get the relative phase of nuclei. Another consequence of the product rule is the cross-suppression effect, which means the presence of strongly coupled nuclei suppress the amplitude of weakly coupled nuclei while weakly coupled ones do not suppress the amplitude of strongly coupled nuclei \cite{stoll2005peak}. However, if we assume the Larmor frequency is relatively high or the modulation depth is low, both of these effect will vanish as the product rule can be approximated by a summation rule:\\
\begin{gather}
	E_\alpha = \prod_{j=1}^n E_{\alpha_+}^{(j)} - \prod_{j=1}^n E_{\alpha_-}^{(j)}  \notag \\ 
	\approx \sum_{j=1}^n \Big[-8Bk\cos^4(\eta) \cos(\omega_\alpha T + \phi_{\alpha_+}+ \phi_{\beta_+}) \Big]^{(j)}
\end{gather}

The blind spot term shows that how this sequence can be engineered to increase or reduce the signal amplitude of one nuclear spin from the spectrum. The bright and blind spots of a frequency in the spectrum are as follows:
\begin{align}
	\text{Blind Spots:	} \tau = even \,\, \frac{\pi}{\omega}\\
	\text{Bright Spots:	} \tau = odd \,\, \frac{\pi}{\omega}
\end{align}
The blind spots does not depend only on one frequency but on the nuclear spin. It means if one resonant frequency is blinded, the other resonant frequency and all the multiple quantum resonances also vanishes. This can be used as a manifestation that which two peaks are from one nuclei. Also, This is very helpful especially in the presence of strongly coupled nuclear spin that suppress other nuclei. By sweeping $\tau_1$ and $\tau_2$, one can go through different bright and blind spots of each nuclear spin, observe which two peaks are correlated.

%pass
\bibliography{references}% Produces the bibliography via BibTeX.

% The \nocite command causes all entries in a bibliography to be printed out
% whether or not they are actually referenced in the text. This is appropriate
% for the sample file to show the different styles of references, but authors
% most likely will not want to use it.
%\nocite{*}
\end{document}
%
% ****** End of file apssamp.tex ******

### 2023-07-25 pict/shield_fitting_model.py

@@ -1,0 +1,229 @@
+import numpy as np 
+import matplotlib.pyplot as plt 
+import scipy as sp
+from scipy import special, stats
+
+# poisson distribution fitting definition - odd/even : odd number events of switching events
+
+def f_odd(tau, n, tR, g0, g1, u0, u1):
+    '''Part of the NV photon statistic. Function in the integral from formula S4 in shields 2015 prl spin to charge conversion paper'''
+    func = g1 * np.exp((g0 - g1) * tau - g0 * tR) * special.iv(0, 2 * np.sqrt(
+        g1 * g0 * tau * (tR - tau))) * stats.poisson.pmf(n, u1 * tau + u0 * (tR - tau))
+    return func
+
+
+def f_even(tau, n, tR, g0, g1, u0, u1):
+    '''Part of the NV photon statistic. Function in the integral from formula S5 in shields 2015 prl spin to charge conversion paper'''
+    func = float(np.sqrt(g1 * g0 * tau / (tR - tau)) * np.exp((g0 - g1) * tau - g0 * tR) * special.iv(1, 2 * np.sqrt(
+        g1 * g0 * tau * (tR - tau))) * stats.poisson.pmf(n, u1 * tau + u0 * (tR - tau)))
+    return func
+
+
+def prob_photon_num(n, tR, g0, g1, u0, u1):
+    """
+    Part of the NV photon statistic. Integration of f_odd and f_even like
+    in the formulas S4/S5 in shields 2015 prl spin to charge conversion paper'''
+    :param n:
+    :param tR:
+    :param g0:
+    :param g1:
+    :param u0:
+    :param u1:
+    :return:
+    """
+    # for NV- g0,g1,u0,u1 stand for g0-,g-0,gamma0,gamma, respectively - in S4
+    # for NV0 switch 0 and 1
+    # tR : readout time of NV spin,
+    # tau : occupying time in charge state
+
+    p_odd, err_odd = sp.integrate.quad(f_odd, 0, tR, args=(n, tR, g0, g1, u0, u1))
+
+    p_even, err_even = sp.integrate.quad(f_even, 0, tR, args=(n, tR, g0, g1, u0, u1))
+
+    p_even += np.exp(-g1 * tR) * stats.poisson.pmf(n,u1 * tR)
+    return p_odd + p_even
+
+
+def prob_total(n, tR, g0, g1, u0, u1):
[…]

### 2023-08-03 article.tex
a
fig

@@
 
-\title{Blueprint for nuclear spin characterization in color centers}% Force line breaks with \\
+\title{Blueprint for nuclear spin characterization in single color center}% Force line breaks with \\
 %\thanks{A footnote to the article title}%
@@
 	\begin{center}
-		\includegraphics[width=0.7\textwidth]{pict/fig1.png}
+		\includegraphics[width=0.7\textwidth]{pict/drawing0.pdf}
 		\caption{a.
@@
 In this work, we take 23 nuclear spin characterized in paper \cite{abobeih2019atomic} as a realistic case.
-\begin{figure*}%[htbp]
+\begin{figure*}[htbp]
 	\begin{center}
@@
 \ref{eq:H}.
-\begin{figure*}%[htbp]
+\begin{figure*}[htbp]
 	\begin{center}
@@
 To distinguish other nuclei, extra measurements is required.
-One method is to use two dimensional hyperfine correlation spectroscopy (2D Hyscore)  \ref{vorobyov2022addressing}.
+One method is to use two dimensional hyperfine correlation spectroscopy (2D Hyscore)  \cite{vorobyov2022addressing}.
 However, this method is rather time-consuming as two time variables has to be swept.

### 2023-08-21 article.tex
fisher
a
f

@@
 
-\title{Blueprint for nuclear spin characterization in single color center}% Force line breaks with \\
+\title{Blueprint for nuclear spin characterization in  color center}% Force line breaks with \\
 %\thanks{A footnote to the article title}%
@@
 Ramsey sequence is sensitive to detuning since the electron spin is not refocused, however it is possible to sense nuclear spins with vanishing perpendicular hyperfine coupling.\\
-\begin{figure}%[htbp]
-	\begin{center}
-		\includegraphics[width=0.9\columnwidth]{pict/seqs.png}
-		\caption{Pulse sequences a. Ramsey b. Hahn Echo c. Dynamical Decoupling d. DDESEEM}
-		\label{fig:seqs}
-	\end{center}
-\end{figure} 
+
 To enhance the relaxation time and have access to more nuclei, one can add a $\pi$ pulse in between the Ramsey sequence and create Hahn-echo sequence and obtain the following signal:
@@
 	\begin{center}
-		\includegraphics[width=0.8\textwidth]{pict/fig3.png}
+		\includegraphics[width=0.8\textwidth]{pict/dd_compare2.pdf}
 		\caption{a. DD for NV in diamond b. DD for group IV defect in diamond }
@@
 	\begin{center}
-		\includegraphics[width=0.9\textwidth]{pict/fig4.png}
+		\includegraphics[width=0.9\textwidth]{pict/eseem_compare2.pdf}
 		\caption{a.
@@
 \section{5pESEEM formula}
+
+Here are the sequences:
+\begin{figure}%[htbp]
+	\begin{center}
+		\includegraphics[width=0.9\columnwidth]{pict/seqs.png}
+		\caption{Pulse sequences a. Ramsey b. Hahn Echo c. Dynamical Decoupling d. DDESEEM}
+		\label{fig:seqs}
+	\end{center}
+\end{figure} 
 \label{app:5pESEEM}

### 2023-08-21 article.tex
n

--- 2023-08-03 article.tex
@@
  \affiliation{3rd physical institute University of Stuttgart, Germany}
-  \affiliation{Max Planck School of Photonics, Germany}%Lines b%Lines break automatically or can be forced with \\
+  %\affiliation{Max Planck School of Photonics, Germany}%Lines b%Lines break automatically or can be forced with \\
 
@@
 	\begin{center}
-		\includegraphics[width=0.7\textwidth]{pict/drawing0.pdf}
-		\caption{a.
-nuclear spins that can be characterized using each sequence.
-b.
-number of nuclear spins as a function of distance for the defect.
-The dashed line shows having T1 = 1s limitation, how many nuclear spins are accessible in diamond.
-}
+		\includegraphics[width=0.9\textwidth]{pict/drawing0.pdf}
+		\caption{Comparing DD and 5pESEEM as two nuclear spin characterization method in different systems.
+a.
+An electron spin one system: in DD signal, each nuclear spin has a distinct resonance time up to first order of $A_{zz}$; the accuracy of the obtained hyperfine interaction is limited to $T_2$ of the electron spin.
+In the Fourier transform of the ESEEM signal, the two resonance frequency of each spin is present; the accuracy of the obtained hyperfine interaction is limited to $T_1$ of the electron spin b.
+An electron spin one system with two strongly coupled nuclear spins and many weakly coupled spins.
+No resonance time is detectable since the required condition for DD ($\omega_L \gg A_{zz}, A{zx}$) does not hold.
+However, resonant frequencies is still obtainable in the ESEEM signal c.
+An electron spin one half system: nuclear spins have more or less the same resonance time as it depends on the second order of hyperfine coupling.
+However, resonant frequency of each spins is distinguishable in the ESEEM signal.
+d.
+A system containing two different nuclear spin species: two nuclear spin bath can interfere in the DD signal, which makes the signal analysis more challenging.
+However, the species can be inferred from ESEEM signal since spe cies have different Larmor frequencies.}
 		\label{fig:1}
@@
 In this work, we take 23 nuclear spin characterized in paper \cite{abobeih2019atomic} as a realistic case.
-\begin{figure*}[htbp]
+\begin{figure}%[htbp]
 	\begin{center}
-		\includegraphics[width=0.8\textwidth]{pict/fig3.png}
-		\caption{a. DD for NV in diamond b. DD for group IV defect in diamond }
+		\includegraphics[width=0.9\columnwidth]{pict/dd_compare2.pdf}
+		\caption{Simulated DD signal with 64 $\pi$-pulses for the register reported \cite{abobeih2019atomic} assuming the electron spin is a.
+spin one b.
+spin one-half system.
+Simulated Fisher information for the case of the electron spin c.
+one d.
+one-half system.}
 		\label{fig:3}
 	\end{center}
-\end{figure*}
+\end{figure}
 Fig \ref{fig:3} compares DD signal for the same nuclear spin register but different defects in diamond.
@@
 \ref{eq:H}.
-\begin{figure*}[htbp]
+\begin{figure}[htbp]
 	\begin{center}
-		\includegraphics[width=0.9\textwidth]{pict/fig4.png}
-		\caption{a.
-FFT of ESEEM signal b.
-a zoom into weakly coupled nuclear spins c.
-Enhancing weakly coupled nuclear spins by having 72 pulses in each entangling period.
-$\tau$ is set to the Larmor bright spot.}
+		\includegraphics[width=0.9\columnwidth]{pict/eseem_compare2.pdf}
+		\caption{Simulated FFT of ESEEM signal with a zoom into weakly coupled nuclear spins for the register reported \cite{abobeih2019atomic} assuming the electron spin is one-half.
+b.
+Enhancing the sensitivity to weakly coupled spins by increasing number of $\pi$-pulses to $N=72$ pulses in each entangling period.
+$\tau$ is set to the Larmor bright spot.
+Simulated Fisher information for the case of the electron spin c.
+one d.
+one-half system.}
 		\label{fig:4}
 	\end{center}
-\end{figure*}
+\end{figure}
 Fig \ref{fig:4} shows the furrier transform of the signal.
@@
 %%%%%%%%%%%%%=========
+\section{5pESEEM formula}
+\label{app:seqs}
+The details of mentioned sequences in the main text can be found in fig \ref{fig:seqs}:
+\begin{figure}%[htbp]
+	\begin{center}
+		\includegraphics[width=0.9\columnwidth]{pict/seqs.png}
+		\caption{Pulse sequences a. Ramsey b. Hahn Echo c. Dynamical Decoupling d. DDESEEM}
+		\label{fig:seqs}
+	\end{center}
+\end{figure}
+
 \section{5pESEEM formula}

### 2023-08-21 article.tex
my stash

--- 2023-08-03 article.tex
@@
 
-\title{Blueprint for nuclear spin characterization in single color center}% Force line breaks with \\
+\title{Blueprint for efficient nuclear spin characterization in  color center}% Force line breaks with \\
 %\thanks{A footnote to the article title}%
@@
 \begin{abstract}
-Color centers are one of the promising platform for implementing quantum applications, using the nuclear spins around the electron spin as qubits with relatively long coherence time.
-However, characterizing each nuclear spin is quite cumbersome as the characterization protocol may differ depending on the strength of the hyperfine coupling.
+Nuclear spins in solids is one of the most promising platforms for realisation of a scalable quantum hardware.
+They could be efficiently adressed at single site level by nearby single colour centers via the spin resonance.
+However, characterising each nuclear spin is quite cumbersome as the characterisation protocol may differ depending on the strength of the hyperfine coupling.
+The most adopted protocol is modified electron spin Hahn-echos such as CPMG and XY8 pulse sequences.
+In some cases, e.g.
+for spin 1/2, strongly coupled spins, and bispecies bath this protocol contains severe problems in applying for the nuclear spin bath characterisation.
 Here, we present a more straight forward method to obtain hyperfine interaction among nuclear spins and the electron spin. 
-This method can be used for a variety of platform including group IV defects in diamond or Silicon vacancy in Silicon Carbide.
+This method can be used for a variety of platform including emerging S=1/2 group IV defects in diamond (e.g. SiV, GeV, SnV, PbV) or Silicon vacancy in Silicon Carbide.
+We summarize theoretical framework and adopt it from ESR for the use in colour centers with various spins, and numerically consider case of nuclear spin cluster, as compare performance of various protocols on this example via the Fisher information matrix.
 \end{abstract}
@@
 \section{Introduction and background}
-Optically active defects in solids, color centers, has been applied for realizing different quantum applications \cite{awschalom2018quantum}, such as a quantum network \cite{pompili2021realization}, quantum sensing \cite{degen2017quantum}, and quantum register \cite{bradley2019ten}.
-Each center contains an electron spin that can be controlled directly with microwaves and optics and many nuclear spins that can be manipulated through the electron spin.
-Characterizing nuclear spins is necessary for enlarging the quantum register and precise description of the electron spin dynamics.
-Traditionally, nuclear spin characterization is done with Opticall Detected Magnetic Resonance (ODMR) (ref to Phillip Neumann's works), however the spectroscopic resolution is limited to the $T_2^\ast$ of the electron spin.
+Optically active defects in solids, color centers, has been applied for realising different quantum applications \cite{awschalom2018quantum}, such as a quantum network \cite{pompili2021realization}, quantum sensing \cite{degen2017quantum}, and quantum registers \cite{bradley2019ten}.
+Each center contains an electron spin that can be controlled directly with microwaves, aligned and read via optics. 
+The key element for most applications is that they could be coupled through the hyperfine coupling to the bath of numerous nuclear spins presenting a long living quantum memories and could present a nuclear spin qubit register.
+To design the efficient quantum control for the memories, a precise knowledge of the full hamiltonian of the register needs to be known and characterised before. 
+However, characterising the nuclear spin hyperfine coupling could be a challenge and a lengthy procedure.
+
+is necessary for enlarging the quantum register and precise description of the electron spin dynamics.
+Traditionally, nuclear spin characterisation is done with Optically Detected Magnetic Resonance (ODMR) (ref to Phillip Neumann's works), however the spectroscopic resolution is limited to the $T_2^\ast$ of the electron spin.
 Hence, some sequence is needed to increase the resolution.
@@
 Depending on the applied protocol for nuclear spins characterization, the number of accessible nuclear spin can increase.
-Electron Spin Echo Envelop Modulation (ESEEM) types of sequences allow us to access the highest number of nuclear spins since the spectroscopy resolution is limited to the longitudinal relaxation time (T1) of the system (see fig.
+Electron Spin Echo Envelop Modulation (ESEEM) types of sequences allow us to access the highest number of nuclear spins since the spectroscopy resolution is limited to the longitudinal relaxation time ($T_1$) of the system (see fig.
 \ref{fig:1}).
@@
 Assuming the typical values of $T_2^{HE} = 100 $ $\mu$s, a nuclear spin can be distinguished from another one if their transverse hyperfine coupling is separated by $\delta A_{zx} = 80$ kHz, which is quite inaccurate.\\
+
+\begin{figure*}[htbp]
+	\begin{center}
+		\includegraphics[width=0.8\textwidth]{pict/Fisher.pdf}
+		\caption{a. DD spin 1 b. DD spin 1/2 c. 5pESEEM spin 1 d. 5pESEEM spin 1/2 }
+		\label{fig:Fisher}
+	\end{center}
+\end{figure*}
 

### 2023-08-22 article.tex
some work on the fig1 text and intro
@majidzahedian please check the fig1

--- 2023-08-21 article.tex
@@
 
-\title{Blueprint for nuclear spin characterization in  color center}% Force line breaks with \\
+\title{Blueprint for efficient nuclear spin characterization in  color center}% Force line breaks with \\
 %\thanks{A footnote to the article title}%
@@
 \section{Introduction and background}
-Optically active defects in solids, color centers, has been applied for realizing different quantum applications \cite{awschalom2018quantum}, such as a quantum network \cite{pompili2021realization}, quantum sensing \cite{degen2017quantum}, and quantum register \cite{bradley2019ten}.
-Each center contains an electron spin that can be controlled directly with microwaves and optics and many nuclear spins that can be manipulated through the electron spin.
-Characterizing nuclear spins is necessary for enlarging the quantum register and precise description of the electron spin dynamics.
-Traditionally, nuclear spin characterization is done with Opticall Detected Magnetic Resonance (ODMR) (ref to Phillip Neumann's works), however the spectroscopic resolution is limited to the $T_2^\ast$ of the electron spin.
-Hence, some sequence is needed to increase the resolution.
-People have used Hahn Echo sequence to refocus the electron spin and enhance the coherence time of the electron spin \cite{childress2006coherent}.
-But this method only works for defects with a specific nuclear spins configuration.
-Depending on the applied protocol for nuclear spins characterization, the number of accessible nuclear spin can increase.
-Electron Spin Echo Envelop Modulation (ESEEM) types of sequences allow us to access the highest number of nuclear spins since the spectroscopy resolution is limited to the longitudinal relaxation time (T1) of the system (see fig.
-\ref{fig:1}).
+Optically active defects in solids, color centers, has been applied for realising different quantum applications \cite{awschalom2018quantum}, such as a quantum network \cite{pompili2021realization}, quantum sensing \cite{degen2017quantum}, and quantum registers \cite{bradley2019ten}.
+Each center contains an electron spin that can be controlled directly with microwaves, initialised and read out via optical excitation. 
+The key element for most applications is that they could be coupled through the hyperfine coupling to the bath of numerous nuclear spins presenting a long living quantum memories and could present an optically accessible nuclear spin qubit register.
+To design the efficient quantum control for the memories, a precise knowledge of the full hamiltonian of the register needs to be known and characterised before. 
+However, characterising the nuclear spin hyperfine coupling could be a challenging and a lengthy procedure \cite{taminuau27, taminiau50}. 
+Traditionally, nuclear spin characterisation is done with Optically Detected Magnetic Resonance (ODMR) \cite{Dreau, Neumann, Eriks}, however the spectroscopic resolution is limited to the $1/T_2^\ast$ of the electron spin.
+Hahn Echo type sequences have been used to refocus the electron spin and enhance the coherence time of the electron spin \cite{childress2006coherent} thus improving the resolution to $1/T_2$. 
+This method could be applied for the defects with a specific nuclear spins configuration \vvv{(which?)}. 
+\vvv{In particular, the certain relation to the magnetic field and the coupling of the nuclear spins should be kept, (weakly coupled nuclear spins), as well as the spin number of the electron spin is affecting the observed behaviour}
+Depending on the applied protocol for the nuclear spins characterization, the number of accessible nuclear spin can increase.
+Electron Spin Echo Envelop Modulation (ESEEM) types of sequences allow us to access the highest number of nuclear spins since the spectroscopy resolution is limited to the longitudinal relaxation time ($T_1$) of the system (see fig.
+\ref{fig:1}) \cite{Laraui, Vorobyov}.
+In particular we consider following common examples of nuclear spin registers ubiquitios in the applications.
+First, NV-like case with S=1, and weakly coupled nuclear spins, at high mangetic field such that $\gamma_n B \gg A_{zx}$.
+This case is very well studied in the works of \cite{Tam27, Tam2012, Tam2014, Wrachtrup, before}.
+The ability to see narrow peaks with analytically predictable position and contrast allows one to solve the inverse problem of characterising the coupling of the nuclear spins to the electron spins. 
+The second case (see in Fig. \ref{fig1b}) refers to a similar case but with a strongly coupled nuclear spin, which hinders the observation of a weakly coupled nuclear spins. 
+This case in particular  is relevant for the case, where additional to the weakly coupled register a strongly coupled nuclear spin is used for e.g.
+repetitive  enhancment of the readout, via using the strongly coupled ancilla resolved in electron spin resonance spectra.
+The third case (Fig.
+1c) is relevant for the S=1/2 case, where due to the lack of the offset in the average evolution of the nuclear spin, its dynamics weakly depends on the Azz and only in the second order on the Azx \cite{suckachev}.
+This leads to a poor distinguising ability of multiple nuclear spins and as a result lack of individual addressability of nuclear spins. 
+Finally, in the case of other materials host platforms, a bispecies nuclear spin bath could be observed, where the resonance peaks referrring to different larmour frequencies of different species additionaly complicate the reconstruction of the hamiltonian, and for unambiguous reconstruction of the interactions, additionall measurements e.g.
+at different B field would be needed.
+In this work we argue that a correlation type sequence, based on 5p eseem could serve as a general framework as it promisses greate reconstruction potential for all above mentioned cases.  
 \begin{figure*}%[htbp]
@@
 		\includegraphics[width=0.9\textwidth]{pict/drawing0.pdf}
-		\caption{Comparing DD and 5pESEEM as two nuclear spin characterization method in different systems.
+		\caption{Comparison of DD and 5pESEEM as two nuclear spin characterization method in different systems.
 a.
-An electron spin one system: in DD signal, each nuclear spin has a distinct resonance time up to first order of $A_{zz}$; the accuracy of the obtained hyperfine interaction is limited to $T_2$ of the electron spin.
+An electron spin one system $S=1$: in DD signal, each nuclear spin has a distinct resonance time up to first order of $A_{zz}$; the accuracy of the obtained hyperfine interaction is limited to $T_2$ of the electron spin.
 In the Fourier transform of the ESEEM signal, the two resonance frequency of each spin is present; the accuracy of the obtained hyperfine interaction is limited to $T_1$ of the electron spin b.
@@
 A system containing two different nuclear spin species: two nuclear spin bath can interfere in the DD signal, which makes the signal analysis more challenging.
-However, the species can be inferred from ESEEM signal since spe cies have different Larmor frequencies.}
+However, the species can be inferred from ESEEM signal since spe cies have different Larmor frequencies.\vvv{@Majid, typo in fig1C ($A_{zx}^2$) Please make the label in the figure larger, e.g.
+Counts, tau, pi, etc.
+Please draw plots without markers, so that they are easier to visualise in pdf, (smaller fig weight in MB)}}
 		\label{fig:1}
@@
 %%%%%%%%%%%%%%%%%%%================= %THEORY
-\section{Methods}
+\section{Results}
 \label{sec:theory}
 %%%%%%%%%%%%%%%Í%%%%=================
-In this section, we provide the theoretical formulas for.
-In a central electron spin with the electron spin $\boldmath{S}$, we only apply pulses resonant with two of the electron spin sublevels, denoted as $m_s=s_0$ and $m_s = s_1$.
-These two spin sublevels are separated, due to Zeeman effect or zero field splitting, and form an artificial two-level system with energy splitting of $\omega_a$.
-Now, we add spin $\frac{1}{2}$nuclear spins to the system (for considering P1 centers, one has to add nuclear quadrupole to the presented Hamiltonian.).
-The Hamiltonian of a central electron spins system surrounded by nuclear spins in the secular approximation in the rotating frame of the applied microwave $\omega_{mw}$ (considering rotating wave approximation) can be written as:
+We consider a central spin system of \textit{non-interacting} nuclear spins $I=1/2$ coupled to the central electron spin $\boldmath{S}$. 
+The central electron spin is manipulated resonantly with the microwave pulses, which transfer the population between the two sublevels, denoted as $m_s=s_0$ and $m_s = s_1$. 
+These two spin sublevels are separated, due to the Zeeman effect and/or zero field splitting, and form an two-level subsystem with energy splitting of $\omega_a$. 
+The Hamiltonian of the system in the secular approximation and in the rotating frame of the applied microwave $\omega_{mw}$ can be written as:
 \begin{align}
@@
 Where $\Delta = \omega_a - \omega_{mw}$ is the detuning, $\omega_L^{(k)} =\gamma_n^{(k)} B$ is nuclear Rabi frequency with $\gamma_n^{(k)}$ nuclear spin gyromagnetic ratio and $B$ external magnetic field, $A_{zz}, A_{zx}$ parallel and perpendicular secular component of hyperfine tensor.
-This Hamiltonian results that depending on the electron spin sublevel $s_i$ ($i=0,1$), the nuclear spin rotate with the resonance frequency of $\omega_i = \sqrt{(\omega_L + s_i A_{zz})^2+ (s_i A_{zx})^2}$, $i=0,1$ along the axes $\vec{n}_i =(\frac{s_i A_{zx}}{\omega_i}, 0, \frac{\omega_L + s_i A_{zz}} {\omega_i})$.
+The Hamiltonian is diagonal in the electron spin subspace, thus the hamiltonian for the nuclear spins could be rewritten in electron spin subdomains $s_i$ ($i=0,1$).
+The nuclear spin hamiltonian could be solved for eigenenergies, which determine the precession frequencies of $\omega_i = \sqrt{(\omega_L + s_i A_{zz})^2+ (s_i A_{zx})^2}$, $i=0,1$ along the eigenvector axes $\vec{n}_i =(\frac{s_i A_{zx}}{\omega_i}, 0, \frac{\omega_L + s_i A_{zz}} {\omega_i})$.
 It is assumed that the pulse duration $t_p$ are short enough ($\omega_L t_p \ll 1$) that the nuclear spin dynamics during this time is negligible.
-The most simplest characterization sequence is Ramsey.
-\\ The Ramsey signal can be obtained as follows:
+For compleetness we start our analysis with the simplest characterization sequence, which is the electron spin ramsey sequence (free induction decay of electron) (see Appendix for derivation).
+The Ramsey signal can be obtained as follows:
 \begin{gather}
@@
 	(\vec{n_0}\cdot \vec{n_1})\sin(\frac{\omega_0 \tau}{2}) \sin(\frac{\omega_1 \tau}{2}) \Big]^{(k)}
-	\textcolor{gray}{e^{-\frac{\tau}{T_2^\ast}}}
+	\textcolor{gray}{e^{-(\frac{\tau}{T_2^\ast})^m}}
 \end{gather} 
 We do not take any relaxation process into account and the gray exponential decay is put by hand to remember the relaxation time scale.
-Ramsey signal decay with electron spin $T_2^\ast$, so it can be used to observe the core of the defect.
+Ramsey signal decay with electron spin $T_2^\ast$, so it can be used to observe the core of the defect which is coupled stronger than $1/T_2^\ast \approx 0.5$ MHz.
 Ramsey sequence is sensitive to detuning since the electron spin is not refocused, however it is possible to sense nuclear spins with vanishing perpendicular hyperfine coupling.\\
 
-To enhance the relaxation time and have access to more nuclei, one can add a $\pi$ pulse in between the Ramsey sequence and create Hahn-echo sequence and obtain the following signal:
+To enhance the relaxation time and have access to more nuclei, one can add a $\pi$ pulse in between the Ramsey sequence and create Hahn-echo sequence and obtain the following signal (see \cite{Maze, HahnEchoESEEM}):
 \begin{gather}
 	\expval{\sigma_z}_{HE} = \prod_{j=1}^n \Big[1 - 2 k^2 
-	\sin^2(\frac{\omega_0 \tau}{2}) \sin^2(\frac{\omega_1 \tau}{2})\Big]^{(j)} \textcolor{gray}{ e^{-\frac{2\tau}{T_2}}}
+	\sin^2(\frac{\omega_0 \tau}{2}) \sin^2(\frac{\omega_1 \tau}{2})\Big]^{(j)} \textcolor{gray}{ e^{-(\frac{2\tau}{T_2})^m}}
 \end{gather}
 Where $k = \frac{(s_1-s_0)\omega_L A_{zx}}{\omega_0 \omega_1}$ is the modulation amplitude of each nuclear spin.  
-We know that without any nuclear spin, Hahn Echo sequence creates the electron spin echo signal with the envelope of exponential decay with $T_2^{HE}$.
+Without any nuclear spin, Hahn Echo sequence creates the electron spin echo signal with the envelope of stretched exponential decay with $T_2^{HE}$. 
 However in the presence of nuclear spins, the electron spin echo envelope will be modulated due to interaction with nuclei. 
@@
 Hahn Echo sequence can be used for defects that contain a few strongly coupled nuclei.
-In order to differentiate the resonance frequency of each nuclear spin or make the oscillation sharper, one has to add more $\pi$ pulses and for the so-called Dynamical Decoupling sequence:
-Finally, the signal for dynamical decoupling is obtained:
+In order to differentiate the resonance frequency of each nuclear spin or make the oscillation sharper, one can to add more $\pi$ pulses and for the so-called Dynamical Decoupling sequence to sharpen the resonance conditions (neglecting decoherence terms):
 \begin{gather}
@@
 	\prod_{j=1}^n \Big[1- 2 k^2  
-	\sin^2(\frac{\omega_0 \tau}{2}) \sin^2(\frac{\omega_1 \tau}{2}) \frac{\sin^2(\frac{N}{2} \theta)}{\cos^2(\frac{1}{2}\theta)}  \Big]^{(j)} \textcolor{gray}{ e^{-\frac{2N\tau}{T_2(N)}}} 
+	\sin^2(\frac{\omega_0 \tau}{2}) \sin^2(\frac{\omega_1 \tau}{2}) \frac{\sin^2(\frac{N}{2} \theta)}{\cos^2(\frac{1}{2}\theta)}  \Big]^{(j)} %\textcolor{gray}{ e^{-\frac{2N\tau}{T_2(N)}}} 
 \end{gather}
@@
 \end{gather}
-$\vec{n}_0 \cdot \vec{n}_1 = \frac{\omega_L^2+(s_0+s_1)A_{zz}+s_0 s_1 (A_{zz}^2+A_{zx}^2)}{\omega_0 \omega_1}$ and $N$ is the number of $\pi$ pulses that must be an even. Each nuclear 
-If the magnetic field is high or all nuclear spins are weakly coupled such that $\omega_L \gg A_{zz}, A_{zx}$, the multiplication rule can be approximated by a summation rule, which makes the higher order resonance disappear:
+$\vec{n}_0 \cdot \vec{n}_1 = \frac{\omega_L^2+(s_0+s_1)A_{zz}+s_0 s_1 (A_{zz}^2+A_{zx}^2)}{\omega_0 \omega_1}$ and $N$ is the number of $\pi$ pulses that must be an even number.
+ If the magnetic field is high or all nuclear spins are weakly coupled such that $\omega_L \gg A_{zz}, A_{zx}$, the multiplication rule can be approximated by a summation rule, which makes the higher order resonance disappear (neglecting decoherence decay terms):
 \begin{gather}
 	\expval{\sigma_z}_{DD} \approx 1 -2
-	\sum_{j=1}^n \Big[ k^2 	 \sin^2(\frac{\omega_0 \tau}{2}) \sin^2(\frac{\omega_1 \tau}{2}) \frac{\sin^2(\frac{N}{2} \theta)}{\cos^2(\frac{1}{2}\theta)}  \Big]^{(j)} \textcolor{gray}{ e^{-\frac{2N\tau}{T_2(N)}}}
+	\sum_{j=1}^n \Big[ k^2 	 \sin^2(\frac{\omega_0 \tau}{2}) \sin^2(\frac{\omega_1 \tau}{2}) \frac{\sin^2(\frac{N}{2} \theta)}{\cos^2(\frac{1}{2}\theta)}  \Big]^{(j)} %\textcolor{gray}{ e^{-\frac{2N\tau}{T_2(N)}}}
 \end{gather}
@@
 The perpendicular part of hyperfine interaction can be obtained from a fit to the Lorentzian dip with the width of $\frac{(s_1-s_0)\omega_L A_{zx}}{(2p+1)\pi\omega_0 \omega_1}$ or varying the number of pulses and fitting the minima position to the formula $\expval{\sigma_z}_{DD}^{(k)} \approx 1- 2 \sin^2\big(\frac{N}{2}\frac{(s_1-s_0)\omega_L A_{zx}}{\omega_0 \omega_1}\big) $.
-Although Dynamical Decoupling (DD) sequence is well understood and used to characterize nuclear spins, it is not applicable for any system.
+Although Dynamical Decoupling (DD) sequence is well understood and used to characterize nuclear spins, it is not applicable for any system (see Fig.1 a).
 First, DD only works for defects with high magnetic field and low hyperfine coupling ($\omega_L \gg A_{zz}, A_{zx}$).
@@
 (Maybe AI solves this problem in the future?) one has to collect enough data to make sure no two nuclear spin overlap in the signal.
-Forth, this sequence does not work for spin one half system, e.g., group IV defect in diamond, since parallel component of hyperfine coupling cancels their effect in the resonance time up to the first and second order.
+Forth, this sequence does not work for spin one half system, e.g., group IV defect in diamond, since parallel component of hyperfine coupling cancels their effect in the resonance time up to the first and second order (see Fig.
+1c).
 Hence, the resonance time depends on the second order of perpendicular component.
-In this work, we take 23 nuclear spin characterized in paper \cite{abobeih2019atomic} as a realistic case.
 \begin{figure}%[htbp]
@@
 		\caption{Simulated DD signal with 64 $\pi$-pulses for the register reported \cite{abobeih2019atomic} assuming the electron spin is a.
-spin one b.
-spin one-half system.
+S=1 spin one b.
+S=1/2 spin one-half system.
 Simulated Fisher information for the case of the electron spin c.
-one d.
-one-half system.}
+S=1 d.
+S=1/2 one-half system.}
 		\label{fig:3}
@@
 \end{figure}
+
+In this work, we take the 23 nuclear spins cluster characterized in paper \cite{abobeih2019atomic} as a realistic case. 
+First, we apply this to the dynamical decoupling sequence, and visualise the obtained results. 
 Fig \ref{fig:3} compares DD signal for the same nuclear spin register but different defects in diamond. 
-We present a handwavy definition for the sensitivity of a sequence to the variation of hyperfine coupling.
+An intuitive description for the sensitivity of a sequence to the variation of hyperfine coupling could estimated knowing the width and sensitivity of the position of the resonances. 
 First, we consider the case of NV center in diamond. 
-By knowing the width of a dip $\delta \tau = \frac{A_{zx}}{\omega_L^2}$  and taking the derivative of the resonance time, we define the sensitivity of longitudinal hyperfine coupling as follows:
+The width of a dip $\delta \tau = \frac{A_{zx}}{\omega_L^2}$  and taking the derivative of the resonance time, we define the sensitivity of longitudinal hyperfine coupling as follows:
 \begin{gather}

### 2023-08-22 article.tex
work on the text
@majidzahedian , please reply to XXX

@@
 If we assume the typical values of $T_2^{HE} = 100 $ $\mu$s and $\omega_L=500 $ kHz, a weakly coupled nuclear spin $A_{zx}=5$ kHz can be distinguished from another weakly coupled nuclear spin with $\delta A_{zz} = 400$ Hz.
-On the other hand, for group IV detects in diamond, The resonance times is sensitive to the second order of $A_{zx}$ and no sensitivity to $A_{zz}$.
-Hence, even at large $\tau$ the nuclear spin not separated well.
+For $S=1/2$, e.g. for group IV defects in diamond, the resonance times is sensitive to the second order of $A_{zx}$ and no sensitivity to $A_{zz}$. 
+Hence, even at large $\tau$ the resonances related to nuclear spins will not be separated well. 
 We define the sensitivity for the spin one half system as follows:
@@
 \end{gather}
-Assuming the typical values of $T_2^{HE} = 100 $ $\mu$s, a nuclear spin can be distinguished from another one if their transverse hyperfine coupling is separated by $\delta A_{zx} = 80$ kHz, which is quite inaccurate.\\
+Assuming the typical values of $T_2^{HE} = 100 $ $\mu$s, a nuclear spin can be distinguished from another one if their transverse hyperfine coupling is separated by $\delta A_{zx} = 80$ kHz, which is quite inaccurate and $\approx 160$ times worse than for $S=1$.
+To quantify the difference in sensitivity to estimating the hyperfine parameters, we perform calculation of the Fisher information matrix (FIM) for the 23 nuclear spin cluster, with 23 $A_{zz}$ and 23 $A_{zx}$ parameters (see Fig.
+\ref{fig:3}c,d).
+The fisher information matrix is estimated for the probability to measure state $|0\rangle$ and reads as: 
+\begin{equation}
+F_{ij}(\textbf{A})=\sum_\tau \frac{\partial p(0, \tau, \textbf{A})}{\partial A_i}\frac{\partial p(0, \tau, \textbf{A})}{ \partial A_j} \frac{1}{p (1-p)}.
+\end{equation}
+For the typical case of NV center, with $S=1$, since all the nuclear spin resonances are clearly resolved, the Fisher information matrix takes a diagonal shape, revealing a low covariance between the various nuclear spin resonances.
+The crosstalk is existing between $A_{zz}$ and $A_{zx}$ of same nuclear spin, which is because the position of the peaks depends on both values. 
+The fisher information gives a bound for the precision of parameter estimation, known as Cramér–Rao bound: 
+\begin{equation}
+\delta A^2 \ge \frac{1}{F(A) N}
+\end{equation}
+For the presented protocol, the precision for various spins is limited by \vvv{XXX} for the S=1, for the N = 4000.
 
-We want to make a sequence that is limited by T1 instead of T2.
-The idea of 5-pulse ESEEM \cite{kasumaj20085} is that to create an entanglement (Hahn-echo) before the free evolution (Ramsey).
-In other words, change the initial density matrix for the Ramsey sequence from such that entanglement already exist in the electron polarization terms of the density matrix.
+ The striking difference to the $S=1$ fisher information matrix, is the behaviour of the defect with $S=1/2$
+
+On the other hand, a sequence that is limited by $T_1$ instead of $T_2$ is based on 3 and 5-pulse ESEEM.
+The main principle of 5-pulse ESEEM \cite{kasumaj20085} is to create an entanglement (via e.g.
+Hahn-echo block) before the free evolution of the nuclear spins and after make a second correlating sequence.
+In other words, change the initial density matrix for the Ramsey sequence from such that entanglement already exist in the electron polarization terms of the density matrix, thus limitied by $T_1$ time.
 Fig \ref{fig:seqs} shows the sequence, which can be interpreted as two Hahn Echos that are separated by a long free evolution $T\gg T_2^\ast$ such that the coherence of the electron spin vanishes. 
@@
 \end{figure}
-Fig \ref{fig:4} shows the furrier transform of the signal.
+Fig \ref{fig:4} shows the Fourier transform of the signal. 
 Zooming into area close to the Larmor frequency reveals the weakly coupled nuclei. 
@@
 Expanding the resonance frequencies up to first order with respect to hyperfine coupling results that the weakly coupled nuclei keep their order as they go further away from the nuclei. 
-This fact makes their characterization rather straight forward.
-To observe the weakly coupled nuclei more pronouncedly, one can use DDESEEM sequence by adding more $\pi$ pulses in the entangling periods.
+This fact makes their characterisation rather straight forward. 
+To observe the weakly coupled nuclei more pronouncedly, one can use DD-ESEEM sequence by adding more $\pi$ pulses in the entangling periods. 
 To distinguish other nuclei, extra measurements is required. 

### 2023-08-23 article.tex
a

--- 2023-08-21 article.tex
@@
 In this work, we take 23 nuclear spin characterized in paper \cite{abobeih2019atomic} as a realistic case.
-\begin{figure*}[htbp]
+\begin{figure*}%[htbp]
 	\begin{center}
-		\includegraphics[width=0.8\textwidth]{pict/fig3.png}
-		\caption{a. DD for NV in diamond b. DD for group IV defect in diamond }
+		\includegraphics[width=0.9\textwidth]{pict/dd_compare2.pdf}
+		\caption{Simulated DD signal with 64 $\pi$-pulses for the register reported \cite{abobeih2019atomic} assuming the electron spin is a.
+spin one b.
+spin one-half system.
+Simulated Fisher information for the case of the electron spin c.
+one d.
+one-half system.}
 		\label{fig:3}
@@
 
-\begin{figure*}[htbp]
-	\begin{center}
-		\includegraphics[width=0.8\textwidth]{pict/Fisher.pdf}
-		\caption{a. DD spin 1 b. DD spin 1/2 c. 5pESEEM spin 1 d. 5pESEEM spin 1/2 }
-		\label{fig:Fisher}
-	\end{center}
-\end{figure*}
-
 We want to make a sequence that is limited by T1 instead of T2.
@@
 	\begin{center}
-		\includegraphics[width=0.9\textwidth]{pict/fig4.png}
-		\caption{a.
-FFT of ESEEM signal b.
-a zoom into weakly coupled nuclear spins c.
-Enhancing weakly coupled nuclear spins by having 72 pulses in each entangling period.
-$\tau$ is set to the Larmor bright spot.}
+		\includegraphics[width=0.9\textwidth]{pict/eseem_compare2.pdf}
+		\caption{Simulated FFT of ESEEM signal with a zoom into weakly coupled nuclear spins for the register reported \cite{abobeih2019atomic} assuming the electron spin is one-half.
+b.
+Enhancing the sensitivity to weakly coupled spins by increasing number of $\pi$-pulses to $N=72$ pulses in each entangling period.
+$\tau$ is set to the Larmor bright spot.
+Simulated Fisher information for the case of the electron spin c.
+one d.
+one-half system.}
 		\label{fig:4}

### 2023-08-24 article.tex
ok
a

@@
 A system containing two different nuclear spin species: two nuclear spin bath can interfere in the DD signal, which makes the signal analysis more challenging.
-However, the species can be inferred from ESEEM signal since spe cies have different Larmor frequencies.}
+However, the species can be inferred from ESEEM signal since species have different Larmor frequencies.}
 		\label{fig:1}
@@
 In this work, we take 23 nuclear spin characterized in paper \cite{abobeih2019atomic} as a realistic case.
-\begin{figure*}%[htbp]
+\begin{figure}%[htbp]
 	\begin{center}
-		\includegraphics[width=0.9\textwidth]{pict/dd_compare2.pdf}
+		\includegraphics[width=0.9\columnwidth]{pict/dd_compare2.pdf}
 		\caption{Simulated DD signal with 64 $\pi$-pulses for the register reported \cite{abobeih2019atomic} assuming the electron spin is a.
@@
 	\end{center}
-\end{figure*}
+\end{figure}
 Fig \ref{fig:3} compares DD signal for the same nuclear spin register but different defects in diamond.
@@
 \ref{eq:H}.
+
 \begin{figure*}[htbp]
@@
 \end{figure*}
+
+>>>>>>> c0eaca02ca59681a3dedd48a17843824ce2f8aac
 Fig \ref{fig:4} shows the furrier transform of the signal.

### 2023-08-24 article.tex
copy pasted vadim text

@@
 In this work, we take 23 nuclear spin characterized in paper \cite{abobeih2019atomic} as a realistic case.
-\begin{figure}%[htbp]
+\begin{figure*}%[htbp]
 	\begin{center}
-		\includegraphics[width=0.9\columnwidth]{pict/dd_compare2.pdf}
+		\includegraphics[width=0.9\textwidth]{pict/dd_compare2.pdf}
 		\caption{Simulated DD signal with 64 $\pi$-pulses for the register reported \cite{abobeih2019atomic} assuming the electron spin is a.
@@
 	\end{center}
-\end{figure}
+\end{figure*}
 Fig \ref{fig:3} compares DD signal for the same nuclear spin register but different defects in diamond.
@@
 \end{gather}
-Assuming the typical values of $T_2^{HE} = 100 $ $\mu$s, a nuclear spin can be distinguished from another one if their transverse hyperfine coupling is separated by $\delta A_{zx} = 80$ kHz, which is quite inaccurate.\\
+Assuming the typical values of $T_2^{HE} = 100 $ $\mu$s, a nuclear spin can be distinguished from another one if their transverse hyperfine coupling is separated by $\delta A_{zx} = 80$ kHz, which is quite inaccurate and $\approx 160$ times worse than for $S=1$.
+To quantify the difference in sensitivity to estimating the hyperfine parameters, we perform calculation of the Fisher information matrix (FIM) for the 23 nuclear spin cluster, with 23 $A_{zz}$ and 23 $A_{zx}$ parameters (see Fig.
+\ref{fig:3}c,d).
+The fisher information matrix is estimated for the probability to measure state $|0\rangle$ and reads as: 
+\begin{equation}
+	F_{ij}(\textbf{A})=\sum_\tau \frac{\partial p(0, \tau, \textbf{A})}{\partial A_i}\frac{\partial p(0, \tau, \textbf{A})}{ \partial A_j} \frac{1}{p (1-p)}.
+\end{equation}
+For the typical case of NV center, with $S=1$, since all the nuclear spin resonances are clearly resolved, the Fisher information matrix takes a diagonal shape, revealing a low covariance between the various nuclear spin resonances.
+The crosstalk is existing between $A_{zz}$ and $A_{zx}$ of same nuclear spin, which is because the position of the peaks depends on both values. 
+The fisher information gives a bound for the precision of parameter estimation, known as Cramér–Rao bound: 
+\begin{equation}
+	\delta A^2 \ge \frac{1}{F(A) N}
+\end{equation}
+For the presented protocol, the precision for various spins is limited by \vvv{XXX} for the S=1, for the N = 4000. \\
 
-We want to make a sequence that is limited by T1 instead of T2.
-The idea of 5-pulse ESEEM \cite{kasumaj20085} is that to create an entanglement (Hahn-echo) before the free evolution (Ramsey).
-In other words, change the initial density matrix for the Ramsey sequence from such that entanglement already exist in the electron polarization terms of the density matrix.
+The striking difference to the $S=1$ fisher information matrix, is the behaviour of the defect with $S=1/2$.
+
+On the other hand, a sequence that is limited by $T_1$ instead of $T_2$ is based on 3 and 5-pulse ESEEM.
+The main principle of 5-pulse ESEEM \cite{kasumaj20085} is to create an entanglement (via e.g.
+Hahn-echo block) before the free evolution of the nuclear spins and after make a second correlating sequence.
+In other words, change the initial density matrix for the Ramsey sequence from such that entanglement already exist in the electron polarization terms of the density matrix, thus limitied by $T_1$ time.
 Fig \ref{fig:seqs} shows the sequence, which can be interpreted as two Hahn Echos that are separated by a long free evolution $T\gg T_2^\ast$ such that the coherence of the electron spin vanishes. 
@@
 
->>>>>>> c0eaca02ca59681a3dedd48a17843824ce2f8aac
-Fig \ref{fig:4} shows the furrier transform of the signal.
+Fig \ref{fig:4} shows the Fourier transform of the signal. 
 Zooming into area close to the Larmor frequency reveals the weakly coupled nuclei. 

### 2023-08-24 article.tex
final?

@@
 Finally, the signal for dynamical decoupling is obtained:
+\small 
 \begin{gather}
@@
 \end{gather}
+\normalsize
 Where
@@
 If the magnetic field is high or all nuclear spins are weakly coupled such that $\omega_L \gg A_{zz}, A_{zx}$, the multiplication rule can be approximated by a summation rule, which makes the higher order resonance disappear:
+\small
 \begin{gather}
@@
 	\sum_{j=1}^n \Big[ k^2 	 \sin^2(\frac{\omega_0 \tau}{2}) \sin^2(\frac{\omega_1 \tau}{2}) \frac{\sin^2(\frac{N}{2} \theta)}{\cos^2(\frac{1}{2}\theta)}  \Big]^{(j)} \textcolor{gray}{ e^{-\frac{2N\tau}{T_2(N)}}}
+	\label{eq:approx_DD}
 \end{gather}
+\normalsize
 The parallel component of the hyperfine interaction can be obtained from the resonance time of each nuclear spin:
@@
 \end{equation}
-For the presented protocol, the precision for various spins is limited by \vvv{XXX} for the S=1, for the N = 4000. \\
+For the presented protocol, the precision for various spins is limited by 0.09 Hz for the S=1, for the N = 4000. \\
 
@@
 %%%%%%%%%%%%%=========
-\section{5pESEEM formula}
+\section{Sequences}
 \label{app:seqs}
@@
 
+\section{DD analysis for bispecies systems}
+\label{app:bispecies}
+Consider a single color center that is surrounded by two nuclear spin species.
+Each species has a distinct bath, which is processing with its corresponding Larmor frequency.
+Assuming large Larmor frequency with respect to hyperfine couplings, one can write Eq.
+\ref{eq:approx_DD} for two bath ($\omega_0 \approx \omega_1 \approx \omega_L$) as follows:
+\begin{gather}
+	\expval{\sigma_z}_{bath} \approx 1 -2 k_1^2 \sin^4(\frac{\omega_L^{(1)} \tau}{2}) -2 k_2^2 \sin^4(\frac{\omega_L^{(2)} \tau}{2})
+\end{gather}
+This means that two baths interfere, and the periodicity of the total bath is not straightforward any more.
+Hence, if there is a narrow peak next in DD signal, it can be attributed to both of the baths.
+To clarify the type of nuclear spins, one has to perform further experiments, e.g., in various external magnetic fields.
 %pass

### 2023-08-30 article.tex
hehe, bring back my text from Majid's merge from origin (my commit work in the text was overwritten)

@@
 Optically active defects in solids, color centers, has been applied for realising different quantum applications \cite{awschalom2018quantum}, such as a quantum network \cite{pompili2021realization}, quantum sensing \cite{degen2017quantum}, and quantum registers \cite{bradley2019ten}.
-Each center contains an electron spin that can be controlled directly with microwaves, aligned and read via optics. 
-The key element for most applications is that they could be coupled through the hyperfine coupling to the bath of numerous nuclear spins presenting a long living quantum memories and could present a nuclear spin qubit register.
+
+Each center contains an electron spin that can be controlled directly with microwaves, initialised and read out via optical excitation. 
+The key element for most applications is that they could be coupled through the hyperfine coupling to the bath of numerous nuclear spins presenting a long living quantum memories and could present an optically accessible nuclear spin qubit register.
 To design the efficient quantum control for the memories, a precise knowledge of the full hamiltonian of the register needs to be known and characterised before. 
-However, characterising the nuclear spin hyperfine coupling could be a challenge and a lengthy procedure.
+However, characterising the nuclear spin hyperfine coupling could be a challenging and a lengthy procedure \cite{taminuau27, taminiau50}. 
+Traditionally, nuclear spin characterisation is done with Optically Detected Magnetic Resonance (ODMR) \cite{Dreau, Neumann, Eriks}, however the spectroscopic resolution is limited to the $1/T_2^\ast$ of the electron spin.
+Hahn Echo type sequences have been used to refocus the electron spin and enhance the coherence time of the electron spin \cite{childress2006coherent} thus improving the resolution to $1/T_2$. 
+This method could be applied for the defects with a specific nuclear spins configuration \vvv{(which?)}. 
+\vvv{In particular, the certain relation to the magnetic field and the coupling of the nuclear spins should be kept, (weakly coupled nuclear spins), as well as the spin number of the electron spin is affecting the observed behaviour}
+Depending on the applied protocol for the nuclear spins characterization, the number of accessible nuclear spin can increase.
+Electron Spin Echo Envelop Modulation (ESEEM) types of sequences allow us to access the highest number of nuclear spins since the spectroscopy resolution is limited to the longitudinal relaxation time ($T_1$) of the system (see fig.
+\ref{fig:1}) \cite{Laraui, Vorobyov}.
+In particular we consider following common examples of nuclear spin registers ubiquitios in the applications.
+First, NV-like case with S=1, and weakly coupled nuclear spins, at high mangetic field such that $\gamma_n B \gg A_{zx}$.
+This case is very well studied in the works of \cite{Tam27, Tam2012, Tam2014, Wrachtrup, before}.
+The ability to see narrow peaks with analytically predictable position and contrast allows one to solve the inverse problem of characterising the coupling of the nuclear spins to the electron spins. 
+The second case (see in Fig. \ref{fig1b}) refers to a similar case but with a strongly coupled nuclear spin, which hinders the observation of a weakly coupled nuclear spins. 
+This case in particular  is relevant for the case, where additional to the weakly coupled register a strongly coupled nuclear spin is used for e.g.
+repetitive  enhancment of the readout, via using the strongly coupled ancilla resolved in electron spin resonance spectra.
+The third case (Fig.
+1c) is relevant for the S=1/2 case, where due to the lack of the offset in the average evolution of the nuclear spin, its dynamics weakly depends on the Azz and only in the second order on the Azx \cite{suckachev}.
+This leads to a poor distinguising ability of multiple nuclear spins and as a result lack of individual addressability of nuclear spins. 
+Finally, in the case of other materials host platforms, a bispecies nuclear spin bath could be observed, where the resonance peaks referrring to different larmour frequencies of different species additionaly complicate the reconstruction of the hamiltonian, and for unambiguous reconstruction of the interactions, additionall measurements e.g.
+at different B field would be needed.
+In this work we argue that a correlation type sequence, based on 5p eseem could serve as a general framework as it promisses greate reconstruction potential for all above mentioned cases.
 
-is necessary for enlarging the quantum register and precise description of the electron spin dynamics.
-Traditionally, nuclear spin characterisation is done with Optically Detected Magnetic Resonance (ODMR) (ref to Phillip Neumann's works), however the spectroscopic resolution is limited to the $T_2^\ast$ of the electron spin.
-Hence, some sequence is needed to increase the resolution.
-People have used Hahn Echo sequence to refocus the electron spin and enhance the coherence time of the electron spin \cite{childress2006coherent}.
-But this method only works for defects with a specific nuclear spins configuration.
-Depending on the applied protocol for nuclear spins characterization, the number of accessible nuclear spin can increase.
-Electron Spin Echo Envelop Modulation (ESEEM) types of sequences allow us to access the highest number of nuclear spins since the spectroscopy resolution is limited to the longitudinal relaxation time ($T_1$) of the system (see fig.
-\ref{fig:1}).
 \begin{figure*}%[htbp]
@@
 Where $\Delta = \omega_a - \omega_{mw}$ is the detuning, $\omega_L^{(k)} =\gamma_n^{(k)} B$ is nuclear Rabi frequency with $\gamma_n^{(k)}$ nuclear spin gyromagnetic ratio and $B$ external magnetic field, $A_{zz}, A_{zx}$ parallel and perpendicular secular component of hyperfine tensor.
-This Hamiltonian results that depending on the electron spin sublevel $s_i$ ($i=0,1$), the nuclear spin rotate with the resonance frequency of $\omega_i = \sqrt{(\omega_L + s_i A_{zz})^2+ (s_i A_{zx})^2}$, $i=0,1$ along the axes $\vec{n}_i =(\frac{s_i A_{zx}}{\omega_i}, 0, \frac{\omega_L + s_i A_{zz}} {\omega_i})$.
+The Hamiltonian is diagonal in the electron spin subspace, thus the hamiltonian for the nuclear spins could be rewritten in electron spin subdomains $s_i$ ($i=0,1$).
+The nuclear spin hamiltonian could be solved for eigenenergies, which determine the precession frequencies of $\omega_i = \sqrt{(\omega_L + s_i A_{zz})^2+ (s_i A_{zx})^2}$, $i=0,1$ along the eigenvector axes $\vec{n}_i =(\frac{s_i A_{zx}}{\omega_i}, 0, \frac{\omega_L + s_i A_{zz}} {\omega_i})$.
 It is assumed that the pulse duration $t_p$ are short enough ($\omega_L t_p \ll 1$) that the nuclear spin dynamics during this time is negligible.
-The most simplest characterization sequence is Ramsey.
-\\ The Ramsey signal can be obtained as follows:
+For completeness we start our analysis with the simplest characterization sequence, which is the electron spin ramsey sequence (free induction decay of electron) (see Appendix for derivation).
+The Ramsey signal can be obtained as follows:
 \begin{gather}
@@
 	(\vec{n_0}\cdot \vec{n_1})\sin(\frac{\omega_0 \tau}{2}) \sin(\frac{\omega_1 \tau}{2}) \Big]^{(k)}
-	\textcolor{gray}{e^{-\frac{\tau}{T_2^\ast}}}
+	\textcolor{gray}{e^{-(\frac{\tau}{T_2^\ast})^m}}
 \end{gather}	
@@
 Where $k = \frac{(s_1-s_0)\omega_L A_{zx}}{\omega_0 \omega_1}$ is the modulation amplitude of each nuclear spin.  
-We know that without any nuclear spin, Hahn Echo sequence creates the electron spin echo signal with the envelope of exponential decay with $T_2^{HE}$.
+Without any nuclear spin, Hahn Echo sequence creates the electron spin echo signal with the envelope of stretched exponential decay with $T_2^{HE}$. 
 However in the presence of nuclear spins, the electron spin echo envelope will be modulated due to interaction with nuclei. 
@@
 Hahn Echo sequence can be used for defects that contain a few strongly coupled nuclei.
-In order to differentiate the resonance frequency of each nuclear spin or make the oscillation sharper, one has to add more $\pi$ pulses and for the so-called Dynamical Decoupling sequence:
-Finally, the signal for dynamical decoupling is obtained:
-\small 
+In order to differentiate the resonance frequency of each nuclear spin or make the oscillation sharper, one can to add more $\pi$ pulses and for the so-called Dynamical Decoupling sequence to sharpen the resonance conditions (neglecting decoherence terms):
 \begin{gather}
@@
 \end{figure*}
+In this work, we take the 23 nuclear spins cluster characterized in paper \cite{abobeih2019atomic} as a realistic case. 
+First, we apply this to the dynamical decoupling sequence, and visualise the obtained results. 
 Fig \ref{fig:3} compares DD signal for the same nuclear spin register but different defects in diamond. 
-We present a handwavy definition for the sensitivity of a sequence to the variation of hyperfine coupling.
+An intuitive description for the sensitivity of a sequence to the variation of hyperfine coupling could estimated knowing the width and sensitivity of the position of the resonances. 
 First, we consider the case of NV center in diamond. 
-By knowing the width of a dip $\delta \tau = \frac{A_{zx}}{\omega_L^2}$  and taking the derivative of the resonance time, we define the sensitivity of longitudinal hyperfine coupling as follows:
+The width of a dip $\delta \tau = \frac{A_{zx}}{\omega_L^2}$  and taking the derivative of the resonance time, we define the sensitivity of longitudinal hyperfine coupling as follows:
 \begin{gather}

### 2023-08-30 article.tex
sent to jörg

@@
 Nuclear spins in solids is one of the most promising platforms for realisation of a scalable quantum hardware.
-They could be efficiently adressed at single site level by nearby single colour centers via the spin resonance.
+They could be efficiently addressed at single site level by nearby single colour centers via the spin resonance.
 However, characterising each nuclear spin is quite cumbersome as the characterisation protocol may differ depending on the strength of the hyperfine coupling.
@@
 \vvv{In particular, the certain relation to the magnetic field and the coupling of the nuclear spins should be kept, (weakly coupled nuclear spins), as well as the spin number of the electron spin is affecting the observed behaviour}
-Depending on the applied protocol for the nuclear spins characterization, the number of accessible nuclear spin can increase.
+Depending on the applied protocol for the nuclear spins characterisation, the number of accessible nuclear spin can increase.
 Electron Spin Echo Envelop Modulation (ESEEM) types of sequences allow us to access the highest number of nuclear spins since the spectroscopy resolution is limited to the longitudinal relaxation time ($T_1$) of the system (see fig.
 \ref{fig:1}) \cite{Laraui, Vorobyov}.
-In particular we consider following common examples of nuclear spin registers ubiquitios in the applications.
-First, NV-like case with S=1, and weakly coupled nuclear spins, at high mangetic field such that $\gamma_n B \gg A_{zx}$.
+In particular we consider following common examples of nuclear spin registers ubiquitous in the applications.
+First, NV-like case with S=1, and weakly coupled nuclear spins, at high magnetic field such that $\gamma_n B \gg A_{zx}$.
 This case is very well studied in the works of \cite{Tam27, Tam2012, Tam2014, Wrachtrup, before}.
 The ability to see narrow peaks with analytically predictable position and contrast allows one to solve the inverse problem of characterising the coupling of the nuclear spins to the electron spins. 
-The second case (see in Fig. \ref{fig1b}) refers to a similar case but with a strongly coupled nuclear spin, which hinders the observation of a weakly coupled nuclear spins. 
+The second case (see in Fig. \ref{fig:1}b) refers to a similar case but with a strongly coupled nuclear spin, which hinders the observation of a weakly coupled nuclear spins. 
 This case in particular  is relevant for the case, where additional to the weakly coupled register a strongly coupled nuclear spin is used for e.g.
-repetitive  enhancment of the readout, via using the strongly coupled ancilla resolved in electron spin resonance spectra.
+repetitive  enhancement of the readout, via using the strongly coupled ancilla resolved in electron spin resonance spectra.
 The third case (Fig.
-1c) is relevant for the S=1/2 case, where due to the lack of the offset in the average evolution of the nuclear spin, its dynamics weakly depends on the Azz and only in the second order on the Azx \cite{suckachev}.
-This leads to a poor distinguising ability of multiple nuclear spins and as a result lack of individual addressability of nuclear spins. 
-Finally, in the case of other materials host platforms, a bispecies nuclear spin bath could be observed, where the resonance peaks referrring to different larmour frequencies of different species additionaly complicate the reconstruction of the hamiltonian, and for unambiguous reconstruction of the interactions, additionall measurements e.g.
+1c) is relevant for the S=1/2 case, where due to the lack of the offset in the average evolution of the nuclear spin, its dynamics weakly depends on the Azz and only in the second order on the $A_{zx}$ \cite{suckachev}.
+This leads to a poor distinguishing ability of multiple nuclear spins and as a result lack of individual addressability of nuclear spins. 
+Finally, in the case of other materials host platforms, a bispecies nuclear spin bath could be observed, where the resonance peaks referring to different Larmour frequencies of different species additionally complicate the reconstruction of the hamiltonian, and for unambiguous reconstruction of the interactions, additional measurements e.g.
 at different B field would be needed.
-In this work we argue that a correlation type sequence, based on 5p eseem could serve as a general framework as it promisses greate reconstruction potential for all above mentioned cases.
+In this work we argue that a correlation type sequence, based on 5p eseem could serve as a general framework as it promises great reconstruction potential for all above mentioned cases.
 
@@
 		\includegraphics[width=0.9\textwidth]{pict/drawing0.pdf}
-		\caption{Comparing DD and 5pESEEM as two nuclear spin characterization method in different systems.
+		\caption{Comparing DD and 5pESEEM as two nuclear spin characterisation method in different systems.
 a.
@@
 A system containing two different nuclear spin species: two nuclear spin bath can interfere in the DD signal, which makes the signal analysis more challenging.
-However, the species can be inferred from ESEEM signal since species have different Larmor frequencies.}
+However, the species can be inferred from ESEEM signal since species have different Larmour frequencies.}
 		\label{fig:1}
@@
 spin one-half system.
-Simulated Fisher information for the case of the electron spin c.
+Simulated Fisher information matrix for the case of the electron spin c.
 one d.
@@
 \end{equation}
-For the presented protocol, the precision for various spins is limited by 0.09 Hz for the S=1, for the N = 4000. \\
-
+For the presented protocol, the precision for various spins is limited by 0.09 Hz \vvv{Hz squared?} for the S=1, for the N = 4000, while for the S=1/2 the value of the Cramer-Rao bound reads as \vvv{XXX} which is \vvv{YYYY} time smaller.
+\\
 The striking difference to the $S=1$ fisher information matrix, is the behaviour of the defect with $S=1/2$.
-
-On the other hand, a sequence that is limited by $T_1$ instead of $T_2$ is based on 3 and 5-pulse ESEEM.
+First of all, for both spin S=1/2 and S=1, the sequence spectral resolution is limited with $T_1$ relaxation time of the electron spin. 
+On the other hand, a sequence sensitivity is limited by $T_2$. 
 The main principle of 5-pulse ESEEM \cite{kasumaj20085} is to create an entanglement (via e.g.
-Hahn-echo block) before the free evolution of the nuclear spins and after make a second correlating sequence.
+Hahn-echo or CPMG block) before the free evolution of the nuclear spins and after make a second correlating sequence.
 In other words, change the initial density matrix for the Ramsey sequence from such that entanglement already exist in the electron polarization terms of the density matrix, thus limitied by $T_1$ time.
@@
 Zooming into area close to the Larmor frequency reveals the weakly coupled nuclei. 
-Each nuclear spins have two peaks in the spectrum. 
+Each nuclear spins have two peaks in the spectrum refering to the $\omega_a$ and $\omega_b$. 
 Expanding the resonance frequencies up to first order with respect to hyperfine coupling results that the weakly coupled nuclei keep their order as they go further away from the nuclei. 
@@
 However, this method is rather time-consuming as two time variables has to be swept.
-We suggest sweeping $\tau$ parameter and keep the track of frequency amplitude as a function of $\tau$. 
+The optimum time sampling techniques might be used to optimise the time of 2D sampling.  
+Here we suggest an alternative way, which in conventional ESR is used, i.e. sweeping $\tau$ parameter and keep the track of frequency amplitude as a function of $\tau$. 
 Two frequencies that belong to the same nuclear are correlated because the modulation depth oscillates with blind spot terms of both frequencies $\sin^2(\frac{\omega_0 \tau}{2}) \sin^2(\frac{\omega_1 \tau}{2})$.
@@
 \\
-
-Here, we try to simulate the realistic situation.
-First, the electron spin state is projected to 0 and 1 with a binomial distribution, the probability determined by the theoretical signal.
+To simulate the realistic experimental situation we model the electron spin state is projected to 0 and 1 with a binomial distribution where the probability determined by the analytical expressions.
 Then, we assume the bright (dark) state emits 3 (0.1) photons on average with a Poissonian distribution.
-We repeat the measurement at each point for 10000 times to reduce classical noise.\\
-How many nuclear spin is identifiable with this method? It depends on the duration of free evolution time and the choice of inter-pulse timing $\tau$.
+We repeat the measurement at each point for 10000 times to reduce the classical photon shot noise.\\
+Next we approach estimation of number of nuclear spins, which could be identified.
+It depends on the duration of free evolution time and the choice of inter-pulse timing $\tau$.
 
@@
 
-\section{Conclusion}
+\section{Discussion}
 \label{sec:discussion}

### 2024-01-30 article.tex

@@
 In some cases, e.g.
-for spin 1/2, strongly coupled spins, and bispecies bath this protocol contains severe problems in applying for the nuclear spin bath characterisation.
+for spin 1/2, strongly coupled spins, and bispecies bath this protocol suffers severe problems when applied for the nuclear spin bath characterisation.
 Here, we present a more straight forward method to obtain hyperfine interaction among nuclear spins and the electron spin. 
 This method can be used for a variety of platform including emerging S=1/2 group IV defects in diamond (e.g. SiV, GeV, SnV, PbV) or Silicon vacancy in Silicon Carbide.
-We summarize theoretical framework and adopt it from ESR for the use in colour centers with various spins, and numerically consider case of nuclear spin cluster, as compare performance of various protocols on this example via the Fisher information matrix.
+We summarize theoretical framework and adopt it from ESR for the use in colour centers with various spins, and numerically consider case of nuclear spin cluster for performance comparison of various protocols on this example via the Fisher information matrix as a metric.
 \end{abstract}
@@
 %\subsection{Advanced filters}
-Here is the concise conclusion @Vadim
+Here is the concise conclusion
 

### 2024-01-30 article.tex
text

--- 2023-08-30 article.tex
@@
 \author{Majid Zahedian}
- \affiliation{3rd physical institute University of Stuttgart, Germany}
-  %\affiliation{Max Planck School of Photonics, Germany}%Lines b%Lines break automatically or can be forced with \\
+ \affiliation{3rd Physical Institute University of Stuttgart, Germany}
+ \affiliation{Institute of Quantum Electronics, ETH Z\"urich, Switzerland}%Lines b%Lines break automatically or can be forced with \\
 
@@
 \email[]{v.vorobyov@pi3.uni-stuttgart.de}
- \affiliation{3rd physical institute University of Stuttgart, Germany}  
+ \affiliation{3rd Physical Institute University of Stuttgart, Germany}  
 % with \\
@@
 \author{J\"org Wrachtrup}
- \affiliation{3rd physical institute University of Stuttgart, Germany}%Lines break 
+ \affiliation{3rd Physical Institute University of Stuttgart, Germany}%Lines break 
  \affiliation{Max Planck Institute for solid state physics, Stuttgart, Germany}%Lines break 
@@
 \begin{abstract}
-Nuclear spins in solids is one of the most promising platforms for realisation of a scalable quantum hardware.
-They could be efficiently adressed at single site level by nearby single colour centers via the spin resonance.
-However, characterising each nuclear spin is quite cumbersome as the characterisation protocol may differ depending on the strength of the hyperfine coupling.
-The most adopted protocol is modified electron spin Hahn-echos such as CPMG and XY8 pulse sequences.
-In some cases, e.g.
-for spin 1/2, strongly coupled spins, and bispecies bath this protocol contains severe problems in applying for the nuclear spin bath characterisation.
-Here, we present a more straight forward method to obtain hyperfine interaction among nuclear spins and the electron spin. 
-This method can be used for a variety of platform including emerging S=1/2 group IV defects in diamond (e.g. SiV, GeV, SnV, PbV) or Silicon vacancy in Silicon Carbide.
-We summarize theoretical framework and adopt it from ESR for the use in colour centers with various spins, and numerically consider case of nuclear spin cluster, as compare performance of various protocols on this example via the Fisher information matrix.
+Nuclear spins in solids offer a promising avenue for developing scalable quantum hardware.
+Leveraging nearby single-color centers, these spins can be efficiently addressed at the single-site level through spin resonance.
+However, characterising individual nuclear spin is quite cumbersome since the utility of characterisation protocols may differ depending on the strength of the hyperfine coupling, necessitating tailored characterization protocols.
+While modified electron spin Hahn echoes like CPMG and XY8 pulse sequences are commonly employed, they encounter significant limitations in scenarios involving spin-1/2 systems, strongly coupled spins, or nuclear spin baths comprising distinct isotopes.
+Here, we present a more straightforward approach for determining the hyperfine interactions among each nuclear and the electron spin. 
+This method holds promise across diverse platforms, including emerging S=1/2 group IV defects in diamond (e.g., SiV, GeV, SnV, PbV) or silicon vacancies in silicon carbide. 
+We provide a theoretical framework and adapt it for use with color centers exhibiting various spins.
+Through simulations conducted on nuclear spin clusters, we evaluate different protocols and compare their performance using the Fisher information matrix.
 \end{abstract}
@@
 \section{Introduction and background}
-Optically active defects in solids, color centers, has been applied for realising different quantum applications \cite{awschalom2018quantum}, such as a quantum network \cite{pompili2021realization}, quantum sensing \cite{degen2017quantum}, and quantum registers \cite{bradley2019ten}.
+Optically active defects in solids, known as color centers, have been utilized in various quantum applications \cite{awschalom2018quantum}, including quantum networks \cite{pompili2021realization}, quantum sensing \cite{degen2017quantum}, and quantum registers \cite{bradley2019ten}.
 
-Each center contains an electron spin that can be controlled directly with microwaves, initialised and read out via optical excitation. 
-The key element for most applications is that they could be coupled through the hyperfine coupling to the bath of numerous nuclear spins presenting a long living quantum memories and could present an optically accessible nuclear spin qubit register.
-To design the efficient quantum control for the memories, a precise knowledge of the full hamiltonian of the register needs to be known and characterised before. 
-However, characterising the nuclear spin hyperfine coupling could be a challenging and a lengthy procedure \cite{taminuau27, taminiau50}. 
-Traditionally, nuclear spin characterisation is done with Optically Detected Magnetic Resonance (ODMR) \cite{Dreau, Neumann, Eriks}, however the spectroscopic resolution is limited to the $1/T_2^\ast$ of the electron spin.
-Hahn Echo type sequences have been used to refocus the electron spin and enhance the coherence time of the electron spin \cite{childress2006coherent} thus improving the resolution to $1/T_2$. 
-This method could be applied for the defects with a specific nuclear spins configuration \vvv{(which?)}. 
-\vvv{In particular, the certain relation to the magnetic field and the coupling of the nuclear spins should be kept, (weakly coupled nuclear spins), as well as the spin number of the electron spin is affecting the observed behaviour}
-Depending on the applied protocol for the nuclear spins characterization, the number of accessible nuclear spin can increase.
-Electron Spin Echo Envelop Modulation (ESEEM) types of sequences allow us to access the highest number of nuclear spins since the spectroscopy resolution is limited to the longitudinal relaxation time ($T_1$) of the system (see fig.
+Each center contains an electron spin that can be directly controlled using microwaves, and it can be initialized and read out through optical excitation. 
+The potential hyperfine interactions with a bath of numerous nuclear spins are crucial for diverse applications, as they offer long-lived quantum memories and enable the creation of an optically accessible nuclear spin qubit register.
+To implement efficient quantum control for these memories, it is imperative to have precise knowledge of the full Hamiltonian governing the register.
+However, characterizing the hyperfine coupling of nuclear spins can be both challenging and time-consuming \cite{abobeih2019atomic, van2023mapping}. 
+Traditionally, nuclear spin characterization is accomplished through Optically Detected Magnetic Resonance (ODMR) \cite{Dreau, Neumann, Eriks}, but the spectroscopic resolution is constrained by the $1/T_2^\ast$ of the electron spin.
+To overcome this limitation, Hahn-Echo-type sequences have been employed to refocus the electron spin and extend its coherence time \cite{childress2006coherent}, thereby improving the resolution to $1/T_2$.
+This method could be applied to defects with a specific configuration of nuclear spins, particularly those with a certain relation to the magnetic field and the coupling of the nuclear spins, such as weakly coupled nuclear spins.
+Also, the protocols also can only be applied to electron spins with a specific spin multiplicity
+Depending on the applied protocol for the nuclear spins characterisation, the number of identifiable nuclear spin can increase.
+Electron Spin Echo Envelop Modulation (ESEEM) types of sequences allow access to the highest number of nuclear spins, as the spectroscopy resolution is limited to the longitudinal relaxation time ($T_1$) of the system.
+(see fig.
 \ref{fig:1}) \cite{Laraui, Vorobyov}.
-In particular we consider following common examples of nuclear spin registers ubiquitios in the applications.
-First, NV-like case with S=1, and weakly coupled nuclear spins, at high mangetic field such that $\gamma_n B \gg A_{zx}$.
-This case is very well studied in the works of \cite{Tam27, Tam2012, Tam2014, Wrachtrup, before}.
-The ability to see narrow peaks with analytically predictable position and contrast allows one to solve the inverse problem of characterising the coupling of the nuclear spins to the electron spins. 
-The second case (see in Fig. \ref{fig1b}) refers to a similar case but with a strongly coupled nuclear spin, which hinders the observation of a weakly coupled nuclear spins. 
-This case in particular  is relevant for the case, where additional to the weakly coupled register a strongly coupled nuclear spin is used for e.g.
-repetitive  enhancment of the readout, via using the strongly coupled ancilla resolved in electron spin resonance spectra.
+In particular, we consider the following common examples of nuclear spin registers that are ubiquitous in applications.
+First, the NV-like case with S=1 and weakly coupled nuclear spins, operating at high magnetic fields where $\gamma_n B \gg A_{zx}$ which has been extensively studied in the works of \cite{abobeih2019atomic, taminiau2012detection, Tam2014, Wrachtrup, before}.
+The capability to observe narrow peaks with analytically predictable positions and contrasts enables the solution of the inverse problem concerning the characterization of the coupling between nuclear spins and electron spins.
+The second case (as depicted in Fig.
+\ref{fig:1}b) corresponds to a scenario similar to the first, but with the presence of a strongly coupled nuclear spin, which obstructs the observation of weakly coupled nuclear spins.
+This case is particularly relevant in situations where, in addition to the weakly coupled register, a strongly coupled nuclear spin is utilized, for instance, for repetitive enhancement of the readout.
+This enhancement is achieved by exploiting the strongly coupled ancilla, which is discernible in electron spin resonance spectra.
 The third case (Fig.
-1c) is relevant for the S=1/2 case, where due to the lack of the offset in the average evolution of the nuclear spin, its dynamics weakly depends on the Azz and only in the second order on the Azx \cite{suckachev}.
-This leads to a poor distinguising ability of multiple nuclear spins and as a result lack of individual addressability of nuclear spins. 
-Finally, in the case of other materials host platforms, a bispecies nuclear spin bath could be observed, where the resonance peaks referrring to different larmour frequencies of different species additionaly complicate the reconstruction of the hamiltonian, and for unambiguous reconstruction of the interactions, additionall measurements e.g.
-at different B field would be needed.
-In this work we argue that a correlation type sequence, based on 5p eseem could serve as a general framework as it promisses greate reconstruction potential for all above mentioned cases.
+1c) pertains to the S=1/2 scenario, where the lack of offset in the average evolution of the nuclear spin results in its dynamics weakly depending on Azz and only in the second order on $A_{zx}$ \cite{suckachev}.
+Consequently, this leads to a limited ability to distinguish between multiple nuclear spins and, consequently, a lack of individual addressability of nuclear spins.
+Lastly, in the case of other material host platforms, a bispecies nuclear spin bath may be observed, where resonance peaks corresponding to different Larmor frequencies of different species further complicate the reconstruction of the Hamiltonian.
+For unambiguous reconstruction of the interactions, additional measurements, such as those at different magnetic field strengths, would be required.
+In this work, we propose that a correlation-type sequence, based on five pulse ESEEM, could serve as a general framework as it holds promise for the reconstruction of the interactions in all of the aforementioned cases.
 
-\begin{figure*}%[htbp]
+\begin{figure*}%[htb]
 	\begin{center}
 		\includegraphics[width=0.9\textwidth]{pict/drawing0.pdf}
-		\caption{Comparing DD and 5pESEEM as two nuclear spin characterization method in different systems.
+		\caption{Comparing DD and five pulse ESEEM as two nuclear spin characterization methods in different systems.
 a.
-An electron spin one system: in DD signal, each nuclear spin has a distinct resonance time up to first order of $A_{zz}$; the accuracy of the obtained hyperfine interaction is limited to $T_2$ of the electron spin.
-In the Fourier transform of the ESEEM signal, the two resonance frequency of each spin is present; the accuracy of the obtained hyperfine interaction is limited to $T_1$ of the electron spin b.
-An electron spin one system with two strongly coupled nuclear spins and many weakly coupled spins.
-No resonance time is detectable since the required condition for DD ($\omega_L \gg A_{zz}, A{zx}$) does not hold.
-However, resonant frequencies is still obtainable in the ESEEM signal c.
-An electron spin one half system: nuclear spins have more or less the same resonance time as it depends on the second order of hyperfine coupling.
-However, resonant frequency of each spins is distinguishable in the ESEEM signal.
+Electron spin one system: In the DD signal, each nuclear spin exhibits a distinct resonance time up to the first order of $A_{zz}$; the accuracy of the obtained hyperfine interaction is limited to $T_2$ of the electron spin.
+In the Fourier transform of the ESEEM signal, the two resonance frequencies of each spin are present; the accuracy of the obtained hyperfine interaction is limited to $T_1$ of the electron spin.
+b.
+Electron spin 1 system with two strongly coupled nuclear spins and many weakly coupled spins: No resonance time is detectable since the required condition for DD ($\omega_L \gg A_{zz}, A_{zx}$) does not hold.
+However, resonant frequencies are still obtainable in the ESEEM signal.
+c.
+Electron spin 1/2 system: Nuclear spins have more or less the same resonance time as it depends on the second order of hyperfine coupling.
+However, the resonant frequency of each spin is distinguishable in the ESEEM signal.
 d.
-A system containing two different nuclear spin species: two nuclear spin bath can interfere in the DD signal, which makes the signal analysis more challenging.
-However, the species can be inferred from ESEEM signal since species have different Larmor frequencies.}
+System containing two different nuclear spin species: Two nuclear spin baths can interfere in the DD signal, making the signal analysis more challenging.
+However, the species can be inferred from the ESEEM signal since species have different Larmor frequencies.}
 		\label{fig:1}
@@
 %%%%%%%%%%%%%%%Í%%%%=================
-We consider a central spin system of \textit{non-interacting} nuclear spins $I=1/2$ coupled to the central electron spin $\boldmath{S}$. 
-The central electron spin is manipulated resonantly with the microwave pulses, which transfer the population between the two sublevels, denoted as $m_s=s_0$ and $m_s = s_1$. 
-These two spin sublevels are separated, due to the Zeeman effect and/or zero field splitting, and form an two-level subsystem with energy splitting of $\omega_a$. 
+We consider a central spin system of \textit{non-interacting} nuclear spins $I=1/2$ coupled to the central electron spin $\boldsymbol{S}$.
+The central electron spin is manipulated resonantly with microwave pulses, which transfer the population between the two sublevels denoted as $m_s=s_0$ and $m_s = s_1$.
+These two spin sublevels are separated due to the Zeeman effect and/or zero-field splitting, forming a two-level subsystem with an energy splitting of $\omega_a$.
 The Hamiltonian of the system in the secular approximation and in the rotating frame of the applied microwave $\omega_{mw}$ can be written as:
@@
 \end{align}
-Where $\Delta = \omega_a - \omega_{mw}$ is the detuning, $\omega_L^{(k)} =\gamma_n^{(k)} B$ is nuclear Rabi frequency with $\gamma_n^{(k)}$ nuclear spin gyromagnetic ratio and $B$ external magnetic field, $A_{zz}, A_{zx}$ parallel and perpendicular secular component of hyperfine tensor.
-The Hamiltonian is diagonal in the electron spin subspace, thus the hamiltonian for the nuclear spins could be rewritten in electron spin subdomains $s_i$ ($i=0,1$).
-The nuclear spin hamiltonian could be solved for eigenenergies, which determine the precession frequencies of $\omega_i = \sqrt{(\omega_L + s_i A_{zz})^2+ (s_i A_{zx})^2}$, $i=0,1$ along the eigenvector axes $\vec{n}_i =(\frac{s_i A_{zx}}{\omega_i}, 0, \frac{\omega_L + s_i A_{zz}} {\omega_i})$.
-It is assumed that the pulse duration $t_p$ are short enough ($\omega_L t_p \ll 1$) that the nuclear spin dynamics during this time is negligible.
-For completeness we start our analysis with the simplest characterization sequence, which is the electron spin ramsey sequence (free induction decay of electron) (see Appendix for derivation).
+Where $\Delta = \omega_a - \omega_{mw}$ is the detuning, $\omega_L^{(k)} =\gamma_n^{(k)} B$ is the nuclear Rabi frequency with $\gamma_n^{(k)}$ being the nuclear spin gyromagnetic ratio and $B$ the external magnetic field, and $A_{zz}$ and $A_{zx}$ are the parallel and perpendicular secular components of the hyperfine tensor, respectively.
+The Hamiltonian is diagonal in the electron spin subspace, thus the Hamiltonian for the nuclear spins could be rewritten in the electron spin subdomains $s_i$ ($i=0,1$).
+The nuclear spin Hamiltonian could be solved for eigenenergies, which determine the precession frequencies of $\omega_i = \sqrt{(\omega_L + s_i A_{zz})^2+ (s_i A_{zx})^2}$, $i=0,1$ along the eigenvector axes $\vec{n}i =(\frac{s_i A{zx}}{\omega_i}, 0, \frac{\omega_L + s_i A_{zz}} {\omega_i})$.
+It is assumed that the pulse duration $t_p$ is short enough ($\omega_L t_p \ll 1$) that the nuclear spin dynamics during this time is negligible.
+For completeness, we start our analysis with the simplest characterization sequence, which is the electron spin Ramsey sequence (free induction decay of the electron) (see the Appendix for derivation).
 The Ramsey signal can be obtained as follows:
 \begin{gather}
-	\expval{\sigma_z}_{Ram} = \cos(\Delta \tau) \prod_{k=1}^{n} \Big[ \cos(\frac{\omega_0 \tau}{2}) \cos(\frac{\omega_1 \tau}{2})+ \notag \\
-	(\vec{n_0}\cdot \vec{n_1})\sin(\frac{\omega_0 \tau}{2}) \sin(\frac{\omega_1 \tau}{2}) \Big]^{(k)}
+	\expval{\sigma_z}_{Ram} = \cos(\Delta \tau) \prod_{j=1}^{n} \Big[ \cos(\frac{\omega_0 \tau}{2}) \cos(\frac{\omega_1 \tau}{2})+ \notag \\
+	(\vec{n_0}\cdot \vec{n_1})\sin(\frac{\omega_0 \tau}{2}) \sin(\frac{\omega_1 \tau}{2}) \Big]^{(j)}
 	\textcolor{gray}{e^{-(\frac{\tau}{T_2^\ast})^m}}
 \end{gather}	
-We do not take any relaxation process into account and the gray exponential decay is put by hand to remember the relaxation time scale.
-Ramsey signal decay with electron spin $T_2^\ast$, so it can be used to observe the core of the defect.
-Ramsey sequence is sensitive to detuning since the electron spin is not refocused, however it is possible to sense nuclear spins with vanishing perpendicular hyperfine coupling.\\
+The exponential decay is introduced to note the Ramsey signal decays with the electron spin $T_2^\ast$ since the formalism does not account for any relaxation processes.
+The Ramsey sequence is sensitive to detuning since the electron spin is not refocused; however, it is possible to sense nuclear spins with vanishing perpendicular hyperfine coupling.\\
 
-To enhance the relaxation time and have access to more nuclei, one can add a $\pi$ pulse in between the Ramsey sequence and create Hahn-echo sequence and obtain the following signal:
+To extend the relaxation time and access more nuclei, one can insert a $\pi$ pulse between the Ramsey sequence, creating a Hahn echo sequence, and obtain the following signal:
 \begin{gather}
@@
 Where $k = \frac{(s_1-s_0)\omega_L A_{zx}}{\omega_0 \omega_1}$ is the modulation amplitude of each nuclear spin.
-Without any nuclear spin, Hahn Echo sequence creates the electron spin echo signal with the envelope of stretched exponential decay with $T_2^{HE}$. 
-However in the presence of nuclear spins, the electron spin echo envelope will be modulated due to interaction with nuclei. 
-Hence, this sequence also called Electron Spin Echo Envelope Modulation or shortly ESEEM. 
+Without any nuclear spin, the Hahn Echo sequence creates an electron spin echo signal with an envelope of stretched exponential decay with $T_2^{HE}$.
+However, in the presence of nuclear spins, the electron spin echo envelope will be modulated due to interaction with the nuclei.
+Hence, this sequence is also called Electron Spin Echo Envelope Modulation or simply ESEEM.
 Even though the coherence time is increased, distinguishing the effect of different nuclear spins in the total signal is very complicated.
-Hahn Echo sequence can be used for defects that contain a few strongly coupled nuclei.
-In order to differentiate the resonance frequency of each nuclear spin or make the oscillation sharper, one can to add more $\pi$ pulses and for the so-called Dynamical Decoupling sequence to sharpen the resonance conditions (neglecting decoherence terms):
-\begin{gather}
+The Hahn Echo sequence can be used for defects that contain a few strongly coupled nuclei.
+In order to differentiate the resonance frequency of each nuclear spin or to sharpen the oscillations, one can add more $\pi$ pulses, creating the so-called Dynamical Decoupling sequence to separate the resonance condition for individual nuclear spin.
+For the even number of $\pi$ pulses, $N$, The DD signal can be obtained (neglecting decoherence terms):
+\begin{gather} \label{eq:DD}
 	\expval{\sigma_z}_{DD} =
@@
 \end{gather}
-$\vec{n}_0 \cdot \vec{n}_1 = \frac{\omega_L^2+(s_0+s_1)A_{zz}+s_0 s_1 (A_{zz}^2+A_{zx}^2)}{\omega_0 \omega_1}$ and $N$ is the number of $\pi$ pulses that must be an even. Each nuclear 
-If the magnetic field is high or all nuclear spins are weakly coupled such that $\omega_L \gg A_{zz}, A_{zx}$, the multiplication rule can be approximated by a summation rule, which makes the higher order resonance disappear:
+Where $\vec{n}_0 \cdot \vec{n}_1 = \frac{\omega_L^2+(s_0+s_1)A_{zz}+s_0 s_1 (A_{zz}^2+A_{zx}^2)}{\omega_0 \omega_1}$.
+At this point, it should be clear that the number of pulses can be used as an additional parameter to modify the modulation depth of each nuclear spin.
+A detailed investigation of the obtained DD signal reveals that by sweeping the time interval between pulses, an exponential decay with the rate of $1/T_2$ is observed, except for some resonance times where the electron spin becomes entangled with a particular nuclear spin, resulting in a sharp drop in the signal.
+This resonance time can be obtained assuming $\omega_L \gg A_{zz}, A_{zx}$ is satisfied: 
+\begin{gather} \label{eq:resonance}
+	\tau_p \approx  \frac{(2p+1) \pi}{\omega_0 + \omega_1} \approx \frac{(2p+1)\pi}{2\omega_L(1+\frac{s_0+s_1}{2} \frac{A_{zz}}{\omega_L}+ \frac{s_0^2+s_1^2}{4}\frac{A_{zx}^2}{\omega_L^2})}
+\end{gather}
+Experimental observation of the resonance times provides valuable information about the nuclear spins.
+For instance, in the case of an NV center, the second-order term $\frac{A_{zx}^2}{\omega_L^2}$ can be neglected, allowing for the direct determination of the $A_{zz}$ hyperfine component from the resonances.
+To proceed with the characterization, Eq. \ref{eq:DD} needs to be further simplified, requiring stronger assumptions.
+Focusing on weakly coupled nuclear spins or high magnetic field situations, the multiplication rule can be approximated by a summation rule, neglecting the higher-order cross-resonance terms:
 \small
@@
 \normalsize
-The parallel component of the hyperfine interaction can be obtained from the resonance time of each nuclear spin:
+Assuming non-overlapping resonance times (which does not hold true for spin 1/2 systems) and expanding the signal around the j-th nuclear spin resonance ($\tau = \tau_p^{(j)}+\delta \tau$) up to the first order of $\delta \tau$ results in approximating each drop with a Lorentzian function:
+\small
 \begin{gather}
-	\tau_p \approx  \frac{(2p+1) \pi}{\omega_0 + \omega_1} \approx \frac{(2p+1)\pi}{2\omega_L(1+\frac{s_0+s_1}{2} \frac{A_{zz}}{\omega_L}+ \frac{s_0^2+s_1^2}{4}\frac{A_{zx}^2}{\omega_L^2})}
+	\expval{\sigma_z}_{DD} (\delta \tau ) \approx 1 -2\sin^2(\frac{N}{2}\frac{(s_1-s_0)A_{zx}}{\omega_L}) \frac{(\frac{(s_1-s_0)A_{zx}}{2\omega_L^2})^2}{{\delta \tau}^2 +(\frac{(s_1-s_0)A_{zx}}{2\omega_L^2})^2}
 \end{gather}
-The perpendicular part of hyperfine interaction can be obtained from a fit to the Lorentzian dip with the width of $\frac{(s_1-s_0)\omega_L A_{zx}}{(2p+1)\pi\omega_0 \omega_1}$ or varying the number of pulses and fitting the minima position to the formula $\expval{\sigma_z}_{DD}^{(k)} \approx 1- 2 \sin^2\big(\frac{N}{2}\frac{(s_1-s_0)\omega_L A_{zx}}{\omega_0 \omega_1}\big) $.
-Although Dynamical Decoupling (DD) sequence is well understood and used to characterize nuclear spins, it is not applicable for any system.
-First, DD only works for defects with high magnetic field and low hyperfine coupling ($\omega_L \gg A_{zz}, A_{zx}$).
-Second, the signal is limited to electron spin $T_2$, which is difficult to make it equal to $T_1$.
-Third, the signal analysis is rather complicated and time-consuming.
-(Maybe AI solves this problem in the future?) one has to collect enough data to make sure no two nuclear spin overlap in the signal.
-Forth, this sequence does not work for spin one half system, e.g., group IV defect in diamond, since parallel component of hyperfine coupling cancels their effect in the resonance time up to the first and second order.
-Hence, the resonance time depends on the second order of perpendicular component.
-In this work, we take 23 nuclear spin characterized in paper \cite{abobeih2019atomic} as a realistic case.
+\normalsize
+This simplification allows for the determination of the parallel component of the hyperfine interaction for each nuclear spin, possibly in two ways.
+First, a Lorentzian with a width of $\frac{(s_1-s_0) A_{zx}}{\omega_L^2}$ can be fitted to a dip to identify $A_{zx}$.
+Second, by keeping track of the minima of a dip while varying the number of pulses, the periodic function $1 - 2 \sin^2\big(\frac{N}{2}\frac{(s_1-s_0) A_{zx}}{\omega_L}\big)$ can be fitted to obtain $A_{zx}$.
+
+Although the Dynamical Decoupling (DD) sequence is well understood and used to characterize nuclear spins, it is not applicable to all systems.
+First, DD only works for defects with high magnetic fields and low hyperfine coupling ($\omega_L \gg A_{zz}, A_{zx}$).
+Second, the signal is limited to the electron spin $T_2$, which only gradually approaches $T_1$.
+Third, signal analysis is rather complicated and time-consuming; one has to collect enough data to ensure that no two nuclear spins overlap in the signal.
+Fourth, this sequence does not work for spin 1/2 systems, such as group IV defects in diamond, since the parallel component of the hyperfine coupling cancels their effect on the first order electron spin signal.
+Hence, the resonance signal depends on the second order of the perpendicular hyperfine component.
+
+In this work, we consider 23 nuclear spins characterized in paper \cite{abobeih2019atomic} as a realistic case.
 \begin{figure*}%[htbp]
@@
 		\includegraphics[width=0.9\textwidth]{pict/dd_compare2.pdf}
-		\caption{Simulated DD signal with 64 $\pi$-pulses for the register reported \cite{abobeih2019atomic} assuming the electron spin is a.
-spin one b.
-spin one-half system.
-Simulated Fisher information for the case of the electron spin c.
-one d.
-one-half system.}
+		\caption{Simulated DD signal with 64 $\pi$-pulses for the register reported in  \cite{abobeih2019atomic} assuming the electron spin is a.
+spin 1 system b.
+spin 1/2 system.
+Simulated Fisher information matrix for the case of the electron spin c.
+spin 1 system d.
+spin 1/2 system.}
 		\label{fig:3}
@@
 \end{figure*}
-In this work, we take the 23 nuclear spins cluster characterized in paper \cite{abobeih2019atomic} as a realistic case. 
-First, we apply this to the dynamical decoupling sequence, and visualise the obtained results. 
-Fig \ref{fig:3} compares DD signal for the same nuclear spin register but different defects in diamond. 
-An intuitive description for the sensitivity of a sequence to the variation of hyperfine coupling could estimated knowing the width and sensitivity of the position of the resonances. 
-First, we consider the case of NV center in diamond. 
-The width of a dip $\delta \tau = \frac{A_{zx}}{\omega_L^2}$  and taking the derivative of the resonance time, we define the sensitivity of longitudinal hyperfine coupling as follows:
+In this work, we consider the 23-nuclear spin cluster characterized in paper \cite{abobeih2019atomic} as a realistic case for our comparison.
+First, we apply this to the dynamical decoupling sequence and visualize the obtained results.
+Fig \ref{fig:3} compares the DD signal for the same nuclear spin register but different defects in diamond.
+An intuitive description of the sensitivity of a sequence to the variation of hyperfine coupling could be estimated by considering the width and sensitivity of the position of the resonances.
+First, we consider the case of an NV center in diamond.
+The width of a dip is $\delta \tau = \frac{A_{zx}}{\omega_L^2}$.
+Taking the derivative of the resonance time, we define the sensitivity of the longitudinal hyperfine coupling as follows, using Eq.
+\ref{eq:resonance} to simplify:
 \begin{gather}
-	\delta A_{zz} = \frac{\delta \tau}{\abs{\frac{\partial \tau_k}{\partial A_{zz}}}} = \frac{2}{\tau_k} \frac{A_{zx}}{\omega_L} \ge \frac{4}{T_2^{HE}} \frac{A_{zx}}{\omega_L}
+	\delta A_{zz} \equiv \frac{\delta \tau}{\abs{\frac{\partial \tau_p}{\partial A_{zz}}}} = \frac{2}{\tau_p} \frac{A_{zx}}{\omega_L} \ge \frac{4}{T_2^{HE}} \frac{A_{zx}}{\omega_L}
 \end{gather}
-If we assume the typical values of $T_2^{HE} = 100 $ $\mu$s and $\omega_L=500 $ kHz, a weakly coupled nuclear spin $A_{zx}=5$ kHz can be distinguished from another weakly coupled nuclear spin with $\delta A_{zz} = 400$ Hz.
-For $S=1/2$, e.g. for group IV defects in diamond, the resonance times is sensitive to the second order of $A_{zx}$ and no sensitivity to $A_{zz}$. 
-Hence, even at large $\tau$ the resonances related to nuclear spins will not be separated well. 
-We define the sensitivity for the spin one half system as follows:
+If we assume typical values of $T_2^{HE} = 100$ $\mu$s and $\omega_L=500$ kHz, a weakly coupled nuclear spin $A_{zx}=5$ kHz can be distinguished from another weakly coupled nuclear spin with $\delta A_{zz} = 400$ Hz.
+For $S=1/2$, such as group IV defects in diamond, the resonance times are sensitive to the second order of $A_{zx}$ and show no sensitivity to $A_{zz}$.
+Hence, even at large $\tau$, the resonances related to nuclear spins will not be well separated.
+We define the sensitivity for the spin one-half system as follows:
 \begin{gather}
-	\delta A_{zx} = \frac{\delta \tau}{\abs{\frac{\partial \tau_k}{\partial A_{zx}}}} = \frac{4}{\tau_k} \ge \frac{8}{T_2^{HE}}
+	\delta A_{zx} \equiv \frac{\delta \tau}{\abs{\frac{\partial \tau_k}{\partial A_{zx}}}} = \frac{4}{\tau_k} \ge \frac{8}{T_2^{HE}}
 \end{gather}
-Assuming the typical values of $T_2^{HE} = 100 $ $\mu$s, a nuclear spin can be distinguished from another one if their transverse hyperfine coupling is separated by $\delta A_{zx} = 80$ kHz, which is quite inaccurate and $\approx 160$ times worse than for $S=1$.
-To quantify the difference in sensitivity to estimating the hyperfine parameters, we perform calculation of the Fisher information matrix (FIM) for the 23 nuclear spin cluster, with 23 $A_{zz}$ and 23 $A_{zx}$ parameters (see Fig.
+Assuming typical values of $T_2^{HE} = 100$ $\mu$s, a nuclear spin can be distinguished from another one if their transverse hyperfine coupling is separated by $\delta A_{zx} = 80$ kHz, which is quite inaccurate and approximately 160 times worse than for $S=1$.
+
+To quantify the difference in sensitivity to estimating the hyperfine parameters, we perform calculations of the Fisher Information Matrix (FIM) for the 23-nuclear spin cluster, with 23 $A_{zz}$ and 23 $A_{zx}$ parameters (see Fig.
 \ref{fig:3}c,d).
-The fisher information matrix is estimated for the probability to measure state $|0\rangle$ and reads as: 
+The Fisher Information Matrix is estimated for the probability to measure state $|0\rangle$ and reads as: 
 \begin{equation}
@@
 \end{equation}
-For the typical case of NV center, with $S=1$, since all the nuclear spin resonances are clearly resolved, the Fisher information matrix takes a diagonal shape, revealing a low covariance between the various nuclear spin resonances.
-The crosstalk is existing between $A_{zz}$ and $A_{zx}$ of same nuclear spin, which is because the position of the peaks depends on both values. 
-The fisher information gives a bound for the precision of parameter estimation, known as Cramér–Rao bound: 
+For the typical case of an NV center with $S=1$, since all the nuclear spin resonances are clearly resolved, the Fisher Information Matrix takes a diagonal shape, revealing low covariance between the various nuclear spin resonances.
+There is crosstalk between $A_{zz}$ and $A_{zx}$ for a nuclear spin, as the position of the peaks depends on both values.
+The Fisher Information provides a bound for the precision of parameter estimation, known as the Cramér–Rao bound: 
 \begin{equation}
@@
 \end{equation}
-For the presented protocol, the precision for various spins is limited by 0.09 Hz for the S=1, for the N = 4000. \\
-
-The striking difference to the $S=1$ fisher information matrix, is the behaviour of the defect with $S=1/2$.
-
-On the other hand, a sequence that is limited by $T_1$ instead of $T_2$ is based on 3 and 5-pulse ESEEM.
-The main principle of 5-pulse ESEEM \cite{kasumaj20085} is to create an entanglement (via e.g.
-Hahn-echo block) before the free evolution of the nuclear spins and after make a second correlating sequence.
-In other words, change the initial density matrix for the Ramsey sequence from such that entanglement already exist in the electron polarization terms of the density matrix, thus limitied by $T_1$ time.
-Fig \ref{fig:seqs} shows the sequence, which can be interpreted as two Hahn Echos that are separated by a long free evolution $T\gg T_2^\ast$ such that the coherence of the electron spin vanishes. 
-The analytical formula to this sequence is provided in the appendix \ref{app:5pESEEM}.
-During the free evolution time, each nuclear spins oscillates with either of two resonance frequencies obtained from eq.
-\ref{eq:H}.
-
+For the presented protocol, the precision for various spins is limited by 0.09 Hz \vvv{Hz squared?} for the S=1, for the N = 4000, while for the S=1/2 the value of the Cramer-Rao bound reads as \vvv{XXX} which is \vvv{YYYY} time smaller.
+\\
+The striking difference to the $S=1$ Fisher Information Matrix is the behavior of the defect with $S=1/2$.
+First of all, for both spin $S=1/2$ and $S=1$, the sequence's spectral resolution is limited by the $T_1$ relaxation time of the electron spin.
+On the other hand, the sequence's sensitivity is limited by $T_2$.
+The main principle of 5-pulse ESEEM \cite{kasumaj20085} is to create entanglement (via, e.g., Hahn-echo or CPMG block) before the free evolution of the nuclear spins and then to apply a second correlating sequence afterwards.
+In other words, the initial density matrix for the Ramsey sequence is modified so that entanglement already exists in the electron polarization terms of the density matrix, thus limited by $T_1$ time.
+Fig \ref{fig:seqs} shows the sequence, which can be interpreted as two Hahn Echos separated by a long free evolution $T\gg T_2^\ast$ such that the coherence of the electron spin vanishes.
+The analytical formula for this sequence is provided in the appendix \ref{app:5pESEEM}.
+During the free evolution time, each nuclear spin oscillates with one of two resonance frequencies obtained from Eq. \ref{eq:H}.
 \begin{figure*}[htbp]
@@
 		\includegraphics[width=0.9\textwidth]{pict/eseem_compare2.pdf}
-		\caption{Simulated FFT of ESEEM signal with a zoom into weakly coupled nuclear spins for the register reported \cite{abobeih2019atomic} assuming the electron spin is one-half.
+		\caption{Simulated FFT of ESEEM signal with a zoom into weakly coupled nuclear spins for the register reported \cite{abobeih2019atomic} assuming the electron spin 1/2 system.
 b.
@@
 one-half system.}
-		\label{fig:4}
+		\label{fig:ddeseem}
 	\end{center}
@@
 
-Fig \ref{fig:4} shows the Fourier transform of the signal. 
-Zooming into area close to the Larmor frequency reveals the weakly coupled nuclei. 
-Each nuclear spins have two peaks in the spectrum. 
-Expanding the resonance frequencies up to first order with respect to hyperfine coupling results that the weakly coupled nuclei keep their order as they go further away from the nuclei. 
-This fact makes their characterisation rather straight forward. 
-To observe the weakly coupled nuclei more pronouncedly, one can use DD-ESEEM sequence by adding more $\pi$ pulses in the entangling periods. 
-To distinguish other nuclei, extra measurements is required. 
-One method is to use two dimensional hyperfine correlation spectroscopy (2D Hyscore)  \cite{vorobyov2022addressing}. 
-However, this method is rather time-consuming as two time variables has to be swept. 
-We suggest sweeping $\tau$ parameter and keep the track of frequency amplitude as a function of $\tau$. 
-Two frequencies that belong to the same nuclear are correlated because the modulation depth oscillates with blind spot terms of both frequencies $\sin^2(\frac{\omega_0 \tau}{2}) \sin^2(\frac{\omega_1 \tau}{2})$.
-Fig.
-\ref{fig:5} shows two frequencies goes to bright and blind spots simultaneously.
-Hence, taking two dimensional correlation of the spectrum, one can deduce which two frequencies are correlated and belong to the same nuclear.
-\\
+Fig. \ref{fig:ddeseem} shows the Fourier transform of the signal.
+Zooming into the area close to the Larmor frequency reveals the weakly coupled nuclei.
+Each nuclear spin has two peaks in the spectrum referring to $\omega_a$ and $\omega_b$.
+Expanding the resonance frequencies up to first order with respect to hyperfine coupling shows that nuclear spins appear in order of their coupling strength, making their characterization rather straightforward.
+To observe the weakly coupled nuclei more pronouncedly, one can use the DD-ESEEM sequence by adding more $\pi$ pulses in the entangling periods.
+To distinguish other nuclei, extra measurements are required.
+One method is to use two-dimensional hyperfine correlation spectroscopy (2D Hyscore) \cite{vorobyov2022addressing}.
+However, this method is rather time-consuming as two time variables have to be swept.
+Optimum time sampling techniques might be used to optimize the timing of 2D sampling.
+Here we suggest an alternative way, which is conventionally used in ESR, i.e., sweeping the $\tau$ parameter and keeping track of the frequency amplitude as a function of $\tau$.
+Two frequencies that belong to the same nucleus are correlated because the modulation depth oscillates with blind spot terms of both frequencies $\sin^2(\frac{\omega_0 \tau}{2}) \sin^2(\frac{\omega_1 \tau}{2})$.
+Fig. \ref{fig:5} shows two frequencies going to bright and blind spots simultaneously.
+Hence, by taking a two-dimensional correlation of the spectrum, one can deduce which two frequencies are correlated and belong to the same nucleus.
 
-Here, we try to simulate the realistic situation.
-First, the electron spin state is projected to 0 and 1 with a binomial distribution, the probability determined by the theoretical signal.
+To simulate the realistic experimental situation, we model the electron spin state as projected to 0 and 1 with a binomial distribution where the probability is determined by the analytical expressions.
 Then, we assume the bright (dark) state emits 3 (0.1) photons on average with a Poissonian distribution.
-We repeat the measurement at each point for 10000 times to reduce classical noise.\\
-How many nuclear spin is identifiable with this method? It depends on the duration of free evolution time and the choice of inter-pulse timing $\tau$.
+We repeat the measurement at each point for 10,000 times to reduce classical photon shot noise.
+
+Next, we approach the estimation of the number of nuclear spins that could be identified. It depends on the duration of free evolution time and the choice of inter-pulse timing $\tau$.
 
@@
 
-\section{Conclusion}
+\section{Discussion}
 \label{sec:discussion}
 %\subsection{Advanced filters}
-Here is the concise conclusion @Vadim
+Here is the concise conclusion
 
@@
 \label{app:5pESEEM}
-Here we need to define a few unitary operators/ The evolution in the first Hahn-echo is given by V operators, the middle free evolution is given by F operators, and the second Hahn-echo is given by W operators:
+
+To define the unitary operators, let's introduce three sets of operators representing the evolution during the sequence:
+1. The evolution during the first Hahn-echo is given by the 
+V operators 2. The middle free evolution is represented by the 
+F operators 3. The second Hahn-echo is governed by the W operators:
 \begin{gather}
@@
 \end{gather}
+These operators define the trajectory of the electron spin during the 5-pulse ESEEM sequence.
 The signal can be obtained from four different types of trajectories that the electron spin can take.
-We use the fact that multiplication of unitary operators is also a unitary operator and every unitary in spin one half space can be written in terms of a rotation angle, axis, and Pauli Matrices $\vec{\sigma}$.
-We denote the unitary operator $U = \exp(-i \theta_U \hat{n}_U\cdot\vec{\sigma}) = M\cos(\theta_U) \mathbf{I}- i \sin(\theta_U) \hat{n}_U\cdot\vec{\sigma}$.
+We can express every unitary operator in terms of a rotation angle, axis, and Pauli matrices $\vec{\sigma}$.
+Denoting the unitary operator $U$ as $U = \exp(-i \theta_U \hat{n}_U\cdot\vec{\sigma}) = M\cos(\theta_U) \mathbf{I}- i \sin(\theta_U) \hat{n}_U\cdot\vec{\sigma}$.
 The signal for 5-pulse ESEEM can be obtained as follows:
@@
 
-As we have shown, the signal from the register comes from the multiplication of signals from individual nuclear spins.
-Hence, if the modulation depth is not low (low magnetic field condition), the second or higher order frequencies will appear in the spectrum.
-So, the product rule lead to the creation of inter-nuclear peaks at multi-quantum frequencies that can be sums or subtraction of single quantum frequencies of various nuclei.
-Nevertheless, the multiple quantum resonance peaks are informative for the electron spin one half system because one can deduce that two peaks that are added or subtracted belong to the same electron spin manifold; Hence it is possible to get the relative phase of nuclei.
-Another consequence of the product rule is the cross-suppression effect, which means the presence of strongly coupled nuclei suppress the amplitude of weakly coupled nuclei while weakly coupled ones do not suppress the amplitude of strongly coupled nuclei \cite{stoll2005peak}.
-However, if we assume the Larmor frequency is relatively high or the modulation depth is low, both of these effect will vanish as the product rule can be approximated by a summation rule:\\
+As demonstrated, the signal from the nuclear spin register arises from the multiplication of signals from individual nuclear spins.
+Consequently, if the modulation depth is not low (indicative of low magnetic field conditions), higher-order frequencies will manifest in the spectrum.
+Thus, the product rule gives rise to inter-nuclear peaks at multi-quantum frequencies, which can represent sums or subtractions of single quantum frequencies from various nuclei.
+However, these multiple quantum resonance peaks are informative for electron spin one-half systems because it enables deduction that two peaks added or subtracted belong to the same electron spin manifold, allowing for determination of relative phase of nuclei.
+Another consequence of the product rule is the cross-suppression effect, where the presence of strongly coupled nuclei suppresses the amplitude of weakly coupled nuclei, while weakly coupled ones do not suppress the amplitude of strongly coupled nuclei \cite{stoll2005peak}.
+However, assuming a relatively high Larmor frequency or low modulation depth, both of these effects will vanish as the product rule can be approximated by a summation rule:\\
 \begin{gather}

### 2024-01-31 article.tex
ploting the ellipse plis workin on the refs

@@
 Here, we present a more straightforward approach for determining the hyperfine interactions among each nuclear and the electron spin. 
-This method holds promise across diverse platforms, including emerging S=1/2 group IV defects in diamond (e.g., SiV, GeV, SnV, PbV) or silicon vacancies in silicon carbide. 
-We provide a theoretical framework and adapt it for use with color centers exhibiting various spins.
+This method holds promise across diverse platforms, especially for emerging S=1/2 group IV defects in diamond (e.g., SiV, GeV, SnV, PbV) or silicon (T-centre). 
+We provide a theoretical framework and adapt it for use with color-centers exhibiting various spins.
 Through simulations conducted on nuclear spin clusters, we evaluate different protocols and compare their performance using the Fisher information matrix.
@@
 However, characterizing the hyperfine coupling of nuclear spins can be both challenging and time-consuming \cite{abobeih2019atomic, van2023mapping}. 
-Traditionally, nuclear spin characterization is accomplished through Optically Detected Magnetic Resonance (ODMR) \cite{Dreau, Neumann, Eriks}, but the spectroscopic resolution is constrained by the $1/T_2^\ast$ of the electron spin.
+Traditionally, nuclear spin characterization is accomplished through Optically Detected Magnetic Resonance (ODMR) \cite{Dreau:2012aa,hesselmeier2023measuring}, but the spectroscopic resolution is constrained by the $1/T_2^\ast$ of the electron spin.
 To overcome this limitation, Hahn-Echo-type sequences have been employed to refocus the electron spin and extend its coherence time \cite{childress2006coherent}, thereby improving the resolution to $1/T_2$.
 This method could be applied to defects with a specific configuration of nuclear spins, particularly those with a certain relation to the magnetic field and the coupling of the nuclear spins, such as weakly coupled nuclear spins.
-Also, the protocols also can only be applied to electron spins with a specific spin multiplicity
+Also, the protocols also can only be applied to electron spins with a specific spin multiplicity.
 Depending on the applied protocol for the nuclear spins characterisation, the number of identifiable nuclear spin can increase.
@@
 (see fig.
-\ref{fig:1}) \cite{Laraui, Vorobyov}.
+\ref{fig:1}) \cite{laraoui2013high, vorobyov2022addressing}.
 In particular, we consider the following common examples of nuclear spin registers that are ubiquitous in applications.
-First, the NV-like case with S=1 and weakly coupled nuclear spins, operating at high magnetic fields where $\gamma_n B \gg A_{zx}$ which has been extensively studied in the works of \cite{abobeih2019atomic, taminiau2012detection, Tam2014, Wrachtrup, before}.
+First, the NV-like case with $S=1$ and weakly coupled nuclear spins, operating at high magnetic fields where $\gamma_n B \gg A_{zx}$ which has been extensively studied in the works of \cite{abobeih2019atomic, taminiau2012detection, Zhao:2014aa}.
 The capability to observe narrow peaks with analytically predictable positions and contrasts enables the solution of the inverse problem concerning the characterization of the coupling between nuclear spins and electron spins.
@@
 The third case (Fig.
-1c) pertains to the S=1/2 scenario, where the lack of offset in the average evolution of the nuclear spin results in its dynamics weakly depending on Azz and only in the second order on $A_{zx}$ \cite{suckachev}.
-Consequently, this leads to a limited ability to distinguish between multiple nuclear spins and, consequently, a lack of individual addressability of nuclear spins.
+\ref{fig:1}c) pertains to the $S=1/2$ scenario, where the lack of offset in the average evolution of the nuclear spin results in its dynamics weakly depending on $A_{zz}$ and only the second order dependence on $A_{zx}$.
+Consequently, this leads to a limited ability to distinguish between multiple nuclear spins and a lack of individual addressability of nuclear spins.
 Lastly, in the case of other material host platforms, a bispecies nuclear spin bath may be observed, where resonance peaks corresponding to different Larmor frequencies of different species further complicate the reconstruction of the Hamiltonian.
 For unambiguous reconstruction of the interactions, additional measurements, such as those at different magnetic field strengths, would be required.
-In this work, we propose that a correlation-type sequence, based on five pulse ESEEM, could serve as a general framework as it holds promise for the reconstruction of the interactions in all of the aforementioned cases.
+While the double resonance methods \cite{Bradley:2019aa,zaiser2016enhancing} posses a large promise for nuclear spin spectroscopy, they require additional experimental hardware, and often are not available.
+Thus, in this work, we investigate the limits of electron spin driven schemes, in particular a correlation-type sequences, which could serve as a general framework and hold promise for the reconstruction of the interactions in all of the aforementioned cases.
 
@@
 
-In this work, we consider 23 nuclear spins characterized in paper \cite{abobeih2019atomic} as a realistic case.
 \begin{figure*}%[htbp]

### 2024-02-02 article.tex
paper text fininshed draft

@@
 
+\begin{figure*}%[htb]
+	\begin{center}
+		\includegraphics[width=0.9\textwidth]{pict/drawing0.pdf}
+		\caption{Comparing DD and five pulse ESEEM as two nuclear spin characterization methods in different systems.
+a.
+Electron spin one system: In the DD signal, each nuclear spin exhibits a distinct resonance time up to the first order of $A_{zz}$; the accuracy of the obtained hyperfine interaction is limited to $T_2$ of the electron spin.
+In the Fourier transform of the ESEEM signal, the two resonance frequencies of each spin are present; the accuracy of the obtained hyperfine interaction is limited to $T_1$ of the electron spin.
+b.
+Electron spin 1 system with two strongly coupled nuclear spins and many weakly coupled spins: No resonance time is detectable since the required condition for DD ($\omega_L \gg A_{zz}, A_{zx}$) does not hold.
+However, resonant frequencies are still obtainable in the ESEEM signal.
+c.
+Electron spin 1/2 system: Nuclear spins have more or less the same resonance time as it depends on the second order of hyperfine coupling.
+However, the resonant frequency of each spin is distinguishable in the ESEEM signal.
+d.
+System containing two different nuclear spin species: Two nuclear spin baths can interfere in the DD signal, making the signal analysis more challenging.
+However, the species can be inferred from the ESEEM signal since species have different Larmor frequencies.}
+		\label{fig:1}
+	\end{center}
+\end{figure*}
+
 Each center contains an electron spin that can be directly controlled using microwaves, and it can be initialized and read out through optical excitation. 
@@
 
-\begin{figure*}%[htb]
-	\begin{center}
-		\includegraphics[width=0.9\textwidth]{pict/drawing0.pdf}
-		\caption{Comparing DD and five pulse ESEEM as two nuclear spin characterization methods in different systems.
-a.
-Electron spin one system: In the DD signal, each nuclear spin exhibits a distinct resonance time up to the first order of $A_{zz}$; the accuracy of the obtained hyperfine interaction is limited to $T_2$ of the electron spin.
-In the Fourier transform of the ESEEM signal, the two resonance frequencies of each spin are present; the accuracy of the obtained hyperfine interaction is limited to $T_1$ of the electron spin.
-b.
-Electron spin 1 system with two strongly coupled nuclear spins and many weakly coupled spins: No resonance time is detectable since the required condition for DD ($\omega_L \gg A_{zz}, A_{zx}$) does not hold.
-However, resonant frequencies are still obtainable in the ESEEM signal.
-c.
-Electron spin 1/2 system: Nuclear spins have more or less the same resonance time as it depends on the second order of hyperfine coupling.
-However, the resonant frequency of each spin is distinguishable in the ESEEM signal.
-d.
-System containing two different nuclear spin species: Two nuclear spin baths can interfere in the DD signal, making the signal analysis more challenging.
-However, the species can be inferred from the ESEEM signal since species have different Larmor frequencies.}
-		\label{fig:1}
-	\end{center}
-\end{figure*}
-
 %%%%%%%%%%%%%%%%%%%================= %THEORY
@@
 \label{sec:theory}
+\begin{figure*}%[htbp]
+	\begin{center}
+		\includegraphics[width=0.9\textwidth]{pict/dd_compare2.pdf}
+		\caption{Simulated DD signal with 64 $\pi$-pulses for the register reported in  \cite{abobeih2019atomic} assuming the electron spin is a.
+spin 1 system b.
+spin 1/2 system.
+Simulated Fisher information matrix for the case of the electron spin c.
+spin 1 system d.
+spin 1/2 system.}
+		\label{fig:3}
+	\end{center}
+\end{figure*}
 %%%%%%%%%%%%%%%Í%%%%=================
@@
 Hence, the resonance signal depends on the second order of the perpendicular hyperfine component.
-
-\begin{figure*}%[htbp]
+\begin{figure*}[htbp]
 	\begin{center}
-		\includegraphics[width=0.9\textwidth]{pict/dd_compare2.pdf}
-		\caption{Simulated DD signal with 64 $\pi$-pulses for the register reported in  \cite{abobeih2019atomic} assuming the electron spin is a.
-spin 1 system b.
-spin 1/2 system.
-Simulated Fisher information matrix for the case of the electron spin c.
-spin 1 system d.
-spin 1/2 system.}
-		\label{fig:3}
+		\includegraphics[width=0.9\textwidth]{pict/eseem_compare2.pdf}
+		\caption{Simulated FFT of ESEEM signal with a zoom into weakly coupled nuclear spins for the register reported \cite{abobeih2019atomic} assuming the electron spin 1/2 system.
+b.
+Enhancing the sensitivity to weakly coupled spins by increasing number of $\pi$-pulses to $N=72$ pulses in each entangling period.
+$\tau$ is set to the Larmor bright spot.
+Simulated Fisher information for the case of the electron spin c.
+one d.
+one-half system.}
+		\label{fig:ddeseem}
 	\end{center}
 \end{figure*}
+
 In this work, we consider the 23-nuclear spin cluster characterized in paper \cite{abobeih2019atomic} as a realistic case for our comparison.
@@
 Assuming typical values of $T_2^{HE} = 100$ $\mu$s, a nuclear spin can be distinguished from another one if their transverse hyperfine coupling is separated by $\delta A_{zx} = 80$ kHz, which is quite inaccurate and approximately 160 times worse than for $S=1$.
+\begin{figure*}%[htbp]
+	\begin{center}
+		\includegraphics[width=0.9\textwidth]{pict/fig5.png}
+		\caption{a. FFT of ESEEM signal for $\tau$ from 10 $\mu$s to 500 $\mu$s with the step of 10 $\mu$s b. 2D correlation of each frequency for different $\tau$.}
+		\label{fig:4}
+	\end{center}
+\end{figure*}
 
@@
 \begin{equation}
-	\delta A^2 \ge \frac{1}{F(A) N}
+	\delta A^2 \ge \frac{1}{N} F(A)^{-1}
 \end{equation}
-For the presented protocol, the precision for various spins is limited by 0.09 Hz \vvv{Hz squared?} for the S=1, for the N = 4000, while for the S=1/2 the value of the Cramer-Rao bound reads as \vvv{XXX} which is \vvv{YYYY} time smaller.
-\\
 The striking difference to the $S=1$ Fisher Information Matrix is the behavior of the defect with $S=1/2$.
@@
 During the free evolution time, each nuclear spin oscillates with one of two resonance frequencies obtained from Eq. \ref{eq:H}.
-\begin{figure*}[htbp]
+
+\label{sec:discussion}
+\begin{figure*}%[htbp]
 	\begin{center}
-		\includegraphics[width=0.9\textwidth]{pict/eseem_compare2.pdf}
-		\caption{Simulated FFT of ESEEM signal with a zoom into weakly coupled nuclear spins for the register reported \cite{abobeih2019atomic} assuming the electron spin 1/2 system.
-b.
-Enhancing the sensitivity to weakly coupled spins by increasing number of $\pi$-pulses to $N=72$ pulses in each entangling period.
-$\tau$ is set to the Larmor bright spot.
-Simulated Fisher information for the case of the electron spin c.
-one d.
-one-half system.}
-		\label{fig:ddeseem}
+		\includegraphics[width=1.0\textwidth]{pict/cov_compare_vad.pdf}
+		\caption{Visualisation of the CramerRao bound for various protocols on existing nuclear spin dataset from \cite{Abobei2019}}
+		\label{fig:cov}
 	\end{center}
 \end{figure*}
-
 Fig. \ref{fig:ddeseem} shows the Fourier transform of the signal.
@@
 Two frequencies that belong to the same nucleus are correlated because the modulation depth oscillates with blind spot terms of both frequencies $\sin^2(\frac{\omega_0 \tau}{2}) \sin^2(\frac{\omega_1 \tau}{2})$.
-Fig. \ref{fig:5} shows two frequencies going to bright and blind spots simultaneously.
+Fig. \ref{fig:4} shows two frequencies going to bright and blind spots simultaneously.
 Hence, by taking a two-dimensional correlation of the spectrum, one can deduce which two frequencies are correlated and belong to the same nucleus.
@@
 
-Next, we approach the estimation of the number of nuclear spins that could be identified. It depends on the duration of free evolution time and the choice of inter-pulse timing $\tau$.
+Next, we approach the estimation of the number of nuclear spins that could be identified.
+It depends on the duration of free evolution time and the choice of inter-pulse timing $\tau$.
+For the realistic case of the $T_1 = 1$ s, and $T_2 = 100 \mu s$, we approach the estimation of the Fisher information matrix for various protocols and approach the system with moderate N=16 pulses for the dynamical decoupling sequence and simplest 5 pulse ESEEM for correlation protocol for simplicity of calculation, since in that case the analytical expressions are available.
 
-\begin{figure*}%[htbp]
-	\begin{center}
-		\includegraphics[width=0.9\textwidth]{pict/fig5.png}
-		\caption{a. FFT of ESEEM signal for $\tau$ from 10 $\mu$s to 500 $\mu$s with the step of 10 $\mu$s b. 2D correlation of each frequency for different $\tau$.}
-		\label{fig:5}
-	\end{center}
-\end{figure*}
+On Fig. \ref{fig:cov} we see a manifestation of the correlation protocol for spin 1/2 system realised in a number of nuclear spins one could estimate with each of the protocols. 
+The figure presents the dots, in the $A_{zz}, A_{zx}$ axes, with an area bounded by Cramer-Rao bound around each point. 
+When uncertainty is larger the absolute values of the coupling, the point is considered to be non-detectable or if it is larger than the distance to the nearest point non distinguishable and is marked in red.
+Alternatively, it is considered to be identified and is turned blue. 
+Additionally, we plot an ellipses, with two points as it foci and small axis size as a value of the covariance between various parameters in the Cramer-Rao bound. 
+We plot only single ellipse with largest covariance value. 
+This values are calculated as off-diagonal elements in the inverse Fisher information matrix. 
+This covariances are mostly show the crosstalk between different parameters in the presented data, and are more strongly present in the DD S=1/2 case. 
+The idea behind ellipse representation, is that when the covariance is larger than the self-variance, the ellipse absorbs the individual points, and the points become indistinguishable. 
+We find that, while this crosstalk is not the limiting factor for informational approach, it might be important when a realistic estimator is considered. 
+We note, that this is not strictly same condition as in the experimental identification, and is idealised. 
+We only consider the available information in the plot, assuming that an optimum estimator for extraction of that information already exist. 
+In reality, one has to additionally assume a non ideal estimator procedure, which involves extraction of the hyperfine parameter values from the raw data and is a subject of further work.
+As a result we see, that while for the DD method, a S=1/2 case for N=16 pulses allows for identification of only 3 spins out of 23, the 5 pulse ESEEM method works with similar success for both S=1 and S=1/2 system.
+Totally, it is capable of detecting 15-17 nuclear spins, and could be further boosted by usage of DD-ESEEM method with multiple pulses in each sensing block analogous to Fig. \ref{fig:ddeseem}
 
 \section{Discussion}
-\label{sec:discussion}
+
 %\subsection{Advanced filters}
-Here is the concise conclusion
+In this work we performed a theoretical and numerical comparison of various ESEEM methods for the purpose of characterisation of the nuclear spin clusters around S=1 and S=1/2 type of defects.
+We found, that while for S=1 systems, modified spin echo sequences, e.g. CPMG and XY-N, are most suited for single nuclear spin qubit spectroscopy, for S=1/2 system they are limited in performance. 
+We see, that a correlation type sequences, e.g. 3,5 pulse ESEEM present a more potential for characterisation of a diluted nuclear spin bath, and perform at least similar to the S=1 case. 
+We believe, that this method boast large potential for preliminary screening of nuclear spin clusters for S=1/2 potential qubit candidate systems, such as G-IV defects in diamond.
+Additionally, our method does not require strong microwave pulse fields, since the pulses do not require to cope with nuclear spin Larmour frequency.
 

### 2024-02-02 article.tex
the paper is ready? @majidzahedian please proof read, then i will also proof read and submit

@@
 		\includegraphics[width=1.0\textwidth]{pict/cov_compare_vad.pdf}
-		\caption{Visualisation of the CramerRao bound for various protocols on existing nuclear spin dataset from \cite{Abobei2019}}
+		\caption{Visualisation of the CramerRao bound for various protocols on existing nuclear spin dataset from \cite{abobeih2019atomic}}
 		\label{fig:cov}
@@
 Additionally, our method does not require strong microwave pulse fields, since the pulses do not require to cope with nuclear spin Larmour frequency.
+In this work we show various sensing methods, while we dont touch the estimator performance. 
+We believe, that this has to be considered in conjuction with adaptive and optimal strategies for controlling the experimental parameters, e.g.
+Bayessian Optimal Experimental Design or Machine Learning for increasing the efficiency of estimation.
 

### 2024-02-05 article.tex
my last edit

--- 2024-01-31 article.tex
@@
 
-Each center contains an electron spin that can be directly controlled using microwaves, and it can be initialized and read out through optical excitation. 
-The potential hyperfine interactions with a bath of numerous nuclear spins are crucial for diverse applications, as they offer long-lived quantum memories and enable the creation of an optically accessible nuclear spin qubit register.
-To implement efficient quantum control for these memories, it is imperative to have precise knowledge of the full Hamiltonian governing the register.
-However, characterizing the hyperfine coupling of nuclear spins can be both challenging and time-consuming \cite{abobeih2019atomic, van2023mapping}. 
-Traditionally, nuclear spin characterization is accomplished through Optically Detected Magnetic Resonance (ODMR) \cite{Dreau:2012aa,hesselmeier2023measuring}, but the spectroscopic resolution is constrained by the $1/T_2^\ast$ of the electron spin.
-To overcome this limitation, Hahn-Echo-type sequences have been employed to refocus the electron spin and extend its coherence time \cite{childress2006coherent}, thereby improving the resolution to $1/T_2$.
-This method could be applied to defects with a specific configuration of nuclear spins, particularly those with a certain relation to the magnetic field and the coupling of the nuclear spins, such as weakly coupled nuclear spins.
-Also, the protocols also can only be applied to electron spins with a specific spin multiplicity.
-Depending on the applied protocol for the nuclear spins characterisation, the number of identifiable nuclear spin can increase.
-Electron Spin Echo Envelop Modulation (ESEEM) types of sequences allow access to the highest number of nuclear spins, as the spectroscopy resolution is limited to the longitudinal relaxation time ($T_1$) of the system.
-(see fig.
-\ref{fig:1}) \cite{laraoui2013high, vorobyov2022addressing}.
-In particular, we consider the following common examples of nuclear spin registers that are ubiquitous in applications.
-First, the NV-like case with $S=1$ and weakly coupled nuclear spins, operating at high magnetic fields where $\gamma_n B \gg A_{zx}$ which has been extensively studied in the works of \cite{abobeih2019atomic, taminiau2012detection, Zhao:2014aa}.
-The capability to observe narrow peaks with analytically predictable positions and contrasts enables the solution of the inverse problem concerning the characterization of the coupling between nuclear spins and electron spins.
-The second case (as depicted in Fig.
-\ref{fig:1}b) corresponds to a scenario similar to the first, but with the presence of a strongly coupled nuclear spin, which obstructs the observation of weakly coupled nuclear spins.
-This case is particularly relevant in situations where, in addition to the weakly coupled register, a strongly coupled nuclear spin is utilized, for instance, for repetitive enhancement of the readout.
-This enhancement is achieved by exploiting the strongly coupled ancilla, which is discernible in electron spin resonance spectra.
-The third case (Fig.
-\ref{fig:1}c) pertains to the $S=1/2$ scenario, where the lack of offset in the average evolution of the nuclear spin results in its dynamics weakly depending on $A_{zz}$ and only the second order dependence on $A_{zx}$.
-Consequently, this leads to a limited ability to distinguish between multiple nuclear spins and a lack of individual addressability of nuclear spins.
-Lastly, in the case of other material host platforms, a bispecies nuclear spin bath may be observed, where resonance peaks corresponding to different Larmor frequencies of different species further complicate the reconstruction of the Hamiltonian.
-For unambiguous reconstruction of the interactions, additional measurements, such as those at different magnetic field strengths, would be required.
-While the double resonance methods \cite{Bradley:2019aa,zaiser2016enhancing} posses a large promise for nuclear spin spectroscopy, they require additional experimental hardware, and often are not available.
-Thus, in this work, we investigate the limits of electron spin driven schemes, in particular a correlation-type sequences, which could serve as a general framework and hold promise for the reconstruction of the interactions in all of the aforementioned cases.
-
 \begin{figure*}%[htb]
@@
 
+Each center contains an electron spin that can be directly controlled using microwaves, and it can be initialized and read out through optical excitation. 
+The potential hyperfine interactions with a bath of numerous nuclear spins are crucial for diverse applications, as they offer long-lived quantum memories and enable the creation of an optically accessible nuclear spin qubit register.
+To implement efficient quantum control for these memories, it is imperative to have precise knowledge of the full Hamiltonian governing the register.
+However, characterizing the hyperfine coupling of nuclear spins can be both challenging and time-consuming \cite{abobeih2019atomic, van2023mapping}. 
+Traditionally, nuclear spin characterization is accomplished through Optically Detected Magnetic Resonance (ODMR) \cite{Dreau:2012aa,hesselmeier2023measuring}, but the spectroscopic resolution is constrained by the $1/T_2^\ast$ of the electron spin.
+To overcome this limitation, Hahn-Echo-type sequences have been employed to refocus the electron spin and extend its coherence time \cite{childress2006coherent}, thereby improving the resolution to $1/T_2$.
+This method could be applied to defects with a specific configuration of nuclear spins, particularly those with a certain relation to the magnetic field and the coupling of the nuclear spins, such as weakly coupled nuclear spins.
+Also, the protocols also can only be applied to electron spins with a specific spin multiplicity.
+Depending on the applied protocol for the nuclear spins characterisation, the number of identifiable nuclear spin can be different.
+Electron Spin Echo Envelop Modulation (ESEEM) types of sequences allow access to the highest number of nuclear spins, as the spectroscopy resolution is limited to the longitudinal relaxation time ($T_1$) of the system.
+(see fig.
+\ref{fig:1}) \cite{laraoui2013high, vorobyov2022addressing}.
+In particular, we consider the following common examples of nuclear spin registers that are ubiquitous in applications.
+First, the NV-like case with $S=1$ and weakly coupled nuclear spins, operating at high magnetic fields where $\gamma_n B \gg A_{zx}$ which has been extensively studied in the works of \cite{abobeih2019atomic, taminiau2012detection, Zhao:2014aa}.
+The capability to observe narrow peaks with analytically predictable positions and contrasts enables the solution of the inverse problem concerning the characterization of the coupling between nuclear spins and electron spins.
+The second case (as depicted in Fig.
+\ref{fig:1}b) corresponds to a scenario similar to the first, but with the presence of a strongly coupled nuclear spin, which obstructs the observation of weakly coupled nuclear spins.
+This case is particularly relevant in situations where, in addition to the weakly coupled register, a strongly coupled nuclear spin is utilized, for instance, for repetitive enhancement of the readout.
+This enhancement is achieved by exploiting the strongly coupled ancilla, which is discernible in electron spin resonance spectra.
+The third case (Fig.
+\ref{fig:1}c) pertains to the $S=1/2$ scenario, where the lack of offset in the average evolution of the nuclear spin results in its dynamics weakly depending on $A_{zz}$ and only the second order dependence on $A_{zx}$.
+Consequently, this leads to a limited ability to distinguish between multiple nuclear spins and a lack of individual addressability of nuclear spins.
+Lastly, in the case of other material host platforms, a bispecies nuclear spin bath may be observed, where resonance peaks corresponding to different Larmor frequencies of different species further complicate the reconstruction of the Hamiltonian.
+For unambiguous reconstruction of the interactions, additional measurements, such as those at different magnetic field strengths, would be required.
+While the double resonance methods \cite{Bradley:2019aa,zaiser2016enhancing} posses a large promise for nuclear spin spectroscopy, they require additional experimental hardware, and often are not available.
+Thus, in this work, we investigate the limits of electron spin driven schemes, in particular a correlation-type sequences, which could serve as a general framework and hold promise for the reconstruction of the interactions in all of the aforementioned cases.
+
 %%%%%%%%%%%%%%%%%%%================= %THEORY
@@
 \label{sec:theory}
+\begin{figure*}%[htbp]
+	\begin{center}
+		\includegraphics[width=0.9\textwidth]{pict/dd_compare2.pdf}
+		\caption{Simulated DD signal with 64 $\pi$-pulses for the register reported in  \cite{abobeih2019atomic} consist of 23 nuclear spins, assuming the electron spin is a.
+spin 1 system b.
+spin 1/2 system.
+Simulated Fisher information matrix for the case of the electron spin c.
+spin 1 system d.
+spin 1/2 system.
+The first 23 hyperfine parameters are $A_{zz}$ and the second 23 parameters are $A_{zx}$ of the nuclear spin register.}
+		\label{fig:3}
+	\end{center}
+\end{figure*}
 %%%%%%%%%%%%%%%Í%%%%=================
@@
 It is assumed that the pulse duration $t_p$ is short enough ($\omega_L t_p \ll 1$) that the nuclear spin dynamics during this time is negligible.
-For completeness, we start our analysis with the simplest characterization sequence, which is the electron spin Ramsey sequence (free induction decay of the electron) (see the Appendix for derivation).
+For completeness, we start our analysis with the simplest characterization sequence, which is the electron spin Ramsey sequence (free induction decay of the electron).
 The Ramsey signal can be obtained as follows:
@@
 The Hahn Echo sequence can be used for defects that contain a few strongly coupled nuclei.
-In order to differentiate the resonance frequency of each nuclear spin or to sharpen the oscillations, one can add more $\pi$ pulses, creating the so-called Dynamical Decoupling sequence to separate the resonance condition for individual nuclear spin.
+In order to differentiate the resonance frequency of each nuclear spin or to sharpen the oscillations, one can add more $\pi$ pulses, creating the so-called Dynamical Decoupling (DD) sequence to separate the resonance condition for individual nuclear spin.
 For the even number of $\pi$ pulses, $N$, The DD signal can be obtained (neglecting decoherence terms):
@@
 To proceed with the characterization, Eq. \ref{eq:DD} needs to be further simplified, requiring stronger assumptions.
-Focusing on weakly coupled nuclear spins or high magnetic field situations, the multiplication rule can be approximated by a summation rule, neglecting the higher-order cross-resonance terms:
+Focusing on weakly coupled nuclear spins or high magnetic field situations, the multiplication over all nuclear spins in Eq.
+\ref{eq:DD} can be approximated by a summation rule, neglecting the higher-order cross-resonance terms:
 \small
@@
 Hence, the resonance signal depends on the second order of the perpendicular hyperfine component.
-
-\begin{figure*}%[htbp]
+\begin{figure*}[htbp]
 	\begin{center}
-		\includegraphics[width=0.9\textwidth]{pict/dd_compare2.pdf}
-		\caption{Simulated DD signal with 64 $\pi$-pulses for the register reported in  \cite{abobeih2019atomic} assuming the electron spin is a.
-spin 1 system b.
-spin 1/2 system.
-Simulated Fisher information matrix for the case of the electron spin c.
-spin 1 system d.
-spin 1/2 system.}
-		\label{fig:3}
+		\includegraphics[width=0.9\textwidth]{pict/eseem_compare2.pdf}
+		\caption{Simulated FFT of ESEEM signal with a zoom into weakly coupled nuclear spins for the register reported \cite{abobeih2019atomic} consist of 23 nuclear spins, assuming the electron spin 1/2 system.
+b.
+Enhancing the sensitivity to weakly coupled spins by increasing number of $\pi$-pulses to $N=72$ pulses in each entangling period.
+$\tau$ is set to the Larmor bright spot.
+Simulated Fisher information for the case of the electron spin c.
+one d.
+one-half system.
+The first 23 hyperfine parameters are $A_{zz}$ and the second 23 parameters are $A_{zx}$ of the nuclear spin register.}
+		\label{fig:ddeseem}
 	\end{center}
 \end{figure*}
+
 In this work, we consider the 23-nuclear spin cluster characterized in paper \cite{abobeih2019atomic} as a realistic case for our comparison.
@@
 The main principle of 5-pulse ESEEM \cite{kasumaj20085} is to create entanglement (via, e.g., Hahn-echo or CPMG block) before the free evolution of the nuclear spins and then to apply a second correlating sequence afterwards.
-In other words, the initial density matrix for the Ramsey sequence is modified so that entanglement already exists in the electron polarization terms of the density matrix, thus limited by $T_1$ time.
+In other words, the initial density matrix for the Hahn Echo sequence is modified so that entanglement already exists in the electron polarization terms of the density matrix, thus limited by $T_1$ time.
 Fig \ref{fig:seqs} shows the sequence, which can be interpreted as two Hahn Echos separated by a long free evolution $T\gg T_2^\ast$ such that the coherence of the electron spin vanishes.
@@
 During the free evolution time, each nuclear spin oscillates with one of two resonance frequencies obtained from Eq. \ref{eq:H}.
-\begin{figure*}[htbp]
+
+\label{sec:discussion}
+\begin{figure*}%[htbp]
 	\begin{center}
-		\includegraphics[width=0.9\textwidth]{pict/eseem_compare2.pdf}
-		\caption{Simulated FFT of ESEEM signal with a zoom into weakly coupled nuclear spins for the register reported \cite{abobeih2019atomic} assuming the electron spin 1/2 system.
-b.
-Enhancing the sensitivity to weakly coupled spins by increasing number of $\pi$-pulses to $N=72$ pulses in each entangling period.
-$\tau$ is set to the Larmor bright spot.
-Simulated Fisher information for the case of the electron spin c.
-one d.
-one-half system.}
-		\label{fig:ddeseem}
+		\includegraphics[width=1.0\textwidth]{pict/cov_compare_vad.pdf}
+		\caption{Visualisation of the CramerRao bound for various protocols on existing nuclear spin dataset from \cite{abobeih2019atomic}}
+		\label{fig:cov}
 	\end{center}
 \end{figure*}
-
 Fig. \ref{fig:ddeseem} shows the Fourier transform of the signal.
@@
 
-Next, we approach the estimation of the number of nuclear spins that could be identified. It depends on the duration of free evolution time and the choice of inter-pulse timing $\tau$.
+To estimate the number of nuclear spins that could be identified, we consider the duration of the free evolution time and the choice of inter-pulse timing $\tau$.
+For a realistic scenario with $T_1 = 1$ s and $T_2 = 100 \mu s$, and sweeping the relevant parameter in 1000 steps, we can estimate the Fisher information matrix for various protocols.
+We will approach the system with a moderate number of pulses, say $N=16$, for the dynamical decoupling sequence, and the simplest 5-pulse ESEEM for the correlation protocol for simplicity of calculation, as analytical expressions are available in that case.
 
-\begin{figure*}%[htbp]
-	\begin{center}
-		\includegraphics[width=0.9\textwidth]{pict/fig5.png}
-		\caption{a. FFT of ESEEM signal for $\tau$ from 10 $\mu$s to 500 $\mu$s with the step of 10 $\mu$s b. 2D correlation of each frequency for different $\tau$.}
-		\label{fig:5}
-	\end{center}
-\end{figure*}
+Fig. \ref{fig:cov} illustrates the manifestation of the correlation protocol for a spin 1/2 system in terms of the number of nuclear spins one could estimate with each of the protocols.
+The dots in the $A_{zz}, A_{zx}$ axes represent the points, with an area bounded by the Cramér-Rao bound around each point.
+A nuclear spin is considered detectable (blue points in Fig.
+\ref{fig:cov}) if the uncertainty of one of the two hyperfine parameters is less than both the absolute value of that parameter and the distance to the closest hyperfine coupling.
+Otherwise, it is considered non-identified (shown as red points). 
+Additionally, covariance between various parameters is calculated from the off-diagonal elements in the inverse Fisher information matrix.
+To illustrate them, an ellipse for each covariance parameter is plotted (colored orange and pink), with two nuclei as the vertices of the ellipse and the small axis size as the Cramér-Rao bound.
+This means that in the case of zero covariance between two nuclei, this ellipse turns into a line.
+To keep the plot readable, for each nuclear spin, only the ellipse with the largest covariance value is plotted.
+These covariances mostly show the crosstalk between different parameters in the presented data and are more strongly present in the DD S=1/2 case. 
+The idea behind the ellipse representation is that when the covariance is larger than the self-variance, the spins become indistinguishable.
+While this crosstalk is not the limiting factor for informational approach, it might be important when considering a realistic estimator.
+It is important to note that this is not strictly the same condition as in experimental identification and is idealized.
+We only consider the available information in the plot, assuming that an optimum estimator for the extraction of that information already exists.
+In reality, one has to additionally assume a non-ideal estimator procedure, which involves the extraction of the hyperfine parameter values from the raw data and is the subject of further work.
+As a result, we see that while for the DD method, a spin 1/2 case for N=16 pulses allows for the identification of only 3 out of 23 nuclear spins, the 5-pulse ESEEM method works with similar success for both S=1 and S=1/2 systems.
+In total, it is capable of detecting 17-18 out of 23 spins with the constrained measurement time and could be further boosted by using the DD-ESEEM method with multiple pulses in each sensing block analogous to Fig.
+\ref{fig:ddeseem}.
 
 \section{Discussion}
-\label{sec:discussion}
+
 %\subsection{Advanced filters}
-Here is the concise conclusion
+In this work, we conducted a theoretical and numerical comparison of various ESEEM methods for characterizing the nuclear spin clusters around S=1 and S=1/2 type of defects.
+We found that for S=1 systems, modified spin echo sequences such as CPMG and XY-N are most suited for single nuclear spin qubit spectroscopy, but for S=1/2 systems, their performance is limited.
+On the other hand, correlation-type sequences like 3 and 5 pulse ESEEM show more potential for characterizing a diluted nuclear spin bath and perform at least as well as in the S=1 case.
+We believe that these methods hold significant potential for preliminary screening of nuclear spin clusters for S=1/2 potential qubit candidate systems, such as G-IV defects in diamond.
+Additionally, our method does not require strong microwave pulse fields since the pulses do not need to cope with the nuclear spin Larmor frequency.
+While we explored various sensing methods in this work, we did not delve into estimator performance.
+We believe that this aspect should be considered in conjunction with adaptive and optimal strategies for controlling the experimental parameters, such as Bayesian Optimal Experimental Design or Machine Learning, to increase the efficiency of estimation.
+This could further enhance the characterization capabilities of these methods in practical experimental scenarios.
 

### 2024-02-07 article.tex
ok

--- 2024-02-02 article.tex
@@
 820394, European Research Council advanced grant No.
-742610, SMel, Federal Ministry of Education and Research (BMBF) project MiLiQuant and Quamapolis, the DFG (FOR 2724), the Max Planck Society, and the Volkswagentiftung.
+742610, SMel, Federal Ministry of Education and Research (BMBF) project MiLiQuant and Quamapolis, Spinning and QR.X the DFG (FOR 2724,INST 41/1109-1 FUGG), the Max Planck Society, and the Volkswagentiftung.
 M.Z.

### 2024-02-09 article.tex
added some references in the introduction

@@
 Leveraging nearby single-color centers, these spins can be efficiently addressed at the single-site level through spin resonance.
-However, characterising individual nuclear spin is quite cumbersome since the utility of characterisation protocols may differ depending on the strength of the hyperfine coupling, necessitating tailored characterization protocols.
+However, characterising individual nuclear spins is quite cumbersome since the utility of characterisation protocols may differ depending on the strength of the hyperfine coupling, necessitating tailored approaches and experimental conditions.
 While modified electron spin Hahn echoes like CPMG and XY8 pulse sequences are commonly employed, they encounter significant limitations in scenarios involving spin-1/2 systems, strongly coupled spins, or nuclear spin baths comprising distinct isotopes.
@@
 This method holds promise across diverse platforms, especially for emerging S=1/2 group IV defects in diamond (e.g., SiV, GeV, SnV, PbV) or silicon (T-centre). 
-We provide a theoretical framework and adapt it for use with color-centers exhibiting various spins.
-Through simulations conducted on nuclear spin clusters, we evaluate different protocols and compare their performance using the Fisher information matrix.
+We provide a theoretical framework and adapt it for the use with color-centers exhibiting various spins.
+Through simulations conducted on nuclear spin clusters, we evaluate different protocols and compare their performance using the Fisher information matrix and Cramer Rao bounds.
 \end{abstract}
@@
 \section{Introduction and background}
-Optically active defects in solids, known as color centers, have been utilized in various quantum applications \cite{awschalom2018quantum}, including quantum networks \cite{pompili2021realization}, quantum sensing \cite{degen2017quantum}, and quantum registers \cite{bradley2019ten}.
+Optically active defects in solids, known as color centers, have been utilized in various quantum applications \cite{awschalom2018quantum}, including quantum networks \cite{pompili2021realization}, quantum sensing \cite{degen2017quantum, meinel2023high}, and quantum registers \cite{bradley2019ten, vorobyov2021quantum, hesselmeier2023measuring, hesselmeier2024high}.
 
@@
 The potential hyperfine interactions with a bath of numerous nuclear spins are crucial for diverse applications, as they offer long-lived quantum memories and enable the creation of an optically accessible nuclear spin qubit register.
-To implement efficient quantum control for these memories, it is imperative to have precise knowledge of the full Hamiltonian governing the register.
+To implement efficient quantum control for these memories, it is imperative to have precise knowledge of the full Hamiltonian governing the register \cite{vorobyov2023transition,bradley2022robust}.
 However, characterizing the hyperfine coupling of nuclear spins can be both challenging and time-consuming \cite{abobeih2019atomic, van2023mapping}. 
@@
 This method could be applied to defects with a specific configuration of nuclear spins, particularly those with a certain relation to the magnetic field and the coupling of the nuclear spins, such as weakly coupled nuclear spins.
-Also, the protocols also can only be applied to electron spins with a specific spin multiplicity.
+Also, the protocols can only be applied to electron spins with a specific spin multiplicity.
 Depending on the applied protocol for the nuclear spins characterisation, the number of identifiable nuclear spin can be different.

### 2024-02-12 article.tex
ready for arxiv

@@
  \affiliation{3rd Physical Institute University of Stuttgart, Germany}%Lines break 
- \affiliation{Max Planck Institute for solid state physics, Stuttgart, Germany}%Lines break 
+ \affiliation{Max Planck Institute for solid state research, Stuttgart, Germany}%Lines break 
  %automatically or can be forced with \\ Third institution, the second for Charlie Author
@@
 Leveraging nearby single-color centers, these spins can be efficiently addressed at the single-site level through spin resonance.
-However, characterising individual nuclear spins is quite cumbersome since the utility of characterisation protocols may differ depending on the strength of the hyperfine coupling, necessitating tailored approaches and experimental conditions.
+However, characterising individual nuclear spins is quite cumbersome since the characterisation protocols may differ depending on the strength of the hyperfine coupling, necessitating tailored approaches and experimental conditions.
 While modified electron spin Hahn echoes like CPMG and XY8 pulse sequences are commonly employed, they encounter significant limitations in scenarios involving spin-1/2 systems, strongly coupled spins, or nuclear spin baths comprising distinct isotopes.
 Here, we present a more straightforward approach for determining the hyperfine interactions among each nuclear and the electron spin. 
-This method holds promise across diverse platforms, especially for emerging S=1/2 group IV defects in diamond (e.g., SiV, GeV, SnV, PbV) or silicon (T-centre). 
-We provide a theoretical framework and adapt it for the use with color-centers exhibiting various spins.
+This method holds promise across diverse platforms, especially for emerging S=1/2 group IV defects in diamond (e.g., SiV, GeV, SnV, PbV) or silicon (T-centre, P-donors). 
+We provide a theoretical framework and adapt it for color-centers exhibiting various spins.
 Through simulations conducted on nuclear spin clusters, we evaluate different protocols and compare their performance using the Fisher information matrix and Cramer Rao bounds.
@@
 \section{Introduction and background}
-Optically active defects in solids, known as color centers, have been utilized in various quantum applications \cite{awschalom2018quantum}, including quantum networks \cite{pompili2021realization}, quantum sensing \cite{degen2017quantum, meinel2023high}, and quantum registers \cite{bradley2019ten, vorobyov2021quantum, hesselmeier2023measuring, hesselmeier2024high}.
+Optically active defects in solids, known as color centers, have been utilized in various quantum applications \cite{awschalom2018quantum}, including quantum networks \cite{pompili2021realization}, quantum sensing \cite{degen2017quantum, meinel2023high}, and quantum registers \cite{bradley2019ten, vorobyov2021quantum, hesselmeier2023measuring, hesselmeier2024high, reiner2024high}.
 
@@
 In particular, we consider the following common examples of nuclear spin registers that are ubiquitous in applications.
-First, the NV-like case with $S=1$ and weakly coupled nuclear spins, operating at high magnetic fields where $\gamma_n B \gg A_{zx}$ which has been extensively studied in the works of \cite{abobeih2019atomic, taminiau2012detection, Zhao:2014aa}.
-The capability to observe narrow peaks with analytically predictable positions and contrasts enables the solution of the inverse problem concerning the characterization of the coupling between nuclear spins and electron spins.
+First, the NV-like case with $S=1$ and weakly coupled nuclear spins, operating at high magnetic fields where $\gamma_n B \gg A_{zx}$ which has been extensively studied \cite{abobeih2019atomic, taminiau2012detection, Zhao:2014aa}.
+The capability to observe narrow peaks with analytically predictable positions and contrasts enables the solution of the inverse problem concerning the characterization of the coupling between nuclear and electron spins.
 The second case (as depicted in Fig.
 \ref{fig:1}b) corresponds to a scenario similar to the first, but with the presence of a strongly coupled nuclear spin, which obstructs the observation of weakly coupled nuclear spins.
-This case is particularly relevant in situations where, in addition to the weakly coupled register, a strongly coupled nuclear spin is utilized, for instance, for repetitive enhancement of the readout.
+This case is particularly relevant in situations where, in addition to the weakly coupled register, a strongly coupled nuclear spin is utilized, for instance, for repetitive enhancement of readout \cite{neumann2010single}.
 This enhancement is achieved by exploiting the strongly coupled ancilla, which is discernible in electron spin resonance spectra.
@@
 For unambiguous reconstruction of the interactions, additional measurements, such as those at different magnetic field strengths, would be required.
-While the double resonance methods \cite{Bradley:2019aa,zaiser2016enhancing} posses a large promise for nuclear spin spectroscopy, they require additional experimental hardware, and often are not available.
+While double resonance methods \cite{Bradley:2019aa,zaiser2016enhancing} hold large promise for nuclear spin spectroscopy, they require additional experimental hardware, and often are not available. 
 Thus, in this work, we investigate the limits of electron spin driven schemes, in particular a correlation-type sequences, which could serve as a general framework and hold promise for the reconstruction of the interactions in all of the aforementioned cases.
@@
 		\includegraphics[width=0.9\textwidth]{pict/dd_compare2.pdf}
-		\caption{Simulated DD signal with 64 $\pi$-pulses for the register reported in  \cite{abobeih2019atomic} consist of 23 nuclear spins, assuming the electron spin is a.
-spin 1 system b.
-spin 1/2 system.
+		\caption{Simulated DD signal with 64 $\pi$-pulses for the register reported in  \cite{abobeih2019atomic} consisting of 23 nuclear spins, assuming the electron spin is a.
+spin $S=1$ system b.
+spin $S=1/2$ system.
 Simulated Fisher information matrix for the case of the electron spin c.
-spin 1 system d.
-spin 1/2 system.
+spin $S=1$ system d.
+spin $S=1/2$ system.
 The first 23 hyperfine parameters are $A_{zz}$ and the second 23 parameters are $A_{zx}$ of the nuclear spin register.}
@@
 %%%%%%%%%%%%%%%Í%%%%=================
-We consider a central spin system of \textit{non-interacting} nuclear spins $I=1/2$ coupled to the central electron spin $\boldsymbol{S}$.
+We consider a central spin system of \textit{non-interacting} nuclear spins $I=1/2$ coupled to a central electron spin $\boldsymbol{S}$.
 The central electron spin is manipulated resonantly with microwave pulses, which transfer the population between the two sublevels denoted as $m_s=s_0$ and $m_s = s_1$.
@@
 The Hamiltonian is diagonal in the electron spin subspace, thus the Hamiltonian for the nuclear spins could be rewritten in the electron spin subdomains $s_i$ ($i=0,1$).
-The nuclear spin Hamiltonian could be solved for eigenenergies, which determine the precession frequencies of $\omega_i = \sqrt{(\omega_L + s_i A_{zz})^2+ (s_i A_{zx})^2}$, $i=0,1$ along the eigenvector axes $\vec{n}i =(\frac{s_i A{zx}}{\omega_i}, 0, \frac{\omega_L + s_i A_{zz}} {\omega_i})$.
+The nuclear spin Hamiltonian could be solved for eigenenergies, which determine the precession frequencies of $\omega_i = \sqrt{(\omega_L + s_i A_{zz})^2+ (s_i A_{zx})^2}$, $i=0,1$ along the eigenvector axes $\vec{n}_i =(\frac{s_i A{zx}}{\omega_i}, 0, \frac{\omega_L + s_i A_{zz}} {\omega_i})$.
 It is assumed that the pulse duration $t_p$ is short enough ($\omega_L t_p \ll 1$) that the nuclear spin dynamics during this time is negligible.
@@
 To proceed with the characterization, Eq. \ref{eq:DD} needs to be further simplified, requiring stronger assumptions.
-Focusing on weakly coupled nuclear spins or high magnetic field situations, the multiplication over all nuclear spins in Eq.
+Focusing on weakly coupled nuclear spins or high magnetic fields, the multiplication over all nuclear spins in Eq.
 \ref{eq:DD} can be approximated by a summation rule, neglecting the higher-order cross-resonance terms:
@@
 Although the Dynamical Decoupling (DD) sequence is well understood and used to characterize nuclear spins, it is not applicable to all systems.
-First, DD only works for defects with high magnetic fields and low hyperfine coupling ($\omega_L \gg A_{zz}, A_{zx}$).
+First, DD only works for defects in high magnetic fields and low hyperfine coupling ($\omega_L \gg A_{zz}, A_{zx}$).
 Second, the signal is limited to the electron spin $T_2$, which only gradually approaches $T_1$.
@@
 		\includegraphics[width=0.9\textwidth]{pict/eseem_compare2.pdf}
-		\caption{Simulated FFT of ESEEM signal with a zoom into weakly coupled nuclear spins for the register reported \cite{abobeih2019atomic} consist of 23 nuclear spins, assuming the electron spin 1/2 system.
+		\caption{Simulated FFT of ESEEM signal with a zoom into weakly coupled nuclear spins for the register reported \cite{abobeih2019atomic} consist of 23 nuclear spins, assuming the electron spin $S=1/2$ system.
 b.
@@
 Simulated Fisher information for the case of the electron spin c.
-one d.
-one-half system.
+$S=1$ d.
+$S=1/2$ system.
 The first 23 hyperfine parameters are $A_{zz}$ and the second 23 parameters are $A_{zx}$ of the nuclear spin register.}
@@
 
-In this work, we consider the 23-nuclear spin cluster characterized in paper \cite{abobeih2019atomic} as a realistic case for our comparison.
+In this work, we consider the 23-nuclear spin cluster characterized previously \cite{abobeih2019atomic} as a realistic case for our comparison.
 First, we apply this to the dynamical decoupling sequence and visualize the obtained results.
@@
 The width of a dip is $\delta \tau = \frac{A_{zx}}{\omega_L^2}$.
-Taking the derivative of the resonance time, we define the sensitivity of the longitudinal hyperfine coupling as follows, using Eq.
+Taking the derivative of the resonance time, we define the sensitivity of the longitudinal hyperfine coupling, using Eq.
 \ref{eq:resonance} to simplify:
@@
 		\includegraphics[width=0.9\textwidth]{pict/fig5.png}
-		\caption{a. FFT of ESEEM signal for $\tau$ from 10 $\mu$s to 500 $\mu$s with the step of 10 $\mu$s b. 2D correlation of each frequency for different $\tau$.}
+		\caption{a. FFT of ESEEM signal for $\tau$ from 10 $\mu$s to 500 $\mu$s with a step of 10 $\mu$s b. 2D correlation of each frequency for different $\tau$.}
 		\label{fig:4}
@@
 \end{equation}
-For the typical case of an NV center with $S=1$, since all the nuclear spin resonances are clearly resolved, the Fisher Information Matrix takes a diagonal shape, revealing low covariance between the various nuclear spin resonances.
+For the typical case of an NV center with $S=1$, since all the nuclear spin resonances are clearly resolved, the Fisher Information Matrix takes a diagonal shape, revealing low covariances between the various nuclear spin resonances.
 There is crosstalk between $A_{zz}$ and $A_{zx}$ for a nuclear spin, as the position of the peaks depends on both values.
@@
 		\includegraphics[width=1.0\textwidth]{pict/cov_compare_vad.pdf}
-		\caption{Visualisation of the CramerRao bound for various protocols on existing nuclear spin dataset from \cite{abobeih2019atomic}}
+		\caption{Visualisation of the CramerRao bound for various protocols on an existing nuclear spin dataset from \cite{abobeih2019atomic}}
 		\label{fig:cov}
@@
 We only consider the available information in the plot, assuming that an optimum estimator for the extraction of that information already exists.
-In reality, one has to additionally assume a non-ideal estimator procedure, which involves the extraction of the hyperfine parameter values from the raw data and is the subject of further work.
+In reality, one has to additionally assume a non-ideal estimator procedure, which involves the extraction of the hyperfine parameter values from the raw data. But this is the subject of further work.
 As a result, we see that while for the DD method, a spin 1/2 case for N=16 pulses allows for the identification of only 3 out of 23 nuclear spins, the 5-pulse ESEEM method works with similar success for both S=1 and S=1/2 systems.
-In total, it is capable of detecting 17-18 out of 23 spins with the constrained measurement time and could be further boosted by using the DD-ESEEM method with multiple pulses in each sensing block analogous to Fig.
+In total, it is capable of detecting 17-18 out of 23 spins within the measurement time constrain.
+This could be further boosted by using the DD-ESEEM method with multiple pulses in each sensing block analogous to Fig.
 \ref{fig:ddeseem}.
@@
 Additionally, our method does not require strong microwave pulse fields since the pulses do not need to cope with the nuclear spin Larmor frequency.
-While we explored various sensing methods in this work, we did not delve into estimator performance.
+While we explore various sensing methods in this work, we did not delve into estimator performance.
 We believe that this aspect should be considered in conjunction with adaptive and optimal strategies for controlling the experimental parameters, such as Bayesian Optimal Experimental Design or Machine Learning, to increase the efficiency of estimation.
@@
 We acknowledge financial support by European Union's Horizon 2020 research and innovation program ASTERIQS under grant No.
-820394, European Research Council advanced grant No.
-742610, SMel, Federal Ministry of Education and Research (BMBF) project MiLiQuant and Quamapolis, Spinning and QR.X the DFG (FOR 2724,INST 41/1109-1 FUGG), the Max Planck Society, and the Volkswagentiftung.
+820394 as well as Spinus, Federal Ministry of Education and Research (BMBF) project MiLiQuant and Quamapolis, Spinning and QR.X the DFG (FOR 2724, INST 41/1109-1 FUGG), the Max Planck Society, and the Volkswagentiftung.
 M.Z.

### 2024-03-27 arxiv/arxiv_main.tex
??

--- 2024-02-12 article.tex
@@
 
-\title{Blueprint for efficient nuclear spin characterization in  color center}% Force line breaks with \\
+\title{Blueprint for efficient nuclear spin characterization with color center}% Force line breaks with \\
 %\thanks{A footnote to the article title}%
@@
 	\begin{center}
-		\includegraphics[width=0.9\textwidth]{pict/drawing0.pdf}
+		\includegraphics[width=0.9\textwidth]{figure_0.pdf}
 		\caption{Comparing DD and five pulse ESEEM as two nuclear spin characterization methods in different systems.
@@
 	\begin{center}
-		\includegraphics[width=0.9\textwidth]{pict/dd_compare2.pdf}
+		\includegraphics[width=0.9\textwidth]{figure_1.pdf}
 		\caption{Simulated DD signal with 64 $\pi$-pulses for the register reported in  \cite{abobeih2019atomic} consisting of 23 nuclear spins, assuming the electron spin is a.
@@
 	\begin{center}
-		\includegraphics[width=0.9\textwidth]{pict/eseem_compare2.pdf}
+		\includegraphics[width=0.9\textwidth]{figure_2.pdf}
 		\caption{Simulated FFT of ESEEM signal with a zoom into weakly coupled nuclear spins for the register reported \cite{abobeih2019atomic} consist of 23 nuclear spins, assuming the electron spin $S=1/2$ system.
@@
 	\begin{center}
-		\includegraphics[width=0.9\textwidth]{pict/fig5.png}
+		\includegraphics[width=0.9\textwidth]{figure_3.png}
 		\caption{a. FFT of ESEEM signal for $\tau$ from 10 $\mu$s to 500 $\mu$s with a step of 10 $\mu$s b. 2D correlation of each frequency for different $\tau$.}
@@
 	\begin{center}
-		\includegraphics[width=1.0\textwidth]{pict/cov_compare_vad.pdf}
+		\includegraphics[width=1.0\textwidth]{figure_4.pdf}
 		\caption{Visualisation of the CramerRao bound for various protocols on an existing nuclear spin dataset from \cite{abobeih2019atomic}}
@@
 	\begin{center}
-		\includegraphics[width=0.9\columnwidth]{pict/seqs.png}
+		\includegraphics[width=0.9\columnwidth]{figure_5.png}
 		\caption{Pulse sequences a. Ramsey b. Hahn Echo c. Dynamical Decoupling d. DDESEEM}
@@
 %pass
-\bibliography{references}% Produces the bibliography via BibTeX.
+%\bibliography{references}% Produces the bibliography via BibTeX.
+\begin{thebibliography}{24}%
+\makeatletter
+\providecommand \@ifxundefined [1]{%
+ \@ifx{#1\undefined}
+}%
+\providecommand \@ifnum [1]{%
+ \ifnum #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \@ifx [1]{%
+ \ifx #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \natexlab [1]{#1}%
+\providecommand \enquote  [1]{``#1''}%
+\providecommand \bibnamefont  [1]{#1}%
+\providecommand \bibfnamefont [1]{#1}%
+\providecommand \citenamefont [1]{#1}%
+\providecommand \href@noop [0]{\@secondoftwo}%
+\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
+\providecommand \@href[1]{\@@startlink{#1}\@@href}%
+\providecommand \@@href[1]{\endgroup#1\@@endlink}%
+\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
+  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
+\providecommand \@@startlink[1]{}%
+\providecommand \@@endlink[0]{}%
+\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
+\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
+\providecommand \urlprefix  [0]{URL }%
+\providecommand \Eprint [0]{\href }%
+\providecommand \doibase [0]{https://doi.org/}%
+\providecommand \selectlanguage [0]{\@gobble}%
+\providecommand \bibinfo  [0]{\@secondoftwo}%
+\providecommand \bibfield  [0]{\@secondoftwo}%
+\providecommand \translation [1]{[#1]}%
+\providecommand \BibitemOpen [0]{}%
+\providecommand \bibitemStop [0]{}%
+\providecommand \bibitemNoStop [0]{.\EOS\space}%
+\providecommand \EOS [0]{\spacefactor3000\relax}%
+\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
+\let\auto@bib@innerbib\@empty
+%</preamble>
+\bibitem [{\citenamefont {Awschalom}\ \emph {et~al.}(2018)\citenamefont
+  {Awschalom}, \citenamefont {Hanson}, \citenamefont {Wrachtrup},\ and\
+  \citenamefont {Zhou}}]{awschalom2018quantum}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~D.}\ \bibnamefont
+  {Awschalom}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Hanson}},
+  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Wrachtrup}},\ and\
+  \bibinfo {author} {\bibfnamefont {B.~B.}\ \bibnamefont {Zhou}},\ }\bibfield
+  {title} {\bibinfo {title} {Quantum technologies with optically interfaced
+  solid-state spins},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+  {journal} {Nature Photonics}\ }\textbf {\bibinfo {volume} {12}},\ \bibinfo
+  {pages} {516} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Pompili}\ \emph {et~al.}(2021)\citenamefont
+  {Pompili}, \citenamefont {Hermans}, \citenamefont {Baier}, \citenamefont
+  {Beukers}, \citenamefont {Humphreys}, \citenamefont {Schouten}, \citenamefont
+  {Vermeulen}, \citenamefont {Tiggelman}, \citenamefont {dos Santos~Martins},
+  \citenamefont {Dirkse} \emph {et~al.}}]{pompili2021realization}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Pompili}}, \bibinfo {author} {\bibfnamefont {S.~L.}\ \bibnamefont
+  {Hermans}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Baier}},
+  \bibinfo {author} {\bibfnamefont {H.~K.}\ \bibnamefont {Beukers}}, \bibinfo
+  {author} {\bibfnamefont {P.~C.}\ \bibnamefont {Humphreys}}, \bibinfo {author}
+  {\bibfnamefont {R.~N.}\ \bibnamefont {Schouten}}, \bibinfo {author}
+  {\bibfnamefont {R.~F.}\ \bibnamefont {Vermeulen}}, \bibinfo {author}
+  {\bibfnamefont {M.~J.}\ \bibnamefont {Tiggelman}}, \bibinfo {author}
+  {\bibfnamefont {L.}~\bibnamefont {dos Santos~Martins}}, \bibinfo {author}
+  {\bibfnamefont {B.}~\bibnamefont {Dirkse}}, \emph {et~al.},\ }\bibfield
+  {title} {\bibinfo {title} {Realization of a multinode quantum network of
+  remote solid-state qubits},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+  {journal} {Science}\ }\textbf {\bibinfo {volume} {372}},\ \bibinfo {pages}
+  {259} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Degen}\ \emph {et~al.}(2017)\citenamefont {Degen},
+  \citenamefont {Reinhard},\ and\ \citenamefont
+  {Cappellaro}}]{degen2017quantum}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~L.}\ \bibnamefont
+  {Degen}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Reinhard}},\
+  and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Cappellaro}},\
+  }\bibfield  {title} {\bibinfo {title} {Quantum sensing},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Reviews of modern physics}\
+  }\textbf {\bibinfo {volume} {89}},\ \bibinfo {pages} {035002} (\bibinfo
+  {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Meinel}\ \emph {et~al.}(2023)\citenamefont {Meinel},
+  \citenamefont {Kwon}, \citenamefont {Maier}, \citenamefont {Dasari},
+  \citenamefont {Sumiya}, \citenamefont {Onoda}, \citenamefont {Isoya},
+  \citenamefont {Vorobyov},\ and\ \citenamefont {Wrachtrup}}]{meinel2023high}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Meinel}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Kwon}},
+  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Maier}}, \bibinfo
+  {author} {\bibfnamefont {D.}~\bibnamefont {Dasari}}, \bibinfo {author}
+  {\bibfnamefont {H.}~\bibnamefont {Sumiya}}, \bibinfo {author} {\bibfnamefont
+  {S.}~\bibnamefont {Onoda}}, \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Isoya}}, \bibinfo {author} {\bibfnamefont
+  {V.}~\bibnamefont {Vorobyov}},\ and\ \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Wrachtrup}},\ }\bibfield  {title} {\bibinfo {title}
+  {High-resolution nanoscale nmr for arbitrary magnetic fields},\ }\href@noop
+  {} {\bibfield  {journal} {\bibinfo  {journal} {Communications Physics}\
+  }\textbf {\bibinfo {volume} {6}},\ \bibinfo {pages} {302} (\bibinfo {year}
+  {2023})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bradley}\ \emph {et~al.}(2019)\citenamefont
+  {Bradley}, \citenamefont {Randall}, \citenamefont {Abobeih}, \citenamefont
+  {Berrevoets}, \citenamefont {Degen}, \citenamefont {Bakker}, \citenamefont
+  {Markham}, \citenamefont {Twitchen},\ and\ \citenamefont
+  {Taminiau}}]{bradley2019ten}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~E.}\ \bibnamefont
+  {Bradley}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Randall}},
+  \bibinfo {author} {\bibfnamefont {M.~H.}\ \bibnamefont {Abobeih}}, \bibinfo
+  {author} {\bibfnamefont {R.}~\bibnamefont {Berrevoets}}, \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Degen}}, \bibinfo {author} {\bibfnamefont
+  {M.~A.}\ \bibnamefont {Bakker}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Markham}}, \bibinfo {author} {\bibfnamefont
+  {D.}~\bibnamefont {Twitchen}},\ and\ \bibinfo {author} {\bibfnamefont
+  {T.~H.}\ \bibnamefont {Taminiau}},\ }\bibfield  {title} {\bibinfo {title} {A
+  ten-qubit solid-state spin register with quantum memory up to one minute},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
+  X}\ }\textbf {\bibinfo {volume} {9}},\ \bibinfo {pages} {031045} (\bibinfo
+  {year} {2019})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Vorobyov}\ \emph {et~al.}(2021)\citenamefont
+  {Vorobyov}, \citenamefont {Zaiser}, \citenamefont {Abt}, \citenamefont
+  {Meinel}, \citenamefont {Dasari}, \citenamefont {Neumann},\ and\
+  \citenamefont {Wrachtrup}}]{vorobyov2021quantum}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
+  {Vorobyov}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Zaiser}},
+  \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Abt}}, \bibinfo {author}
+  {\bibfnamefont {J.}~\bibnamefont {Meinel}}, \bibinfo {author} {\bibfnamefont
+  {D.}~\bibnamefont {Dasari}}, \bibinfo {author} {\bibfnamefont
+  {P.}~\bibnamefont {Neumann}},\ and\ \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Wrachtrup}},\ }\bibfield  {title} {\bibinfo {title}
+  {Quantum fourier transform for nanoscale quantum sensing},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {npj Quantum Information}\
+  }\textbf {\bibinfo {volume} {7}},\ \bibinfo {pages} {124} (\bibinfo {year}
+  {2021})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Hesselmeier}\ \emph {et~al.}(2023)\citenamefont
+  {Hesselmeier}, \citenamefont {Kuna}, \citenamefont {Tak{\'a}cs},
+  \citenamefont {Iv{\'a}dy}, \citenamefont {Knolle}, \citenamefont {Ghezellou},
+  \citenamefont {Ul-Hassan}, \citenamefont {Dasari}, \citenamefont {Kaiser},
+  \citenamefont {Vorobyov} \emph {et~al.}}]{hesselmeier2023measuring}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Hesselmeier}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Kuna}},
+  \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Tak{\'a}cs}}, \bibinfo
+  {author} {\bibfnamefont {V.}~\bibnamefont {Iv{\'a}dy}}, \bibinfo {author}
+  {\bibfnamefont {W.}~\bibnamefont {Knolle}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Ghezellou}}, \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Ul-Hassan}}, \bibinfo {author} {\bibfnamefont
+  {D.}~\bibnamefont {Dasari}}, \bibinfo {author} {\bibfnamefont
+  {F.}~\bibnamefont {Kaiser}}, \bibinfo {author} {\bibfnamefont
+  {V.}~\bibnamefont {Vorobyov}}, \emph {et~al.},\ }\bibfield  {title} {\bibinfo
+  {title} {Measuring nuclear spin qubits by qudit-enhanced spectroscopy in
+  silicon carbide},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {arXiv preprint arXiv:2310.15557}\ } (\bibinfo {year} {2023})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Hesselmeier}\ \emph {et~al.}(2024)\citenamefont
+  {Hesselmeier}, \citenamefont {Kuna}, \citenamefont {Knolle}, \citenamefont
+  {Kaiser}, \citenamefont {Son}, \citenamefont {Ghezellou}, \citenamefont
+  {Ul-Hassan}, \citenamefont {Vorobyov},\ and\ \citenamefont
+  {Wrachtrup}}]{hesselmeier2024high}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Hesselmeier}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Kuna}},
+  \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Knolle}}, \bibinfo
+  {author} {\bibfnamefont {F.}~\bibnamefont {Kaiser}}, \bibinfo {author}
+  {\bibfnamefont {N.~T.}\ \bibnamefont {Son}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Ghezellou}}, \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Ul-Hassan}}, \bibinfo {author} {\bibfnamefont
+  {V.}~\bibnamefont {Vorobyov}},\ and\ \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Wrachtrup}},\ }\bibfield  {title} {\bibinfo {title} {High
+  fidelity optical readout of a nuclear spin qubit in silicon carbide},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {arXiv preprint
+  arXiv:2401.04465}\ } (\bibinfo {year} {2024})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Reiner}\ \emph {et~al.}(2024)\citenamefont {Reiner},
+  \citenamefont {Chung}, \citenamefont {Misha}, \citenamefont {Lehner},
+  \citenamefont {Moehle}, \citenamefont {Poulos}, \citenamefont {Monir},
+  \citenamefont {Charde}, \citenamefont {Macha}, \citenamefont {Kranz} \emph
+  {et~al.}}]{reiner2024high}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Reiner}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Chung}},
+  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Misha}}, \bibinfo
+  {author} {\bibfnamefont {C.}~\bibnamefont {Lehner}}, \bibinfo {author}
+  {\bibfnamefont {C.}~\bibnamefont {Moehle}}, \bibinfo {author} {\bibfnamefont
+  {D.}~\bibnamefont {Poulos}}, \bibinfo {author} {\bibfnamefont
+  {S.}~\bibnamefont {Monir}}, \bibinfo {author} {\bibfnamefont
+  {K.}~\bibnamefont {Charde}}, \bibinfo {author} {\bibfnamefont
+  {P.}~\bibnamefont {Macha}}, \bibinfo {author} {\bibfnamefont
+  {L.}~\bibnamefont {Kranz}}, \emph {et~al.},\ }\bibfield  {title} {\bibinfo
+  {title} {High-fidelity initialization and control of electron and nuclear
+  spins in a four-qubit register},\ }\href@noop {} {\bibfield  {journal}
+  {\bibinfo  {journal} {Nature Nanotechnology}\ ,\ \bibinfo {pages} {1}}
+  (\bibinfo {year} {2024})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Vorobyov}\ \emph {et~al.}(2023)\citenamefont
+  {Vorobyov}, \citenamefont {Meinel}, \citenamefont {Sumiya}, \citenamefont
+  {Onoda}, \citenamefont {Isoya}, \citenamefont {Gulinsky},\ and\ \citenamefont
+  {Wrachtrup}}]{vorobyov2023transition}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.~V.}\ \bibnamefont
+  {Vorobyov}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Meinel}},
+  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Sumiya}}, \bibinfo
+  {author} {\bibfnamefont {S.}~\bibnamefont {Onoda}}, \bibinfo {author}
+  {\bibfnamefont {J.}~\bibnamefont {Isoya}}, \bibinfo {author} {\bibfnamefont
+  {O.}~\bibnamefont {Gulinsky}},\ and\ \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Wrachtrup}},\ }\bibfield  {title} {\bibinfo {title}
+  {Transition from quantum to classical dynamics in weak measurements and
+  reconstruction of quantum correlation},\ }\href@noop {} {\bibfield  {journal}
+  {\bibinfo  {journal} {Physical Review A}\ }\textbf {\bibinfo {volume}
+  {107}},\ \bibinfo {pages} {042212} (\bibinfo {year} {2023})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Bradley}\ \emph {et~al.}(2022)\citenamefont
+  {Bradley}, \citenamefont {de~Bone}, \citenamefont {M{\"o}ller}, \citenamefont
+  {Baier}, \citenamefont {Degen}, \citenamefont {Loenen}, \citenamefont
+  {Bartling}, \citenamefont {Markham}, \citenamefont {Twitchen}, \citenamefont
+  {Hanson} \emph {et~al.}}]{bradley2022robust}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+  {Bradley}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {de~Bone}},
+  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {M{\"o}ller}}, \bibinfo
+  {author} {\bibfnamefont {S.}~\bibnamefont {Baier}}, \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Degen}}, \bibinfo {author} {\bibfnamefont
+  {S.}~\bibnamefont {Loenen}}, \bibinfo {author} {\bibfnamefont
+  {H.}~\bibnamefont {Bartling}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Markham}}, \bibinfo {author} {\bibfnamefont
+  {D.}~\bibnamefont {Twitchen}}, \bibinfo {author} {\bibfnamefont
+  {R.}~\bibnamefont {Hanson}}, \emph {et~al.},\ }\bibfield  {title} {\bibinfo
+  {title} {Robust quantum-network memory based on spin qubits in isotopically
+  engineered diamond},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+  {journal} {npj Quantum Information}\ }\textbf {\bibinfo {volume} {8}},\
+  \bibinfo {pages} {122} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Abobeih}\ \emph {et~al.}(2019)\citenamefont
+  {Abobeih}, \citenamefont {Randall}, \citenamefont {Bradley}, \citenamefont
+  {Bartling}, \citenamefont {Bakker}, \citenamefont {Degen}, \citenamefont
+  {Markham}, \citenamefont {Twitchen},\ and\ \citenamefont
+  {Taminiau}}]{abobeih2019atomic}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Abobeih}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Randall}},
+  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Bradley}}, \bibinfo
+  {author} {\bibfnamefont {H.}~\bibnamefont {Bartling}}, \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Bakker}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Degen}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Markham}}, \bibinfo {author} {\bibfnamefont
+  {D.}~\bibnamefont {Twitchen}},\ and\ \bibinfo {author} {\bibfnamefont
+  {T.}~\bibnamefont {Taminiau}},\ }\bibfield  {title} {\bibinfo {title}
+  {Atomic-scale imaging of a 27-nuclear-spin cluster using a quantum sensor},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nature}\ }\textbf
+  {\bibinfo {volume} {576}},\ \bibinfo {pages} {411} (\bibinfo {year}
+  {2019})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {van~de Stolpe}\ \emph {et~al.}(2023)\citenamefont
+  {van~de Stolpe}, \citenamefont {Kwiatkowski}, \citenamefont {Bradley},
+  \citenamefont {Randall}, \citenamefont {Breitweiser}, \citenamefont
+  {Bassett}, \citenamefont {Markham}, \citenamefont {Twitchen},\ and\
+  \citenamefont {Taminiau}}]{van2023mapping}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {van~de Stolpe}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Kwiatkowski}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+  {Bradley}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Randall}},
+  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Breitweiser}}, \bibinfo
+  {author} {\bibfnamefont {L.}~\bibnamefont {Bassett}}, \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Markham}}, \bibinfo {author} {\bibfnamefont
+  {D.}~\bibnamefont {Twitchen}},\ and\ \bibinfo {author} {\bibfnamefont
+  {T.}~\bibnamefont {Taminiau}},\ }\bibfield  {title} {\bibinfo {title}
+  {Mapping a 50-spin-qubit network through correlated sensing},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {arXiv preprint arXiv:2307.06939}\
+  } (\bibinfo {year} {2023})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Dr{\'e}au}(2012)}]{Dreau:2012aa}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Dr{\'e}au}},\ }\bibfield  {title} {\bibinfo {title} {High-resolution
+  spectroscopy of single nv defects coupled with nearby $^{13}$c nuclear spins
+  in diamond},\ }\bibfield  {journal} {\bibinfo  {journal} {Physical Review B}\
+  }\textbf {\bibinfo {volume} {85}},\ \href
+  {https://doi.org/10.1103/PhysRevB.85.134107} {10.1103/PhysRevB.85.134107}
+  (\bibinfo {year} {2012})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Childress}\ \emph {et~al.}(2006)\citenamefont
+  {Childress}, \citenamefont {Gurudev~Dutt}, \citenamefont {Taylor},
+  \citenamefont {Zibrov}, \citenamefont {Jelezko}, \citenamefont {Wrachtrup},
+  \citenamefont {Hemmer},\ and\ \citenamefont {Lukin}}]{childress2006coherent}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Childress}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Gurudev~Dutt}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Taylor}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Zibrov}},
+  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Jelezko}}, \bibinfo
+  {author} {\bibfnamefont {J.}~\bibnamefont {Wrachtrup}}, \bibinfo {author}
+  {\bibfnamefont {P.}~\bibnamefont {Hemmer}},\ and\ \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Lukin}},\ }\bibfield  {title} {\bibinfo
+  {title} {Coherent dynamics of coupled electron and nuclear spin qubits in
+  diamond},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Science}\ }\textbf {\bibinfo {volume} {314}},\ \bibinfo {pages} {281}
+  (\bibinfo {year} {2006})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Laraoui}\ \emph {et~al.}(2013)\citenamefont
+  {Laraoui}, \citenamefont {Dolde}, \citenamefont {Burk}, \citenamefont
+  {Reinhard}, \citenamefont {Wrachtrup},\ and\ \citenamefont
+  {Meriles}}]{laraoui2013high}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Laraoui}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Dolde}},
+  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Burk}}, \bibinfo {author}
+  {\bibfnamefont {F.}~\bibnamefont {Reinhard}}, \bibinfo {author}
+  {\bibfnamefont {J.}~\bibnamefont {Wrachtrup}},\ and\ \bibinfo {author}
+  {\bibfnamefont {C.~A.}\ \bibnamefont {Meriles}},\ }\bibfield  {title}
+  {\bibinfo {title} {High-resolution correlation spectroscopy of 13c spins near
+  a nitrogen-vacancy centre in diamond},\ }\href@noop {} {\bibfield  {journal}
+  {\bibinfo  {journal} {Nature communications}\ }\textbf {\bibinfo {volume}
+  {4}},\ \bibinfo {pages} {1651} (\bibinfo {year} {2013})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Vorobyov}\ \emph {et~al.}(2022)\citenamefont
+  {Vorobyov}, \citenamefont {Javadzade}, \citenamefont {Joliffe}, \citenamefont
+  {Kaiser},\ and\ \citenamefont {Wrachtrup}}]{vorobyov2022addressing}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
+  {Vorobyov}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Javadzade}},
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Joliffe}}, \bibinfo
+  {author} {\bibfnamefont {F.}~\bibnamefont {Kaiser}},\ and\ \bibinfo {author}
+  {\bibfnamefont {J.}~\bibnamefont {Wrachtrup}},\ }\bibfield  {title} {\bibinfo
+  {title} {Addressing single nuclear spins quantum memories by a central
+  electron spin},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Applied Magnetic Resonance}\ }\textbf {\bibinfo {volume} {53}},\ \bibinfo
+  {pages} {1317} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Taminiau}\ \emph {et~al.}(2012)\citenamefont
+  {Taminiau}, \citenamefont {Wagenaar}, \citenamefont {Van~der Sar},
+  \citenamefont {Jelezko}, \citenamefont {Dobrovitski},\ and\ \citenamefont
+  {Hanson}}]{taminiau2012detection}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Taminiau}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Wagenaar}},
+  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Van~der Sar}}, \bibinfo
+  {author} {\bibfnamefont {F.}~\bibnamefont {Jelezko}}, \bibinfo {author}
+  {\bibfnamefont {V.~V.}\ \bibnamefont {Dobrovitski}},\ and\ \bibinfo {author}
+  {\bibfnamefont {R.}~\bibnamefont {Hanson}},\ }\bibfield  {title} {\bibinfo
+  {title} {Detection and control of individual nuclear spins using a weakly
+  coupled electron spin},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+  {journal} {Physical review letters}\ }\textbf {\bibinfo {volume} {109}},\
+  \bibinfo {pages} {137602} (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Zhao}(2014)}]{Zhao:2014aa}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+  {Zhao}},\ }\bibfield  {title} {\bibinfo {title} {Dynamical decoupling design
+  for identifying weakly coupled nuclear spins in a bath},\ }\bibfield
+  {journal} {\bibinfo  {journal} {Physical Review A}\ }\textbf {\bibinfo
+  {volume} {90}},\ \href {https://doi.org/10.1103/PhysRevA.90.032319}
+  {10.1103/PhysRevA.90.032319} (\bibinfo {year} {2014})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Neumann}\ \emph {et~al.}(2010)\citenamefont
+  {Neumann}, \citenamefont {Beck}, \citenamefont {Steiner}, \citenamefont
+  {Rempp}, \citenamefont {Fedder}, \citenamefont {Hemmer}, \citenamefont
+  {Wrachtrup},\ and\ \citenamefont {Jelezko}}]{neumann2010single}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Neumann}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Beck}},
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Steiner}}, \bibinfo
+  {author} {\bibfnamefont {F.}~\bibnamefont {Rempp}}, \bibinfo {author}
+  {\bibfnamefont {H.}~\bibnamefont {Fedder}}, \bibinfo {author} {\bibfnamefont
+  {P.~R.}\ \bibnamefont {Hemmer}}, \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Wrachtrup}},\ and\ \bibinfo {author} {\bibfnamefont
+  {F.}~\bibnamefont {Jelezko}},\ }\bibfield  {title} {\bibinfo {title}
+  {Single-shot readout of a single nuclear spin},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {science}\ }\textbf {\bibinfo {volume}
+  {329}},\ \bibinfo {pages} {542} (\bibinfo {year} {2010})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Bradley}(2019)}]{Bradley:2019aa}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+  {Bradley}},\ }\bibfield  {title} {\bibinfo {title} {A ten-qubit solid-state
+  spin register with quantum memory up to one minute},\ }\bibfield  {journal}
+  {\bibinfo  {journal} {Physical Review X}\ }\textbf {\bibinfo {volume} {9}},\
+  \href {https://doi.org/10.1103/PhysRevX.9.031045} {10.1103/PhysRevX.9.031045}
+  (\bibinfo {year} {2019})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Zaiser}\ \emph {et~al.}(2016)\citenamefont {Zaiser},
+  \citenamefont {Rendler}, \citenamefont {Jakobi}, \citenamefont {Wolf},
+  \citenamefont {Lee}, \citenamefont {Wagner}, \citenamefont {Bergholm},
+  \citenamefont {Schulte-Herbr{\"u}ggen}, \citenamefont {Neumann},\ and\
+  \citenamefont {Wrachtrup}}]{zaiser2016enhancing}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Zaiser}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Rendler}},
+  \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Jakobi}}, \bibinfo
+  {author} {\bibfnamefont {T.}~\bibnamefont {Wolf}}, \bibinfo {author}
+  {\bibfnamefont {S.-Y.}\ \bibnamefont {Lee}}, \bibinfo {author} {\bibfnamefont
+  {S.}~\bibnamefont {Wagner}}, \bibinfo {author} {\bibfnamefont
+  {V.}~\bibnamefont {Bergholm}}, \bibinfo {author} {\bibfnamefont
+  {T.}~\bibnamefont {Schulte-Herbr{\"u}ggen}}, \bibinfo {author} {\bibfnamefont
+  {P.}~\bibnamefont {Neumann}},\ and\ \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Wrachtrup}},\ }\bibfield  {title} {\bibinfo {title}
+  {Enhancing quantum sensing sensitivity by a quantum memory},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Nature communications}\ }\textbf
+  {\bibinfo {volume} {7}},\ \bibinfo {pages} {12279} (\bibinfo {year}
+  {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kasumaj}\ and\ \citenamefont
+  {Stoll}(2008)}]{kasumaj20085}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
+  {Kasumaj}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Stoll}},\ }\bibfield  {title} {\bibinfo {title} {5-and 6-pulse electron spin
+  echo envelope modulation (eseem) of multi-nuclear spin systems},\ }\href@noop
+  {} {\bibfield  {journal} {\bibinfo  {journal} {Journal of Magnetic
+  Resonance}\ }\textbf {\bibinfo {volume} {190}},\ \bibinfo {pages} {233}
+  (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Stoll}\ \emph {et~al.}(2005)\citenamefont {Stoll},
+  \citenamefont {Calle}, \citenamefont {Mitrikas},\ and\ \citenamefont
+  {Schweiger}}]{stoll2005peak}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Stoll}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Calle}},
+  \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Mitrikas}},\ and\
+  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Schweiger}},\ }\bibfield
+  {title} {\bibinfo {title} {Peak suppression in eseem spectra of multinuclear
+  spin systems},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Journal of Magnetic Resonance}\ }\textbf {\bibinfo {volume} {177}},\
+  \bibinfo {pages} {93} (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
+\end{thebibliography}%
 

### 2024-03-27 PRB/coverletter.tex
created a folder for submission and a coverletter

\documentclass[12pt]{amsart}
\usepackage{geometry} % see geometry.pdf on how to lay out the page. There's lots.
\geometry{a4paper} % or letter or a5paper or ... etc
% \geometry{landscape} % rotated page geometry

% See the ``Article customise'' template for come common customisations
% delete this line to display the current date

%%% BEGIN DOCUMENT
\begin{document}

Dear editor,

Accurate characterisation of the nuclear spin environment is pivotal for understanding of an environment of a solid state register. 
This information is crucial for purificatino of the register operation but also is a resource for extending the regsiter itself, utilising the spins in the environment as so. 
As recently the sucess of the pushing the registers using environmental nuclear spins reached around 50 qubits with most studied NV centers in diamond, a surve for spin characterisation techniques suitable for many other colour centers is long awaited in our opinion. 
Partially this is also motivated by the challenge and interest which a simplest S=1/2 electron spin systems present. 
The most succesfull and widespread technique - namely the dynamical decoupling is not applicable in their case. 
Quite interestingly, a detour to the world of convential EPR type techniques, such as ESEEM, (5p, 3p and more exotic, such as HYSCORE) appears usefull. 
Now applied at the level of single S=1/2 systems, it might overperform the conventional DD sequences in terms of resolution and sensitivity to the hyperfine parameters of the nuclear spins in the bath.  
We quantitatively demonstrate how such sequence performs in various scenarious on the example of the well studied 27 nuclear spin bath.
We utilise the Cramer Rao bound for estimating the uncertainty and number of identified nuclear spins using various techniques.

We strongly believe that our work is of importance for future development of colour centers with S=1/2 electron spins, such as Group IV heavy elements split vacancies, as well as newly developed T centers in Silicon and many others. 
\end{document}

### 2024-05-07 PRB - revision reply/main_revision.tex
revision

--- 2024-03-27 arxiv/arxiv_main.tex
@@
 \end{gather}
-Where $\vec{n}_0 \cdot \vec{n}_1 = \frac{\omega_L^2+(s_0+s_1)A_{zz}+s_0 s_1 (A_{zz}^2+A_{zx}^2)}{\omega_0 \omega_1}$.
+Where $\vec{n}_0 \cdot \vec{n}_1 = \frac{\omega_L^2+(s_0+s_1)A_{zz}+s_0 s_1 (A_{zz}^2+A_{zx}^2)}{\omega_0 \omega_1}$, \textcolor{blue}{which is the inner product of precession axes of a nuclear spin condition on the electron spin sublevel.
+This expression indicates the advantage of using DD sequence for sublevels where either $s_0$ or $s_1$ is zero, only first order parallel hyperfine coupling $\frac{A_{zz}}{\omega_L}$ play a role.
+On the other hand, in spin-1/2 systems ($s_0=-\frac{1}{2}$ and $s_1=\frac{1}{2}$), the first order hyperfine coupling vanishes and only second order parallel hyperfine coupling $(\frac{A_{zz}}{\omega_L})^2$ and second order perpendicular hyperfine coupling $(\frac{A_{zx}}{\omega_L})^2$ remain present.
+This indicates weak sensitivity of DD sequence on different nuclear spins.}
 At this point, it should be clear that the number of pulses can be used as an additional parameter to modify the modulation depth of each nuclear spin.

### 2024-05-07 PRB - revision reply/reply.tex
revision

\documentclass[12pt]{amsart}
\usepackage{geometry} % see geometry.pdf on how to lay out the page. There's lots.
\usepackage[dvipsnames]{xcolor}
\geometry{a4paper} % or letter or a5paper or ... etc
% \geometry{landscape} % rotated page geometry

% See the ``Article customise'' template for come common customisations
% delete this line to display the current date

%%% BEGIN DOCUMENT
\begin{document}
	\color{red} \section{ Report of the First Referee}\\
	The authors compare nuclear spin characterization using ESEEM and DD
	sequences. Overall the work seems timely and appropriate for
	publication in PRB.

	However, I think some sections and figures would benefit from further
	revisions. Below is a list of comments and inquiries:

	1) In some places the authors refer to second order hyperfine
	coupling, I assume this is in regard to the Zeeman splitting of the
	central spin but this could be clarified in the text.

	2) I am not sure whether this is intentional but the equations miss
	punctuation and equation references the brackets.

	3) Some equations are hard to read because they overlap with the text
	of the next column.

	4) Related to 1) additional details to derive the Hamiltonian in Eq.
	(1) would be helpful, for instance when does this equation hold, I
	believe $\Delta \gg$ hyperfine elements is assumed to neglect coupling to Sx and
	Sy and then the nuclear spins are rotated such that there occur no
	terms with Iy? Is there a difference in the derivation for S=1 and
	S=1/2? Maybe an appendix applying the secular approximation and the
	appropriate rotation to the frame leading to this form would be
	helpful for future readers.

	5) Fig. 2 misses the labels for the subfigures the same applies to
	Fig. 3 where I think that additionally the heading of the top left
	panel should read "Electron Spin 1".

	6) In Eq. (2) it would help to provide the state that is used for the
	calculation as well as an intuition why it is sufficient to include
	the exponential decay term after solving the dynamics (and when this
	is valid).

	7) The last paragraph of App. B is very hard to read and would benefit
	from some work on the language.

	8) Could the authors comment on whether they have an intuition whether
	adapted approaches would be feasible for systems with an additional
	central spin like the (15N)V center or defects with even larger spin
	like vanadium defects in silicon carbide?

	9) Could the authors provide a short comment comparing to entanglement
	based approaches for nuclear spin control, e.g.,
	https://www.nature.com/articles/ncomms14660?

	Concluding, if the above points are addressed, I deem the article
	suited for publication within PRB.

	\color{black} \section{Reply to the First Referee}\\
	We appreciate the comments made by the referee. We clarify each point as follows:

	1. Second order hyperfine couplings means terms like $(\frac{A_{zz}}{\omega_L})^2$ and $(\frac{A_{zx}}{\omega_L})^2$. This is stated in the sentence:
	((... the second-order term $\frac{A_{zx}^2}{\omega_L^2}$ can be neglected ... ))

	To clarify this point, we add the following explanation to the text:
	((... \textcolor{blue}{which is the inner product of precession axes of a nuclear spin condition on the electron spin sublevel. This expression indicates the advantage of using DD sequence for sublevels where either $s_0$ or $s_1$ is zero, only first order parallel hyperfine coupling $\frac{A_{zz}}{\omega_L}$ play a role. On the other hand, in spin-1/2 systems ($s_0=-\frac{1}{2}$ and $s_1=\frac{1}{2}$), the first order hyperfine coupling vanishes and only second order parallel hyperfine coupling $(\frac{A_{zz}}{\omega_L})^2$ and second order perpendicular hyperfine coupling $(\frac{A_{zx}}{\omega_L})^2$ remain present. This indicates weak sensitivity of DD sequence on different nuclear spins}...))

	2.

	3.

	4.

	5.

	6.

	7.

	8.

	9.

	\color{red} \section{ Report of the Second Referee}
	The authors propose a blueprint for efficient nuclear spin
	characterization with color centers. The authors claim that they
	propose a more straightforward approach for determining the hyperfine
	interactions among each nuclear and the electron spin. The manuscript
	is written clearly by comparing dynamical decoupling (DD) and Electron
	Spin Echo Envelop Modulation (ESEEM), the numerical results are valid
	and may could be of use in other future experiments. I think the
	results obtained by the authors are of interest for Phys. Rev. B
	readers, so I support the publication in its present form.

	As some minor remarks which the authors may take into account to
	beatify their study further, I would like to mention:

	1) There are no a, b, c and d in Fig. 2, Fig. 3 and Fig.5. There is
	lack of definitions and units of “Hyperfine Parameters” in abscissa in
	Fig. 2 and Fig. 3. This sentence is confusing: “The first 23 hyperfine
	parameters are Azz and the second 23 parameters are Azx of the nuclear
	spin register.” What are the specific meanings of hyperfine parameters
	along horizontal axis and vertical axis in Figs2?

	2) Are there any reasons for the exponential decay part in gray for
	almost all the equations? It is a little bit strange, and the
	exponential decay part looks not in same size as well.

	3) Styles of references [9], [14], [19] and [21] are not uniform with
	other references.

	\color{black} \section{Reply to the Second Referee}

	1.

	2.

	3.

	\color{red} \section{Report of the Third Referee}
	Zahedian et al. present a theoretical study on a the appropriateness of
	various methods of nuclear spin spectroscopy using electron spins in
	solid state materials as probes. They compare dynamical decoupling
	based techniques and consider how using a spin-1/2 system as a probe
	differs to the more common case of a spin-1 (such as the NV center in
	diamond). As the authors note, spin-1/2 electron spin systems are
	emerging in materials such as diamond and silicon and so expanding the
	existing nuclear spectroscopy machinery to this case will be of
	interest to the community.

	The paper and its main result that correlation-style dynamical
	decoupling sequences are most appropriate for performing nuclear spin
	spectroscopy with spin-1/2 electron spin systems should be of interest
	to the community, and so in principle I think it is appropriate to
	publish in PRB. In parts I found the arguments a little unclear and so
	I would recommend some minor revisions before publication. Some
	specific points:

	1) It is not clear to me why the correlation sequence performs much
	worse for the spin-1 probe (comparing Fig 2(c) and 3(c)) and there is
	not much discussion of this point in the text. This result also seems
	to conflict with Fig 5. It also does not seem like the spin-1 probe
	should be worse than spin-1/2 in this case. Also, what are the
	parameters used to generate the plots Fig 3c,d - is it simulating the
	72 pulse DDESEEM?

	2) It would be interesting to know, roughly, how the results of e.g.
	Fig 5 scale with properties such as probe T1 and T2. Does this
	strongly impact the optimal sequence choice? Some spin-1/2 systems may
	have short T1 times as they are able to cross relax with other g=2
	spins present in the crystal (or on the diamond surface, for
	instance).

	3) One goal of mapping e.g. a nuclear spin cluster is to also use the
	central electron spin to selectively manipulate individual nuclear
	spins to use as ancillae or implement quantum information protocols.
	Is it straightforward that the spectral resolution offered by the
	correlation style measurements also allow this sort of control? At
	minimum the extra time overhead from using the longer sequence would
	need to be considered in practice. Could the authors comment on the
	outlook here?

	4) Minor comment on figures: some labels are missing and fig 4 appears
	a bit blurry.

	\color{black} \section{ Reply to the Third Referee}

	1.

	2.

	3.

	4.

\end{document}

### 2024-05-08 PRB - revision reply/main_revision.tex
rv

@@
 \usepackage{hyperref}% add hypertext capabilities
+\usepackage{soul}
 %\usepackage[mathlines]{lineno}% Enable numbering of text and display math
@@
 	(\vec{n_0}\cdot \vec{n_1})\sin(\frac{\omega_0 \tau}{2}) \sin(\frac{\omega_1 \tau}{2}) \Big]^{(j)}
-	\textcolor{gray}{e^{-(\frac{\tau}{T_2^\ast})^m}}
+	%\textcolor{gray}{e^{-(\frac{\tau}{T_2^\ast})^m}}
 \end{gather}	
-The exponential decay is introduced to note the Ramsey signal decays with the electron spin $T_2^\ast$ since the formalism does not account for any relaxation processes.
-The Ramsey sequence is sensitive to detuning since the electron spin is not refocused; however, it is possible to sense nuclear spins with vanishing perpendicular hyperfine coupling.\\
+\st{The exponential decay is introduced to note the Ramsey signal decays with the electron spin $T_2^\ast$ since the formalism does not account for any relaxation processes.}  \textcolor{blue}{We note the expressions do not account for any relaxation processes.} The Ramsey sequence is sensitive to detuning since the electron spin is not refocused \textcolor{blue}{and it decays with the electron spin $T_2^\ast$}; however, it is possible to sense nuclear spins with vanishing perpendicular hyperfine coupling.\\
 
@@
 	\expval{\sigma_z}_{HE} = \prod_{j=1}^n \Big[1 - 2 k^2 
-	\sin^2(\frac{\omega_0 \tau}{2}) \sin^2(\frac{\omega_1 \tau}{2})\Big]^{(j)} \textcolor{gray}{ e^{-\frac{2\tau}{T_2}}}
+	\sin^2(\frac{\omega_0 \tau}{2}) \sin^2(\frac{\omega_1 \tau}{2})\Big]^{(j)} %\textcolor{gray}{ e^{-\frac{2\tau}{T_2}}}
 \end{gather}
@@
 	\prod_{j=1}^n \Big[1- 2 k^2  
-	\sin^2(\frac{\omega_0 \tau}{2}) \sin^2(\frac{\omega_1 \tau}{2}) \frac{\sin^2(\frac{N}{2} \theta)}{\cos^2(\frac{1}{2}\theta)}  \Big]^{(j)} \textcolor{gray}{ e^{-\frac{2N\tau}{T_2(N)}}} 
+	\sin^2(\frac{\omega_0 \tau}{2}) \sin^2(\frac{\omega_1 \tau}{2}) \frac{\sin^2(\frac{N}{2} \theta)}{\cos^2(\frac{1}{2}\theta)}  \Big]^{(j)}
+	%\textcolor{gray}{ e^{-\frac{2N\tau}{T_2(N)}}} 
 \end{gather}
@@
 	\expval{\sigma_z}_{DD} \approx 1 -2
-	\sum_{j=1}^n \Big[ k^2 	 \sin^2(\frac{\omega_0 \tau}{2}) \sin^2(\frac{\omega_1 \tau}{2}) \frac{\sin^2(\frac{N}{2} \theta)}{\cos^2(\frac{1}{2}\theta)}  \Big]^{(j)} \textcolor{gray}{ e^{-\frac{2N\tau}{T_2(N)}}}
+	\sum_{j=1}^n \Big[ k^2 	 \sin^2(\frac{\omega_0 \tau}{2}) \sin^2(\frac{\omega_1 \tau}{2}) \frac{\sin^2(\frac{N}{2} \theta)}{\cos^2(\frac{1}{2}\theta)}  \Big]^{(j)} %\textcolor{gray}{ e^{-\frac{2N\tau}{T_2(N)}}}
 	\label{eq:approx_DD}
@@
 $\tau$ is set to the Larmor bright spot.
-Simulated Fisher information for the case of the electron spin c.
+Simulated Fisher Information 56 by 56 matrix for the case of the electron spin c.
 $S=1$ d.
 $S=1/2$ system.
-The first 23 hyperfine parameters are $A_{zz}$ and the second 23 parameters are $A_{zx}$ of the nuclear spin register.}
+The first 23 hyperfine parameters are $A_{zz}$ and the second 23 parameters are $A_{zx}$ of the nuclear spin register.
+\textcolor{blue}{It indicates the covariance between two parameters.
+The main diagonal appears as each parameter is correlated with itself.
+The side-diagonals indicate the two hyperfine parameters that belong to the same nuclei.}}
 		\label{fig:ddeseem}
@@
 In this work, we consider the 23-nuclear spin cluster characterized previously \cite{abobeih2019atomic} as a realistic case for our comparison.
-First, we apply this to the dynamical decoupling sequence and visualize the obtained results.
+\textcolor{blue}{Each nuclear spin is identified with two hyperfine parameters $A_{zz}$ and $A_{zx}$, which shows coupling to the central electron spin.
+Hence, characterizing this 23-nuclear spins requires identifying 56 hyperfine coupling parameters.}
+First, we apply the Dynamical Decoupling (DD) sequence to this nuclear spin register and visualize the obtained results.
 Fig \ref{fig:3} compares the DD signal for the same nuclear spin register but different defects in diamond.
@@
 \end{equation}
+\textcolor{blue}{the summation is over $\tau$, the pulse timing used in the sequence, and $A$ is the array including all hyperfine coupling parameters.
+For the considered nuclear spin register, $A$ includes 56 hyperfine coupling parameters, the first 23 parameters are $A_{zz}$ of different nuclear spins and the second 23 parameters are $A_{zx}$ respectively, resulting in the Fisher information as a 56 by 56 Matrix.
+Fig.
+\ref{fig:3}c,d visualize Fisher Information matrix element for DD sequence in spin 1 and 1/2 systems.}
 For the typical case of an NV center with $S=1$, since all the nuclear spin resonances are clearly resolved, the Fisher Information Matrix takes a diagonal shape, revealing low covariances between the various nuclear spin resonances.
@@
 		+ \prod_{j=1}^n [\cos(\theta_{W_1 F_0 V_0 V_1^\dagger F_0^\dagger W_0^\dagger})]^{(j)}  \notag \\
-		-\prod_{j=1}^n [\cos(\theta_{W_1 F_0 V_1 V_0^\dagger F_0^\dagger W_0^\dagger})]^{(j)} \Big) \textcolor{gray}{e^{-\frac{2\tau_1+2\tau_2}{T_2}- \frac{T}{T_1}}}
+		-\prod_{j=1}^n [\cos(\theta_{W_1 F_0 V_1 V_0^\dagger F_0^\dagger W_0^\dagger})]^{(j)} \Big)
+		%\textcolor{gray}{e^{-\frac{2\tau_1+2\tau_2}{T_2}- \frac{T}{T_1}}}
 \end{gather}
@@
 
-The blind spot term shows that how this sequence can be engineered to increase or reduce the signal amplitude of one nuclear spin from the spectrum.
-The bright and blind spots of a frequency in the spectrum are as follows:
+The blind spot term, B, shows that how this sequence can be engineered to increase or reduce the signal amplitude of one nuclear spin from the spectrum.
+\st{The bright and blind spots of a frequency in the spectrum are as follows} \textcolor{blue}{The Eq.
+\ref{eq:BS} suggests the bright and blind spots of a frequency can be obtained as follows}:
 \begin{align}
@@
 \end{align}
-The blind spots does not depend only on one frequency but on the nuclear spin.
+\st{The blind spots does not depend only on one frequency but on the nuclear spin.
 It means if one resonant frequency is blinded, the other resonant frequency and all the multiple quantum resonances also vanishes.
@@
 Also, This is very helpful especially in the presence of strongly coupled nuclear spin that suppress other nuclei.
-By sweeping $\tau_1$ and $\tau_2$, one can go through different bright and blind spots of each nuclear spin, observe which two peaks are correlated.
+By sweeping $\tau_1$ and $\tau_2$, one can go through different bright and blind spots of each nuclear spin, observe which two peaks are correlated.}
+
+\textcolor{blue}{The blind spot term depends on both $\tau_1$ and $\tau_2$.
+It means if one resonant frequency is blinded, the other resonant frequency and all the multiple quantum resonances also vanishes.
+This can be used as a manifestation that which two peaks in the frequency spectrum are originating from the same nuclei.
+In other words, choosing $\tau$ such that a particular resonant frequency in the spectrum is blinded, the other resonant frequency of the same nuclear spin will also be blinded and both of them disappear from the frequency spectrum together.
+Moreover, this is very helpful especially in the presence of strongly coupled nuclear spin that suppress other nuclei.
+By sweeping $\tau_1$ and $\tau_2$, one can go through different bright and blind spots of each nuclear spin, and observe correlations between different peaks.}
 

### 2024-05-08 PRB - revision reply/reply.tex
rv

@@
 \begin{document}
-	\color{red} \section{ Report of the First Referee}\\
+	\color{red} \section{ Report of the First Referee}
 	The authors compare nuclear spin characterization using ESEEM and DD
@@
 
-	\color{black} \section{Reply to the First Referee}\\
-	We appreciate the comments made by the referee. We clarify each point as follows:
+	\color{black} \section*{Reply to the First Referee}\\
+	We appreciate the comments made by the referee. We clarify each point as follows:\\
 
@@
 
-	To clarify this point, we add the following explanation to the text:
+	To clarify this point, we add the following explanation to the text:\\
+	((...
+\textcolor{blue}{Each nuclear spin is identified with two hyperfine parameters $A_{zz}$ and $A_{zx}$, which shows coupling to the central electron spin.
+Hence, characterizing this 23-nuclear spins requires identifying 56 hyperfine coupling parameters.} ...)) \\
+
 	((...
@@
 On the other hand, in spin-1/2 systems ($s_0=-\frac{1}{2}$ and $s_1=\frac{1}{2}$), the first order hyperfine coupling vanishes and only second order parallel hyperfine coupling $(\frac{A_{zz}}{\omega_L})^2$ and second order perpendicular hyperfine coupling $(\frac{A_{zx}}{\omega_L})^2$ remain present.
-This indicates weak sensitivity of DD sequence on different nuclear spins}...))
+This indicates weak sensitivity of DD sequence on different nuclear spins}...))\\
 
-	2.
+	Also the following text is added to the caption of Fig 2:\\
+	((...
+\textcolor{blue}{It indicates the covariance between two parameters.
+The main diagonal appears as each parameter is correlated with itself.
+The side-diagonals indicate the two hyperfine parameters that belong to the same nuclei.}} ...)) \\
 
-	3.
+	We remark that no unit for Fig. 2c,d and Fig 3c,d are needed since these figures visualize the Fisher Information matrix elements.
+
+	2. \\
+
+	3. We thank the referee for noting this point. We fixed this issue in Eq. 4 and Eq. 7  \\
 
 	4.
+The Hamiltonian in Eq.
+1 is very well-understood in this community [ref here].
+The Hamiltonian conventionally is written in the rotating frame of applied microwave and consist of Electron and nuclear spin Zeeman energy and dipole interaction between them.
+As it is mentioned in the text, the secular approximation is considered so terms like $S_x, S_y$ do not appear.
+Traditionally, the nuclear spins' frame are rotated such that $I_y$ term do not appear.
+This Hamiltonian applied to any two-level system, e.g., this could be any two spin sublevels in Silicon Carbide (S=3/2)\\
 
 	5.
+We thank the referee for pointing out labels for subfigures (pdf is corrected but latex does not show).
+We fixed this issue.
+In Fig.
+3, we are discussing 5pESEEM sequence mostly for Electron spin 1/2 system.
+We did not include FFT of 5pESEEM sequence for spin 1 system because it works just as good as DD sequence, and does not bring any additional information.
+However, the Fisher information obtained for spin 1 system in Fig.
+3c is good metrics to compare with the result of electron spin 1/2 system in Fig 3d.
+\\
 
 	6.
+The initial state for the Ramsey sequence can be any of the two sublevels of spin system.
+Indeed, the gray exponential decay is not sufficient to describe spin relaxations as mentioned in the text, but it shows the time scale of the decay.
+We thank the referee for this point and we decided to remove this exponential decay to avoid confusion.
+\\
 
-	7.
+	7. We thank the referee for pointing out this issue. We added more explanation to the last paragraph in the Appendix B.
+
+	((...\textcolor{blue}{The blind spot term depends on both $\tau_1$ and $\tau_2$.
+It means if one resonant frequency is blinded, the other resonant frequency and all the multiple quantum resonances also vanishes.
+This can be used as a manifestation that which two peaks in the frequency spectrum are originating from the same nuclei.
+In other words, choosing $\tau$ such that a particular resonant frequency in the spectrum is blinded, the other resonant frequency of the same nuclear spin will also be blinded and both of them disappear from the frequency spectrum together.
+Moreover, this is very helpful especially in the presence of strongly coupled nuclear spin that suppress other nuclei.
+By sweeping $\tau_1$ and $\tau_2$, one can go through different bright and blind spots of each nuclear spin, and observe correlations between different peaks.}...))\\
 
 	8.
+This equations are valid as long as the condition stated before Eq.
+1 are valid.
+Most importantly secular approximation is crucial, and also the nuclear spin should be spin 1/2 like Carbons.
+The Spin of electron spin is not play an important role since they can be well separated and pulses resonant with only an effective two level system can be considered.\\
 
 	9.
+In this work, we address nuclear spins only with microwave driving of the electron spin (did we mention this in the text?).
+Applying another radio frequency (RF) driving adds another experimental challenge to the problem.
+In this case, RF spectroscopy to find and drive individual nuclear spins is required, which can add the required time to image nuclear spins.\\
 
@@
 
-	\color{black} \section{Reply to the Second Referee}
-
+	\color{black} \section*{Reply to the Second Referee}
+	We appreciate the comments made by the referee. We clarify each point as follows:\\
 	1.
+We thank the referee for pointing out labels for subfigures (pdf is corrected but latex does not show).
+We fixed this issue.
+Fig.
+5 does not require subfigure labelling.
+We provided more explanation regarding the hyperfine coupling parameters in the text:
+	((...
+\textcolor{blue}{the summation is over $\tau$, the pulse timing used in the sequence, and $A$ is the array including all hyperfine coupling parameters.
+For the considered nuclear spin register, $A$ includes 56 hyperfine coupling parameters, the first 23 parameters are $A_{zz}$ of different nuclear spins and the second 23 parameters are $A_{zx}$ respectively, resulting in the Fisher information as a 56 by 56 Matrix.} ...))
 
 	2.
+Indeed, the gray exponential decay is not sufficient to describe spin relaxations as mentioned in the text, but it shows the time scale of the decay.
+We thank the referee for this point and we decided to remove this exponential decay to avoid confusion.
 
@@
 
-	\color{black} \section{ Reply to the Third Referee}
-
+	\color{black} \section*{ Reply to the Third Referee}
+	We appreciate the comments made by the referee. We clarify each point as follows:\\
 	1.

### 2024-05-10 PRB - revision reply/reply.tex

@@
 The main diagonal appears as each parameter is correlated with itself.
-The side-diagonals indicate the two hyperfine parameters that belong to the same nuclei.}} ...)) \\
+The side-diagonals indicate the two hyperfine parameters that belong to the same nuclei.} ...)) \\
 
@@
 \textcolor{blue}{the summation is over $\tau$, the pulse timing used in the sequence, and $A$ is the array including all hyperfine coupling parameters.
-For the considered nuclear spin register, $A$ includes 56 hyperfine coupling parameters, the first 23 parameters are $A_{zz}$ of different nuclear spins and the second 23 parameters are $A_{zx}$ respectively, resulting in the Fisher information as a 56 by 56 Matrix.} ...))
+For the considered nuclear spin register, $A$ includes 56 hyperfine coupling parameters, the first 23 parameters are $A_{zz}$ of different nuclear spins and the second 23 parameters are $A_{zx}$ respectively, resulting in the Fisher information as a 56 by 56 Matrix.} ...)) \\
 
@@
 Indeed, the gray exponential decay is not sufficient to describe spin relaxations as mentioned in the text, but it shows the time scale of the decay.
-We thank the referee for this point and we decided to remove this exponential decay to avoid confusion.
+We thank the referee for this point and we decided to remove this exponential decay to avoid confusion.\\
 
@@
 	1.
+Characterization of spin-1 system with both DD and DDESEEM works similarly well.
+Indeed, it is important to observe the diagonal and side-diagonals are distinguishable from in the Fisher Information matrix, which in both Fig.
+2c and 3c are clear.
+However, the color scale is levelled such that in each sequence, the perfomance of spin 1/2 can be compared with spin 1.
+Fig.
+3c, 3d are Fisher Information matrix simulated for 5pESEEM.
+For clarity we added this point in the caption.\\
 
 	2.
+$T_1$ limits the resolution of the frequency spectrum.
+However, $T_2$ limits the weakest nuclear spin that can be addressed.
+Ideally, by increasing number of $\pi$ pulses, this limit can be pushed toward $T_1$.
+(did we mention this in the text?) While short transverse relaxation time tolerable, having short longitudinal relaxation time basically means that nuclear spin is not a desired quantum memory.
+\\
 
-	3.
+	3. Using correlation sequences as quantum gates can be challenging as they are not unitary gates due to transverse relaxation of the spins.\\
 
-	4.
+	4. We thank the referee for pointing out labels for subfigures (pdf is corrected but latex does not show). We fixed this issue. Fig. 5 does not require subfigure labelling.
 

### 2024-05-17 PRB - revision reply/main_revision.tex
v2
new
my changes

@@
 This expression indicates the advantage of using DD sequence for sublevels where either $s_0$ or $s_1$ is zero, only first order parallel hyperfine coupling $\frac{A_{zz}}{\omega_L}$ play a role.
-On the other hand, in spin-1/2 systems ($s_0=-\frac{1}{2}$ and $s_1=\frac{1}{2}$), the first order hyperfine coupling vanishes and only second order parallel hyperfine coupling $(\frac{A_{zz}}{\omega_L})^2$ and second order perpendicular hyperfine coupling $(\frac{A_{zx}}{\omega_L})^2$ remain present.
-This indicates weak sensitivity of DD sequence on different nuclear spins.}
+On the other hand, in spin-1/2 systems ($s_0=-\frac{1}{2}$ and $s_1=\frac{1}{2}$), the first order perturbation correction with respect to hyperfine coupling vanishes and only second order perturbation term with respect to parallel $(\frac{A_{zz}}{\omega_L})^2$  and perpendicular coupling $(\frac{A_{zx}}{\omega_L})^2$ remain present.
+This indicates weak sensitivity of DD sequence on different nuclear spins}.
 At this point, it should be clear that the number of pulses can be used as an additional parameter to modify the modulation depth of each nuclear spin.
@@
 $\tau$ is set to the Larmor bright spot.
-Simulated Fisher Information 56 by 56 matrix for the case of the electron spin c.
+Simulated  \textcolor{blue}{5pESEEM} Fisher Information 56 by 56 matrix for the case of the electron spin c.
 $S=1$ d.
@@
 	\begin{center}
-		\includegraphics[width=0.9\textwidth]{figure_3.png}
+		\includegraphics[width=0.9\textwidth]{figure_3.pdf}
 		\caption{a. FFT of ESEEM signal for $\tau$ from 10 $\mu$s to 500 $\mu$s with a step of 10 $\mu$s b. 2D correlation of each frequency for different $\tau$.}

### 2024-05-17 PRB - revision reply/reply.tex
my changes

@@
 	9) Could the authors provide a short comment comparing to entanglement
-	based approaches for nuclear spin control, e.g.,
+	based approaches for nuclear spin control, e.g. : \\
 	https://www.nature.com/articles/ncomms14660?
@@
 
-	\color{black} \section*{Reply to the First Referee}\\
+	\color{black} \section*{Reply to the First Referee}
 	We appreciate the comments made by the referee. We clarify each point as follows:\\
 
-	1. Second order hyperfine couplings means terms like $(\frac{A_{zz}}{\omega_L})^2$ and $(\frac{A_{zx}}{\omega_L})^2$. This is stated in the sentence:
+	1.
+We thank the Referee for the usefull comment, indeed we used a confusing  formulation.
+Second order hyperfine couplings mean terms like $(\frac{A_{zz}}{\omega_L})^2$ and $(\frac{A_{zx}}{\omega_L})^2$ in the resonance conditions.
+This is stated in the sentence:
 	((... the second-order term $\frac{A_{zx}^2}{\omega_L^2}$ can be neglected ... ))
-
+	We replaced this terms by "second order correction of the resonance with respect to hyperfine parameters", which in our opinion better reflects the meaning. 
 	To clarify this point, we add the following explanation to the text:\\
@@
 
-	((...
-\textcolor{blue}{which is the inner product of precession axes of a nuclear spin condition on the electron spin sublevel.
+	((...\textcolor{blue}{which is the inner product of precession axes of a nuclear spin condition on the electron spin sublevel.
 This expression indicates the advantage of using DD sequence for sublevels where either $s_0$ or $s_1$ is zero, only first order parallel hyperfine coupling $\frac{A_{zz}}{\omega_L}$ play a role.
-On the other hand, in spin-1/2 systems ($s_0=-\frac{1}{2}$ and $s_1=\frac{1}{2}$), the first order hyperfine coupling vanishes and only second order parallel hyperfine coupling $(\frac{A_{zz}}{\omega_L})^2$ and second order perpendicular hyperfine coupling $(\frac{A_{zx}}{\omega_L})^2$ remain present.
+On the other hand, in spin-1/2 systems ($s_0=-\frac{1}{2}$ and $s_1=\frac{1}{2}$), the first order perturbation correction with respect to hyperfine coupling vanishes and only second order perturbation term with respect to parallel $(\frac{A_{zz}}{\omega_L})^2$  and perpendicular coupling $(\frac{A_{zx}}{\omega_L})^2$ remain present.
 This indicates weak sensitivity of DD sequence on different nuclear spins}...))\\
@@
 	4.
-The Hamiltonian in Eq.
+\textcolor{red}{We need to either add a reference or a small paragrah saying why Secular is applied and a $U_{int}$ to rotation frame, now it is too rude answer}The Hamiltonian in Eq.
 1 is very well-understood in this community [ref here].
@@
 
-	5.
-We thank the referee for pointing out labels for subfigures (pdf is corrected but latex does not show).
-We fixed this issue.
-In Fig.
-3, we are discussing 5pESEEM sequence mostly for Electron spin 1/2 system.
+	5. We thank the referee for pointing out labels for subfigures (pdf is corrected but latex does not show). In the revised version of the manuscript we fixed this issue. 
+	In Fig. 3, we are discussing 5pESEEM sequence mostly for Electron spin 1/2 system. 
 	We did not include FFT of 5pESEEM sequence for spin 1 system because it works just as good as DD sequence, and does not bring any additional information. 
-However, the Fisher information obtained for spin 1 system in Fig.
-3c is good metrics to compare with the result of electron spin 1/2 system in Fig 3d.
-\\
+	However, we believe, that the Fisher information obtained for spin 1 system in Fig. 3c is good metrics to compare with the result of electron spin 1/2 system in Fig 3d.  \\
 
 	6.
-The initial state for the Ramsey sequence can be any of the two sublevels of spin system.
-Indeed, the gray exponential decay is not sufficient to describe spin relaxations as mentioned in the text, but it shows the time scale of the decay.
+\textcolor{red}{Initial state should be initialised into superposition of two eigenstates, s0,s1, which can be any, right?}The initial state for the Ramsey sequence can be any of the two sub-levels of spin system.
+Indeed, the grey exponential decay is not sufficient to describe spin relaxations as mentioned in the text, but it shows the time scale of the decay.
 We thank the referee for this point and we decided to remove this exponential decay to avoid confusion.
-\\
+We have added this correction to the main text.
+	\textcolor{blue}{((..initial state is XXX..))}.\\
 
@@
 Most importantly secular approximation is crucial, and also the nuclear spin should be spin 1/2 like Carbons.
-The Spin of electron spin is not play an important role since they can be well separated and pulses resonant with only an effective two level system can be considered.\\
+The spin of electron spin is not playing an important role since various allowed microwave transitions can be well separated and pulses resonant with only an effective two level system can be considered.\\
 
 	9.
-In this work, we address nuclear spins only with microwave driving of the electron spin (did we mention this in the text?).
-Applying another radio frequency (RF) driving adds another experimental challenge to the problem.
-In this case, RF spectroscopy to find and drive individual nuclear spins is required, which can add the required time to image nuclear spins.\\
+In this work, we address nuclear spins only with microwave driving of the electron spin (\textcolor{red}{did we mention this in the text?}).
+Applying another radio frequency (RF) driving adds another experimental challenge to the problem and goes beyond the scope of this work.
+In this case, RF spectroscopy to find and drive individual nuclear spins is required, which can add the required time to image nuclear spins, which was successfully demonstrated in various works for spin 1, 3/2,  \cite{DDRF, ENDOR, SSRV2}.
+We believe that it will as well work well for spin $S=1/2$, as it probes the transition frequency of the nuclear spin in $m_s=1/2$ or $m_s=-1/2$ subdomains, making it sensitive to the first order of the $A_{zz}$ coupling.
+Comparison of various RF assisted protocols goes beyond the scope of the current work and requires further investigation.\\
 
-	\color{red} \section{ Report of the Second Referee}
+	\color{red} \section{Report of the Second Referee}
 	The authors propose a blueprint for efficient nuclear spin
@@
 	2.
-Indeed, the gray exponential decay is not sufficient to describe spin relaxations as mentioned in the text, but it shows the time scale of the decay.
+Indeed, the grey exponential decay is not sufficient to describe spin relaxations as mentioned in the text, but it shows the time scale of the decay.
 We thank the referee for this point and we decided to remove this exponential decay to avoid confusion.\\
 
-	3.
+	3. We thank the referee for noting this and fixed the references in the revised version of the manuscript.
 
@@
 	We appreciate the comments made by the referee. We clarify each point as follows:\\
+
 	1.

### 2024-05-18 PRB - revision reply/reply.tex
iteration finished

@@
 $T_1$ limits the resolution of the frequency spectrum.
-However, $T_2$ limits the weakest nuclear spin that can be addressed.
+However, $T_2$ defines the sensitivity to the weakest nuclear spin that can be addressed.
 Ideally, by increasing number of $\pi$ pulses, this limit can be pushed toward $T_1$.
-(did we mention this in the text?) While short transverse relaxation time tolerable, having short longitudinal relaxation time basically means that nuclear spin is not a desired quantum memory.
+While short transverse relaxation time tolerable, having short longitudinal relaxation time basically means that the system is not suitable for consideration as a desired quantum memory.
 \\
 
-	3. Using correlation sequences as quantum gates can be challenging as they are not unitary gates due to transverse relaxation of the spins.\\
+	3.
+Using correlation sequences as quantum gates can be challenging as they are not unitary gates due to transverse relaxation of the spins.
+However the protection of the central spin during the correlation time $T_c$ or purification of the gate by a heralded projection at the end of the sequence opens the possibility to use them as a gate and requires further investigation.\\
 

### 2024-05-18 PRB - revision reply/main_revision.tex
last update?

@@
 ]{revtex4-2}
+\usepackage{dsfont}
+\usepackage{amsmath}
+\usepackage{amsthm}
+\usepackage{mathtools}
 \usepackage{physics}
@@
 \newcommand{\vvv}[1]{\textcolor{blue}{#1}}
+\newcommand{\kb}[2]{\vert #1 \rangle \langle #2 \vert}
+\newcommand{\caver}[1]{\overline{#1}}
+\setlength{\jot}{8pt}
+%\newcommand{\abs}[1]{\vert #1 \vert}
+\let\oldsubref\subref
+%\renewcommand{\subref}[1]{(\oldsubref{#1})}
+\renewcommand{\vec}[1]{\overrightarrow{#1}}
+\newcommand{\tq}[1]{\textquote{#1}}
 %\usepackage[showframe,%Uncomment any one of the following lines to test 
@@
 These two spin sublevels are separated due to the Zeeman effect and/or zero-field splitting, forming a two-level subsystem with an energy splitting of $\omega_a$.
-The Hamiltonian of the system in the secular approximation and in the rotating frame of the applied microwave $\omega_{mw}$ can be written as:
+The Hamiltonian of the system in the secular approximation and in the rotating frame of the applied microwave $\omega_{mw}$ can be written as \textcolor{blue}{(derivation in \ref{app:Hamiltonian})}:
 \begin{align}
@@
 \end{figure}
+
+\section{Hamiltonian}
+\label{app:Hamiltonian}
+The spin Hamiltonian for many color centers can be written as \cite{schweiger2001principles}:
+\begin{gather}
+	H = \mathbf{D}^\intercal \mathbf{S} \mathbf{D} + \beta_e \mathbf{B}^\intercal \mathbf{g} \mathbf{S} + \beta_n \sum_{k=1}^m g_n^{(k)}  \mathbf{B}^\intercal \mathbf{I}^{(k)} \notag \\
+	+ \sum_{I_k>1/2} (\mathbf{I}^{\intercal} \mathbf{P} \mathbf{I})^{(k)} + \sum_{k=1}^m g_n^{(k)} (\mathbf{S}^\intercal \mathbf{A} \mathbf{I})^{(k)}
+\end{gather}
+Where $\mathbf{S}$ and $\mathbf{I}^{(k)}$ are electron and nuclear spin vector operators, $\mathbf{D}$ is zero field splitting tensor, $\mathbf{B}$ is magnetic field vector, $\mathbf{P}$ is nuclear quadrupole tensor, $\mathbf{A}$ is the hyperfine interaction tensor, $\beta_e = \frac{e \hbar}{2m_e}$ and $\beta_n = \frac{-e \hbar}{2m_n}$ are electron and nuclear Bohr magneton.
+Here, we neglected  nuclear-nuclear interactions.
+Also, due to axial symmetry, the zero field splitting can be simplified.
+We assume the magnetic field is only along the symmetry axis, which we denote as z direction.
+Moreover, the secular terms ($S_zI_x, S_zI_y, S_zI_z$) are just a shift of the energy level that are relevant up to first order, while the non-secular terms ($S_xI_x, S_yI_x, S_zI_z, S_xI_y, S_yI_y, S_zI_y$) mix the electron spin levels, which are largely detuned due to the large zero field splitting.
+Hence, the non-secular terms of Hamiltonian are neglected.
+Furthermore, for each nuclear spin, one can go to the xy frame such that $A_{zy}$ term is zero.
+All in all, the spin Hamiltonian with mentioned considerations can be simplified to:
+\begin{gather}
+	H = D_z S_z^2 + \gamma_e B S_z + \gamma_n B I_z^{(k)} + P_z^{(k)} I_z^{2(k)} \notag \\
+	+ A_{zz}^{(k)} S_z I_z^{(k)} + A_{zx}^{(k)} S_z I_x^{(k)}
+\end{gather}
+The summation over k is omitted due to convenience!
+The coefficient $\gamma_e$ and $\gamma_n$ are electron and nuclear gyromagnetic ratios.
+The coefficients' values for the case of NV center in diamond are $D_z= 2.87$ GHz, $\gamma_e= -2.802$ MHz/G, $\gamma_n^{(^{13}C)}= 1.07$ kHz/G, $\gamma_n^{(^{14}N)}= 0.31$ kHz/G, $P_z^{(^{14}N)}= -5.04$ MHz.
+\\
+
+The electron spin in general can take any value, however resonant microwave pulses are applied only for two of the sublevels.
+Hence, the electron spin is effectively a two-level system.
+The electron spin occupies two of its sublevels that are denoted as $\ket{0} = \ket{m_s=s_0}$ and $\ket{1} = \ket{m_s=s_1}$; in other words:
+\begin{gather}
+	S_z= \begin{pmatrix} s_1 & 0 \\ 0 & s_0\end{pmatrix}
+\end{gather}
+One can show that $S_z^2 = (s_1+s_0)S_z-s_1s_0 \mathds{1}$. 
+We define the transition frequency between two spin sub-levels of the electron spin as $\omega_a = D_z (s_1+s_0)+\gamma_e B $.
+Moreover, we note that since we consider nuclei with spin of one half in the system, the nuclear quadrupole term vanishes.
+The Hamiltonian can be written in terms of Pauli matrices:
+\begin{align}
+	H =\omega_aS_z+ \gamma_n B I_z^{(k)} + A_{zz}^{(k)} S_z I_z^{(k)} + A_{zx}^{(k)} S_z I_x^{(k)}
+\end{align}
+
+The Hamiltonian presented so far does not include the microwave drive field.
+Indeed, the microwave pulses are assumed to be instantaneous, but considering the drive field, the Hamiltonian  should be written in the rotating frame and assume rotating wave approximation.
+This frame should be respected for the rest of sequence.
+Since the rotating frame unitary operator commutes with the $\sigma_z$, the expectation value of this operator in the rotating frame is the same as in the lab frame.
+Eventually, free evolution Hamiltonian in the rotating frame is written as follows:
+\begin{align}
+	H = \Delta S_z + \sum_k (\omega_L^{(k)}  + A_{zz}^{(k)} S_z) I_z^{(k)} + A_{zx}^{(k)} S_z I_x^{(k)}
+\end{align}
+Where $\Delta = \omega_a - \omega_{mw}$ is the detuning.
 
@@
   \bibinfo {pages} {93} (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Schweiger}\ and\ \citenamefont
+  	{Jeschke}(2001)}]{schweiger2001principles}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  		{Schweiger}}\ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  		{Jeschke}},\ }\bibfield  {title} {\bibinfo {title} {Principles of pulse electron paramagnetic resonance} }\href@noop
+  {} {\bibfield  {book} {\bibinfo  {book} {Oxford university press}\ }
+  	(\bibinfo {year} {2001})}\BibitemShut {NoStop}%
 \end{thebibliography}%

### 2024-05-18 PRB - revision reply/reply.tex
last update?

@@
 	4.
-\textcolor{red}{We need to either add a reference or a small paragrah saying why Secular is applied and a $U_{int}$ to rotation frame, now it is too rude answer}The Hamiltonian in Eq.
-1 is very well-understood in this community [ref here].
-The Hamiltonian conventionally is written in the rotating frame of applied microwave and consist of Electron and nuclear spin Zeeman energy and dipole interaction between them.
+\textcolor{brown}{We thank the referee to point out that this Hamiltonian needs further explanation.
+We added an Appendix to explain the derivation of this Hamiltonian.} The Hamiltonian conventionally is written in the rotating frame of applied microwave and consist of Electron and nuclear spin Zeeman energy and dipole interaction between them.
 As it is mentioned in the text, the secular approximation is considered so terms like $S_x, S_y$ do not appear.
@@
 
-	6.
-\textcolor{red}{Initial state should be initialised into superposition of two eigenstates, s0,s1, which can be any, right?}The initial state for the Ramsey sequence can be any of the two sub-levels of spin system.
+	6. \textcolor{red}{Initial state should be initialised into superposition of two eigenstates, s0,s1, which can be any, right?}
+	\textcolor{brown}{No, the initial state is always one of s0 or s1, with the first pi-half pulse, the superposition is created.
+Or one can say I know how to generate an initial superposition state, then the first pi-half pulse is not needed.}
+	The initial state for the Ramsey sequence can be any of the two sub-levels of spin system.
 Indeed, the grey exponential decay is not sufficient to describe spin relaxations as mentioned in the text, but it shows the time scale of the decay.
@@
 
-	9.
-In this work, we address nuclear spins only with microwave driving of the electron spin (\textcolor{red}{did we mention this in the text?}).
+	9. In this work, we address nuclear spins only with microwave driving of the electron spin as we mentioned in the text:\\
+	\textcolor{brown}{((While double resonance methods hold large promise for nuclear spin spectroscopy, they require additional experimental hardware, and often are not available.))}
 	Applying another radio frequency (RF) driving adds another experimental challenge to the problem and goes beyond the scope of this work.
@@
 Characterization of spin-1 system with both DD and DDESEEM works similarly well.
-Indeed, it is important to observe the diagonal and side-diagonals are distinguishable from in the Fisher Information matrix, which in both Fig.
-2c and 3c are clear.
+Indeed, it is important to observe the diagonal and side-diagonals, which are clearly distinguishable in the Fisher Information matrix in both Fig.
+2c and 3c.
 However, the color scale is levelled such that in each sequence, the perfomance of spin 1/2 can be compared with spin 1.

### 2024-06-02 PRB - revision reply/reply.tex
Doing final review

@@
 
-	5. We thank the referee for pointing out labels for subfigures (pdf is corrected but latex does not show). In the revised version of the manuscript we fixed this issue. 
+	5. We thank the referee for pointing out labels for subfigures. In the revised version of the manuscript we fixed this issue. 
 	In Fig. 3, we are discussing 5pESEEM sequence mostly for Electron spin 1/2 system. 
@@
 
-	6. \textcolor{red}{Initial state should be initialised into superposition of two eigenstates, s0,s1, which can be any, right?}
-	\textcolor{brown}{No, the initial state is always one of s0 or s1, with the first pi-half pulse, the superposition is created.
-Or one can say I know how to generate an initial superposition state, then the first pi-half pulse is not needed.}
-	The initial state for the Ramsey sequence can be any of the two sub-levels of spin system.
+	6.
+The initial state for the Ramsey sequence can be any of the two sub-levels of spin system ($s_0, s_1$ etc).
 Indeed, the grey exponential decay is not sufficient to describe spin relaxations as mentioned in the text, but it shows the time scale of the decay.
@@
 We have added this correction to the main text.
-	\textcolor{blue}{((..initial state is XXX..))}.\\
 
@@
 	8.
-This equations are valid as long as the condition stated before Eq.
-1 are valid.
-Most importantly secular approximation is crucial, and also the nuclear spin should be spin 1/2 like Carbons.
+These equations are valid as long as the condition stated before Eq.
+1 are satisfied.
+Most important is secular approximation and the nuclear spin $I = 1/2$, e.g.
+$^{13}C$, $^{15}N$ or $^1 H$ .
 The spin of electron spin is not playing an important role since various allowed microwave transitions can be well separated and pulses resonant with only an effective two level system can be considered.\\
@@
 	Applying another radio frequency (RF) driving adds another experimental challenge to the problem and goes beyond the scope of this work.
-In this case, RF spectroscopy to find and drive individual nuclear spins is required, which can add the required time to image nuclear spins, which was successfully demonstrated in various works for spin 1, 3/2,  \cite{DDRF, ENDOR, SSRV2}.
+In this case, RF spectroscopy to find and drive individual nuclear spins is required, which can add the required time to image nuclear spins, which was successfully demonstrated in various works for spin 1, 3/2,
+(Bradley, C.
+E., et al.
+\textit{PRX}  031045 (2019), Zaiser, S.
+et al.
+\textit{Nat.
+Comm.} 12279 (2016), Hesselmeier E.
+et al.
+\textit{PRL} 180804 (2024)).
 We believe that it will as well work well for spin $S=1/2$, as it probes the transition frequency of the nuclear spin in $m_s=1/2$ or $m_s=-1/2$ subdomains, making it sensitive to the first order of the $A_{zz}$ coupling.
@@
 	1.
-We thank the referee for pointing out labels for subfigures (pdf is corrected but latex does not show).
+We thank the referee for pointing out labels for subfigures.
 We fixed this issue.

### 2024-06-03 PRB - revision reply/main_revision.tex
References are still to be fixed

@@
 %\linenumbers\relax % Commence numbering lines
-\newcommand{\vvv}[1]{\textcolor{blue}{#1}}
+\newcommand{\vvv}[1]{\textcolor{black}{#1}}
 \newcommand{\kb}[2]{\vert #1 \rangle \langle #2 \vert}
@@
 These two spin sublevels are separated due to the Zeeman effect and/or zero-field splitting, forming a two-level subsystem with an energy splitting of $\omega_a$.
-The Hamiltonian of the system in the secular approximation and in the rotating frame of the applied microwave $\omega_{mw}$ can be written as \textcolor{blue}{(derivation in \ref{app:Hamiltonian})}:
+The Hamiltonian of the system in the secular approximation and in the rotating frame of the applied microwave $\omega_{mw}$ can be written as \textcolor{black}{(derivation in \ref{app:Hamiltonian})}:
 \begin{align}
@@
 \end{gather}	
-\st{The exponential decay is introduced to note the Ramsey signal decays with the electron spin $T_2^\ast$ since the formalism does not account for any relaxation processes.}  \textcolor{blue}{We note the expressions do not account for any relaxation processes.} The Ramsey sequence is sensitive to detuning since the electron spin is not refocused \textcolor{blue}{and it decays with the electron spin $T_2^\ast$}; however, it is possible to sense nuclear spins with vanishing perpendicular hyperfine coupling.\\
+%\st{The exponential decay is introduced to note the Ramsey signal decays with the electron spin $T_2^\ast$ since the formalism does not account for any relaxation processes.} 
+ \textcolor{black}{We note the expressions do not account for any relaxation processes.} The Ramsey sequence is sensitive to detuning since the electron spin is not refocused \textcolor{black}{and it decays with the electron spin $T_2^\ast$}; however, it is possible to sense nuclear spins with vanishing perpendicular hyperfine coupling.\\
 
@@
 \end{gather}
-Where $\vec{n}_0 \cdot \vec{n}_1 = \frac{\omega_L^2+(s_0+s_1)A_{zz}+s_0 s_1 (A_{zz}^2+A_{zx}^2)}{\omega_0 \omega_1}$, \textcolor{blue}{which is the inner product of precession axes of a nuclear spin condition on the electron spin sublevel.
+Where $\vec{n}_0 \cdot \vec{n}_1 = \frac{\omega_L^2+(s_0+s_1)A_{zz}+s_0 s_1 (A_{zz}^2+A_{zx}^2)}{\omega_0 \omega_1}$, \textcolor{black}{which is the inner product of precession axes of a nuclear spin condition on the electron spin sublevel.
 This expression indicates the advantage of using DD sequence for sublevels where either $s_0$ or $s_1$ is zero, only first order parallel hyperfine coupling $\frac{A_{zz}}{\omega_L}$ play a role.
@@
 $\tau$ is set to the Larmor bright spot.
-Simulated  \textcolor{blue}{5pESEEM} Fisher Information 56 by 56 matrix for the case of the electron spin c.
+Simulated  \textcolor{black}{5pESEEM} Fisher Information 56 by 56 matrix for the case of the electron spin c.
 $S=1$ d.
@@
 The first 23 hyperfine parameters are $A_{zz}$ and the second 23 parameters are $A_{zx}$ of the nuclear spin register.
-\textcolor{blue}{It indicates the covariance between two parameters.
+\textcolor{black}{It indicates the covariance between two parameters.
 The main diagonal appears as each parameter is correlated with itself.
@@
 In this work, we consider the 23-nuclear spin cluster characterized previously \cite{abobeih2019atomic} as a realistic case for our comparison.
-\textcolor{blue}{Each nuclear spin is identified with two hyperfine parameters $A_{zz}$ and $A_{zx}$, which shows coupling to the central electron spin.
+\textcolor{black}{Each nuclear spin is identified with two hyperfine parameters $A_{zz}$ and $A_{zx}$, which shows coupling to the central electron spin.
 Hence, characterizing this 23-nuclear spins requires identifying 56 hyperfine coupling parameters.}
@@
 \end{equation}
-\textcolor{blue}{the summation is over $\tau$, the pulse timing used in the sequence, and $A$ is the array including all hyperfine coupling parameters.
+\textcolor{black}{the summation is over $\tau$, the pulse timing used in the sequence, and $A$ is the array including all hyperfine coupling parameters.
 For the considered nuclear spin register, $A$ includes 56 hyperfine coupling parameters, the first 23 parameters are $A_{zz}$ of different nuclear spins and the second 23 parameters are $A_{zx}$ respectively, resulting in the Fisher information as a 56 by 56 Matrix.
@@
 The blind spot term, B, shows that how this sequence can be engineered to increase or reduce the signal amplitude of one nuclear spin from the spectrum.
-\st{The bright and blind spots of a frequency in the spectrum are as follows} \textcolor{blue}{The Eq.
+\st{The bright and blind spots of a frequency in the spectrum are as follows} \textcolor{black}{The Eq.
 \ref{eq:BS} suggests the bright and blind spots of a frequency can be obtained as follows}:
@@
 \end{align}
-\st{The blind spots does not depend only on one frequency but on the nuclear spin.
+%\st{The blind spots does not depend only on one frequency but on the nuclear spin.
 It means if one resonant frequency is blinded, the other resonant frequency and all the multiple quantum resonances also vanishes.
@@
 
-\textcolor{blue}{The blind spot term depends on both $\tau_1$ and $\tau_2$.
+\textcolor{black}{The blind spot term depends on both $\tau_1$ and $\tau_2$.
 It means if one resonant frequency is blinded, the other resonant frequency and all the multiple quantum resonances also vanishes.
@@
   {2021})}\BibitemShut {NoStop}%
+  %7
 \bibitem [{\citenamefont {Hesselmeier}\ \emph {et~al.}(2023)\citenamefont
@@
   {NoStop}%
+%8
 \bibitem [{\citenamefont {Hesselmeier}\ \emph {et~al.}(2024)\citenamefont
@@
   fidelity optical readout of a nuclear spin qubit in silicon carbide},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {arXiv preprint
-  arXiv:2401.04465}\ } (\bibinfo {year} {2024})}\BibitemShut {NoStop}%
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review Letters}\ } (\bibinfo {year} {2024})}\BibitemShut {NoStop}%
+%9
 \bibitem [{\citenamefont {Reiner}\ \emph {et~al.}(2024)\citenamefont {Reiner},
@@
   (\bibinfo {year} {2024})}\BibitemShut {NoStop}%
+%10
 \bibitem [{\citenamefont {Vorobyov}\ \emph {et~al.}(2023)\citenamefont

### 2024-06-03 PRB - revision reply/references_exampe.tex
References are still to be fixed

--- 2024-05-18 PRB - revision reply/reply.tex
@@
 \usepackage{geometry} % see geometry.pdf on how to lay out the page. There's lots.
-\usepackage[dvipsnames]{xcolor}
 \geometry{a4paper} % or letter or a5paper or ... etc
@@
 % See the ``Article customise'' template for come common customisations
-% delete this line to display the current date
+
+\title{asdf}
+\author{sdf}
+\date{} % delete this line to display the current date
 
@@
 \begin{document}
-	\color{red} \section{ Report of the First Referee}
-	The authors compare nuclear spin characterization using ESEEM and DD
-	sequences. Overall the work seems timely and appropriate for
-	publication in PRB.
 
-	However, I think some sections and figures would benefit from further
-	revisions. Below is a list of comments and inquiries:
+\maketitle
+\tableofcontents
 
-	1) In some places the authors refer to second order hyperfine
-	coupling, I assume this is in regard to the Zeeman splitting of the
-	central spin but this could be clarified in the text.
-
-	2) I am not sure whether this is intentional but the equations miss
-	punctuation and equation references the brackets.
-
-	3) Some equations are hard to read because they overlap with the text
-	of the next column.
-
-	4) Related to 1) additional details to derive the Hamiltonian in Eq.
-	(1) would be helpful, for instance when does this equation hold, I
-	believe $\Delta \gg$ hyperfine elements is assumed to neglect coupling to Sx and
-	Sy and then the nuclear spins are rotated such that there occur no
-	terms with Iy? Is there a difference in the derivation for S=1 and
-	S=1/2? Maybe an appendix applying the secular approximation and the
-	appropriate rotation to the frame leading to this form would be
-	helpful for future readers.
-
-	5) Fig. 2 misses the labels for the subfigures the same applies to
-	Fig. 3 where I think that additionally the heading of the top left
-	panel should read "Electron Spin 1".
-
-	6) In Eq. (2) it would help to provide the state that is used for the
-	calculation as well as an intuition why it is sufficient to include
-	the exponential decay term after solving the dynamics (and when this
-	is valid).
-
-	7) The last paragraph of App. B is very hard to read and would benefit
-	from some work on the language.
-
-	8) Could the authors comment on whether they have an intuition whether
-	adapted approaches would be feasible for systems with an additional
-	central spin like the (15N)V center or defects with even larger spin
-	like vanadium defects in silicon carbide?
-
-	9) Could the authors provide a short comment comparing to entanglement
-	based approaches for nuclear spin control, e.g. : \\
-	https://www.nature.com/articles/ncomms14660?
-
-	Concluding, if the above points are addressed, I deem the article
-	suited for publication within PRB.
-
-	\color{black} \section*{Reply to the First Referee}
-	We appreciate the comments made by the referee. We clarify each point as follows:\\
-
-	1.
-We thank the Referee for the usefull comment, indeed we used a confusing  formulation.
-Second order hyperfine couplings mean terms like $(\frac{A_{zz}}{\omega_L})^2$ and $(\frac{A_{zx}}{\omega_L})^2$ in the resonance conditions.
-This is stated in the sentence:
-	((... the second-order term $\frac{A_{zx}^2}{\omega_L^2}$ can be neglected ... ))
-	We replaced this terms by "second order correction of the resonance with respect to hyperfine parameters", which in our opinion better reflects the meaning. 
-	To clarify this point, we add the following explanation to the text:\\
-	((...
-\textcolor{blue}{Each nuclear spin is identified with two hyperfine parameters $A_{zz}$ and $A_{zx}$, which shows coupling to the central electron spin.
-Hence, characterizing this 23-nuclear spins requires identifying 56 hyperfine coupling parameters.} ...)) \\
-
-	((...\textcolor{blue}{which is the inner product of precession axes of a nuclear spin condition on the electron spin sublevel.
-This expression indicates the advantage of using DD sequence for sublevels where either $s_0$ or $s_1$ is zero, only first order parallel hyperfine coupling $\frac{A_{zz}}{\omega_L}$ play a role.
-On the other hand, in spin-1/2 systems ($s_0=-\frac{1}{2}$ and $s_1=\frac{1}{2}$), the first order perturbation correction with respect to hyperfine coupling vanishes and only second order perturbation term with respect to parallel $(\frac{A_{zz}}{\omega_L})^2$  and perpendicular coupling $(\frac{A_{zx}}{\omega_L})^2$ remain present.
-This indicates weak sensitivity of DD sequence on different nuclear spins}...))\\
-
-	Also the following text is added to the caption of Fig 2:\\
-	((...
-\textcolor{blue}{It indicates the covariance between two parameters.
-The main diagonal appears as each parameter is correlated with itself.
-The side-diagonals indicate the two hyperfine parameters that belong to the same nuclei.} ...)) \\
-
-	We remark that no unit for Fig. 2c,d and Fig 3c,d are needed since these figures visualize the Fisher Information matrix elements.
-
-	2. \\
-
-	3. We thank the referee for noting this point. We fixed this issue in Eq. 4 and Eq. 7  \\
-
-	4.
-\textcolor{red}{We need to either add a reference or a small paragrah saying why Secular is applied and a $U_{int}$ to rotation frame, now it is too rude answer}The Hamiltonian in Eq.
-1 is very well-understood in this community [ref here].
-The Hamiltonian conventionally is written in the rotating frame of applied microwave and consist of Electron and nuclear spin Zeeman energy and dipole interaction between them.
-As it is mentioned in the text, the secular approximation is considered so terms like $S_x, S_y$ do not appear.
-Traditionally, the nuclear spins' frame are rotated such that $I_y$ term do not appear.
-This Hamiltonian applied to any two-level system, e.g., this could be any two spin sublevels in Silicon Carbide (S=3/2)\\
-
-	5. We thank the referee for pointing out labels for subfigures (pdf is corrected but latex does not show). In the revised version of the manuscript we fixed this issue. 
-	In Fig. 3, we are discussing 5pESEEM sequence mostly for Electron spin 1/2 system. 
-	We did not include FFT of 5pESEEM sequence for spin 1 system because it works just as good as DD sequence, and does not bring any additional information. 
-	However, we believe, that the Fisher information obtained for spin 1 system in Fig. 3c is good metrics to compare with the result of electron spin 1/2 system in Fig 3d.  \\
-
-	6.
-\textcolor{red}{Initial state should be initialised into superposition of two eigenstates, s0,s1, which can be any, right?}The initial state for the Ramsey sequence can be any of the two sub-levels of spin system.
-Indeed, the grey exponential decay is not sufficient to describe spin relaxations as mentioned in the text, but it shows the time scale of the decay.
-We thank the referee for this point and we decided to remove this exponential decay to avoid confusion.
-We have added this correction to the main text.
-	\textcolor{blue}{((..initial state is XXX..))}.\\
-
-	7. We thank the referee for pointing out this issue. We added more explanation to the last paragraph in the Appendix B.
-
-	((...\textcolor{blue}{The blind spot term depends on both $\tau_1$ and $\tau_2$.
-It means if one resonant frequency is blinded, the other resonant frequency and all the multiple quantum resonances also vanishes.
-This can be used as a manifestation that which two peaks in the frequency spectrum are originating from the same nuclei.
-In other words, choosing $\tau$ such that a particular resonant frequency in the spectrum is blinded, the other resonant frequency of the same nuclear spin will also be blinded and both of them disappear from the frequency spectrum together.
-Moreover, this is very helpful especially in the presence of strongly coupled nuclear spin that suppress other nuclei.
-By sweeping $\tau_1$ and $\tau_2$, one can go through different bright and blind spots of each nuclear spin, and observe correlations between different peaks.}...))\\
-
-	8.
-This equations are valid as long as the condition stated before Eq.
-1 are valid.
-Most importantly secular approximation is crucial, and also the nuclear spin should be spin 1/2 like Carbons.
-The spin of electron spin is not playing an important role since various allowed microwave transitions can be well separated and pulses resonant with only an effective two level system can be considered.\\
-
-	9.
-In this work, we address nuclear spins only with microwave driving of the electron spin (\textcolor{red}{did we mention this in the text?}).
-Applying another radio frequency (RF) driving adds another experimental challenge to the problem and goes beyond the scope of this work.
-In this case, RF spectroscopy to find and drive individual nuclear spins is required, which can add the required time to image nuclear spins, which was successfully demonstrated in various works for spin 1, 3/2,  \cite{DDRF, ENDOR, SSRV2}.
-We believe that it will as well work well for spin $S=1/2$, as it probes the transition frequency of the nuclear spin in $m_s=1/2$ or $m_s=-1/2$ subdomains, making it sensitive to the first order of the $A_{zz}$ coupling.
-Comparison of various RF assisted protocols goes beyond the scope of the current work and requires further investigation.\\
-
-	\color{red} \section{Report of the Second Referee}
-	The authors propose a blueprint for efficient nuclear spin
-	characterization with color centers. The authors claim that they
-	propose a more straightforward approach for determining the hyperfine
-	interactions among each nuclear and the electron spin. The manuscript
-	is written clearly by comparing dynamical decoupling (DD) and Electron
-	Spin Echo Envelop Modulation (ESEEM), the numerical results are valid
-	and may could be of use in other future experiments. I think the
-	results obtained by the authors are of interest for Phys. Rev. B
-	readers, so I support the publication in its present form.
-
-	As some minor remarks which the authors may take into account to
-	beatify their study further, I would like to mention:
-
-	1) There are no a, b, c and d in Fig. 2, Fig. 3 and Fig.5. There is
-	lack of definitions and units of “Hyperfine Parameters” in abscissa in
-	Fig. 2 and Fig. 3. This sentence is confusing: “The first 23 hyperfine
-	parameters are Azz and the second 23 parameters are Azx of the nuclear
-	spin register.” What are the specific meanings of hyperfine parameters
-	along horizontal axis and vertical axis in Figs2?
-
-	2) Are there any reasons for the exponential decay part in gray for
-	almost all the equations? It is a little bit strange, and the
-	exponential decay part looks not in same size as well.
-
-	3) Styles of references [9], [14], [19] and [21] are not uniform with
-	other references.
-
-	\color{black} \section*{Reply to the Second Referee}
-	We appreciate the comments made by the referee. We clarify each point as follows:\\
-	1.
-We thank the referee for pointing out labels for subfigures (pdf is corrected but latex does not show).
-We fixed this issue.
-Fig.
-5 does not require subfigure labelling.
-We provided more explanation regarding the hyperfine coupling parameters in the text:
-	((...
-\textcolor{blue}{the summation is over $\tau$, the pulse timing used in the sequence, and $A$ is the array including all hyperfine coupling parameters.
-For the considered nuclear spin register, $A$ includes 56 hyperfine coupling parameters, the first 23 parameters are $A_{zz}$ of different nuclear spins and the second 23 parameters are $A_{zx}$ respectively, resulting in the Fisher information as a 56 by 56 Matrix.} ...)) \\
-
-	2.
-Indeed, the grey exponential decay is not sufficient to describe spin relaxations as mentioned in the text, but it shows the time scale of the decay.
-We thank the referee for this point and we decided to remove this exponential decay to avoid confusion.\\
-
-	3. We thank the referee for noting this and fixed the references in the revised version of the manuscript.
-
-	\color{red} \section{Report of the Third Referee}
-	Zahedian et al. present a theoretical study on a the appropriateness of
-	various methods of nuclear spin spectroscopy using electron spins in
-	solid state materials as probes. They compare dynamical decoupling
-	based techniques and consider how using a spin-1/2 system as a probe
-	differs to the more common case of a spin-1 (such as the NV center in
-	diamond). As the authors note, spin-1/2 electron spin systems are
-	emerging in materials such as diamond and silicon and so expanding the
-	existing nuclear spectroscopy machinery to this case will be of
-	interest to the community.
-
-	The paper and its main result that correlation-style dynamical
-	decoupling sequences are most appropriate for performing nuclear spin
-	spectroscopy with spin-1/2 electron spin systems should be of interest
-	to the community, and so in principle I think it is appropriate to
-	publish in PRB. In parts I found the arguments a little unclear and so
-	I would recommend some minor revisions before publication. Some
-	specific points:
-
-	1) It is not clear to me why the correlation sequence performs much
-	worse for the spin-1 probe (comparing Fig 2(c) and 3(c)) and there is
-	not much discussion of this point in the text. This result also seems
-	to conflict with Fig 5. It also does not seem like the spin-1 probe
-	should be worse than spin-1/2 in this case. Also, what are the
-	parameters used to generate the plots Fig 3c,d - is it simulating the
-	72 pulse DDESEEM?
-
-	2) It would be interesting to know, roughly, how the results of e.g.
-	Fig 5 scale with properties such as probe T1 and T2. Does this
-	strongly impact the optimal sequence choice? Some spin-1/2 systems may
-	have short T1 times as they are able to cross relax with other g=2
-	spins present in the crystal (or on the diamond surface, for
-	instance).
-
-	3) One goal of mapping e.g. a nuclear spin cluster is to also use the
-	central electron spin to selectively manipulate individual nuclear
-	spins to use as ancillae or implement quantum information protocols.
-	Is it straightforward that the spectral resolution offered by the
-	correlation style measurements also allow this sort of control? At
-	minimum the extra time overhead from using the longer sequence would
-	need to be considered in practice. Could the authors comment on the
-	outlook here?
-
-	4) Minor comment on figures: some labels are missing and fig 4 appears
-	a bit blurry.
-
-	\color{black} \section*{ Reply to the Third Referee}
-	We appreciate the comments made by the referee. We clarify each point as follows:\\
-
-	1.
-Characterization of spin-1 system with both DD and DDESEEM works similarly well.
-Indeed, it is important to observe the diagonal and side-diagonals are distinguishable from in the Fisher Information matrix, which in both Fig.
-2c and 3c are clear.
-However, the color scale is levelled such that in each sequence, the perfomance of spin 1/2 can be compared with spin 1.
-Fig.
-3c, 3d are Fisher Information matrix simulated for 5pESEEM.
-For clarity we added this point in the caption.\\
-
-	2.
-$T_1$ limits the resolution of the frequency spectrum.
-However, $T_2$ defines the sensitivity to the weakest nuclear spin that can be addressed.
-Ideally, by increasing number of $\pi$ pulses, this limit can be pushed toward $T_1$.
-While short transverse relaxation time tolerable, having short longitudinal relaxation time basically means that the system is not suitable for consideration as a desired quantum memory.
-\\
-
-	3.
-Using correlation sequences as quantum gates can be challenging as they are not unitary gates due to transverse relaxation of the spins.
-However the protection of the central spin during the correlation time $T_c$ or purification of the gate by a heralded projection at the end of the sequence opens the possibility to use them as a gate and requires further investigation.\\
-
-	4. We thank the referee for pointing out labels for subfigures (pdf is corrected but latex does not show). We fixed this issue. Fig. 5 does not require subfigure labelling.
+\section{111}
+\subsection{2323}
+\cite{}
+\bibliography{references}
 

### 2024-06-03 PRB - revision reply/main_revision.tex
resubmitted

@@
 \section{Introduction and background}
-Optically active defects in solids, known as color centers, have been utilized in various quantum applications \cite{awschalom2018quantum}, including quantum networks \cite{pompili2021realization}, quantum sensing \cite{degen2017quantum, meinel2023high}, and quantum registers \cite{bradley2019ten, vorobyov2021quantum, hesselmeier2023measuring, hesselmeier2024high, reiner2024high}.
+Optically active defects in solids, known as color centers, have been utilized in various quantum applications \cite{awschalom2018quantum}, including quantum networks \cite{pompili2021realization}, quantum sensing \cite{degen2017quantum, meinel2023high}, and quantum registers \cite{bradley2019ten, vorobyov2021quantum, hesselmeier2024qudit, hesselmeier2024high, reiner2024high}.
 
@@
 To implement efficient quantum control for these memories, it is imperative to have precise knowledge of the full Hamiltonian governing the register \cite{vorobyov2023transition,bradley2022robust}.
-However, characterizing the hyperfine coupling of nuclear spins can be both challenging and time-consuming \cite{abobeih2019atomic, van2023mapping}. 
-Traditionally, nuclear spin characterization is accomplished through Optically Detected Magnetic Resonance (ODMR) \cite{Dreau:2012aa,hesselmeier2023measuring}, but the spectroscopic resolution is constrained by the $1/T_2^\ast$ of the electron spin.
+However, characterizing the hyperfine coupling of nuclear spins can be both challenging and time-consuming \cite{abobeih2019atomic, van2024mapping}. 
+Traditionally, nuclear spin characterization is accomplished through Optically Detected Magnetic Resonance (ODMR) \cite{dreau2012high,hesselmeier2024qudit}, but the spectroscopic resolution is constrained by the $1/T_2^\ast$ of the electron spin.
 To overcome this limitation, Hahn-Echo-type sequences have been employed to refocus the electron spin and extend its coherence time \cite{childress2006coherent}, thereby improving the resolution to $1/T_2$.
@@
 In particular, we consider the following common examples of nuclear spin registers that are ubiquitous in applications.
-First, the NV-like case with $S=1$ and weakly coupled nuclear spins, operating at high magnetic fields where $\gamma_n B \gg A_{zx}$ which has been extensively studied \cite{abobeih2019atomic, taminiau2012detection, Zhao:2014aa}.
+First, the NV-like case with $S=1$ and weakly coupled nuclear spins, operating at high magnetic fields where $\gamma_n B \gg A_{zx}$ which has been extensively studied \cite{abobeih2019atomic, taminiau2012detection, zhao2014dynamical}.
 The capability to observe narrow peaks with analytically predictable positions and contrasts enables the solution of the inverse problem concerning the characterization of the coupling between nuclear and electron spins.
@@
 For unambiguous reconstruction of the interactions, additional measurements, such as those at different magnetic field strengths, would be required.
-While double resonance methods \cite{Bradley:2019aa,zaiser2016enhancing} hold large promise for nuclear spin spectroscopy, they require additional experimental hardware, and often are not available. 
+While double resonance methods \cite{bradley2019ten,zaiser2016enhancing} hold large promise for nuclear spin spectroscopy, they require additional experimental hardware, and often are not available. 
 Thus, in this work, we investigate the limits of electron spin driven schemes, in particular a correlation-type sequences, which could serve as a general framework and hold promise for the reconstruction of the interactions in all of the aforementioned cases.
@@
 \label{app:Hamiltonian}
-The spin Hamiltonian for many color centers can be written as \cite{schweiger2001principles}:
+The spin Hamiltonian for many color centers can be written as\cite{Schweiger2001Principles}:
 \begin{gather}
@@
 The blind spot term, B, shows that how this sequence can be engineered to increase or reduce the signal amplitude of one nuclear spin from the spectrum. 
-\st{The bright and blind spots of a frequency in the spectrum are as follows} \textcolor{black}{The Eq.
-\ref{eq:BS} suggests the bright and blind spots of a frequency can be obtained as follows}:
+%\st{The bright and blind spots of a frequency in the spectrum are as follows} 
+\textcolor{black}{The Eq. \ref{eq:BS} suggests the bright and blind spots of a frequency can be obtained as follows}:
 \begin{align}
@@
 %pass
-%\bibliography{references}% Produces the bibliography via BibTeX.
-\begin{thebibliography}{24}%
-\makeatletter
-\providecommand \@ifxundefined [1]{%
- \@ifx{#1\undefined}
-}%
-\providecommand \@ifnum [1]{%
- \ifnum #1\expandafter \@firstoftwo
- \else \expandafter \@secondoftwo
- \fi
-}%
-\providecommand \@ifx [1]{%
- \ifx #1\expandafter \@firstoftwo
- \else \expandafter \@secondoftwo
- \fi
-}%
-\providecommand \natexlab [1]{#1}%
-\providecommand \enquote  [1]{``#1''}%
-\providecommand \bibnamefont  [1]{#1}%
-\providecommand \bibfnamefont [1]{#1}%
-\providecommand \citenamefont [1]{#1}%
-\providecommand \href@noop [0]{\@secondoftwo}%
-\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
-\providecommand \@href[1]{\@@startlink{#1}\@@href}%
-\providecommand \@@href[1]{\endgroup#1\@@endlink}%
-\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
-  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
-\providecommand \@@startlink[1]{}%
-\providecommand \@@endlink[0]{}%
-\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
-\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
-\providecommand \urlprefix  [0]{URL }%
-\providecommand \Eprint [0]{\href }%
-\providecommand \doibase [0]{https://doi.org/}%
-\providecommand \selectlanguage [0]{\@gobble}%
-\providecommand \bibinfo  [0]{\@secondoftwo}%
-\providecommand \bibfield  [0]{\@secondoftwo}%
-\providecommand \translation [1]{[#1]}%
-\providecommand \BibitemOpen [0]{}%
-\providecommand \bibitemStop [0]{}%
-\providecommand \bibitemNoStop [0]{.\EOS\space}%
-\providecommand \EOS [0]{\spacefactor3000\relax}%
-\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
-\let\auto@bib@innerbib\@empty
-%</preamble>
-\bibitem [{\citenamefont {Awschalom}\ \emph {et~al.}(2018)\citenamefont
-  {Awschalom}, \citenamefont {Hanson}, \citenamefont {Wrachtrup},\ and\
-  \citenamefont {Zhou}}]{awschalom2018quantum}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~D.}\ \bibnamefont
-  {Awschalom}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Hanson}},
-  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Wrachtrup}},\ and\
-  \bibinfo {author} {\bibfnamefont {B.~B.}\ \bibnamefont {Zhou}},\ }\bibfield
-  {title} {\bibinfo {title} {Quantum technologies with optically interfaced
-  solid-state spins},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-  {journal} {Nature Photonics}\ }\textbf {\bibinfo {volume} {12}},\ \bibinfo
-  {pages} {516} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Pompili}\ \emph {et~al.}(2021)\citenamefont
-  {Pompili}, \citenamefont {Hermans}, \citenamefont {Baier}, \citenamefont
-  {Beukers}, \citenamefont {Humphreys}, \citenamefont {Schouten}, \citenamefont
-  {Vermeulen}, \citenamefont {Tiggelman}, \citenamefont {dos Santos~Martins},
-  \citenamefont {Dirkse} \emph {et~al.}}]{pompili2021realization}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Pompili}}, \bibinfo {author} {\bibfnamefont {S.~L.}\ \bibnamefont
-  {Hermans}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Baier}},
-  \bibinfo {author} {\bibfnamefont {H.~K.}\ \bibnamefont {Beukers}}, \bibinfo
-  {author} {\bibfnamefont {P.~C.}\ \bibnamefont {Humphreys}}, \bibinfo {author}
-  {\bibfnamefont {R.~N.}\ \bibnamefont {Schouten}}, \bibinfo {author}
-  {\bibfnamefont {R.~F.}\ \bibnamefont {Vermeulen}}, \bibinfo {author}
-  {\bibfnamefont {M.~J.}\ \bibnamefont {Tiggelman}}, \bibinfo {author}
-  {\bibfnamefont {L.}~\bibnamefont {dos Santos~Martins}}, \bibinfo {author}
-  {\bibfnamefont {B.}~\bibnamefont {Dirkse}}, \emph {et~al.},\ }\bibfield
-  {title} {\bibinfo {title} {Realization of a multinode quantum network of
-  remote solid-state qubits},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-  {journal} {Science}\ }\textbf {\bibinfo {volume} {372}},\ \bibinfo {pages}
-  {259} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Degen}\ \emph {et~al.}(2017)\citenamefont {Degen},
-  \citenamefont {Reinhard},\ and\ \citenamefont
-  {Cappellaro}}]{degen2017quantum}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~L.}\ \bibnamefont
-  {Degen}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Reinhard}},\
-  and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Cappellaro}},\
-  }\bibfield  {title} {\bibinfo {title} {Quantum sensing},\ }\href@noop {}
-  {\bibfield  {journal} {\bibinfo  {journal} {Reviews of modern physics}\
-  }\textbf {\bibinfo {volume} {89}},\ \bibinfo {pages} {035002} (\bibinfo
-  {year} {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Meinel}\ \emph {et~al.}(2023)\citenamefont {Meinel},
-  \citenamefont {Kwon}, \citenamefont {Maier}, \citenamefont {Dasari},
-  \citenamefont {Sumiya}, \citenamefont {Onoda}, \citenamefont {Isoya},
-  \citenamefont {Vorobyov},\ and\ \citenamefont {Wrachtrup}}]{meinel2023high}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Meinel}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Kwon}},
-  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Maier}}, \bibinfo
-  {author} {\bibfnamefont {D.}~\bibnamefont {Dasari}}, \bibinfo {author}
-  {\bibfnamefont {H.}~\bibnamefont {Sumiya}}, \bibinfo {author} {\bibfnamefont
-  {S.}~\bibnamefont {Onoda}}, \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {Isoya}}, \bibinfo {author} {\bibfnamefont
-  {V.}~\bibnamefont {Vorobyov}},\ and\ \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {Wrachtrup}},\ }\bibfield  {title} {\bibinfo {title}
-  {High-resolution nanoscale nmr for arbitrary magnetic fields},\ }\href@noop
-  {} {\bibfield  {journal} {\bibinfo  {journal} {Communications Physics}\
-  }\textbf {\bibinfo {volume} {6}},\ \bibinfo {pages} {302} (\bibinfo {year}
-  {2023})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Bradley}\ \emph {et~al.}(2019)\citenamefont
-  {Bradley}, \citenamefont {Randall}, \citenamefont {Abobeih}, \citenamefont
-  {Berrevoets}, \citenamefont {Degen}, \citenamefont {Bakker}, \citenamefont
-  {Markham}, \citenamefont {Twitchen},\ and\ \citenamefont
-  {Taminiau}}]{bradley2019ten}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~E.}\ \bibnamefont
-  {Bradley}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Randall}},
-  \bibinfo {author} {\bibfnamefont {M.~H.}\ \bibnamefont {Abobeih}}, \bibinfo
-  {author} {\bibfnamefont {R.}~\bibnamefont {Berrevoets}}, \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Degen}}, \bibinfo {author} {\bibfnamefont
-  {M.~A.}\ \bibnamefont {Bakker}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Markham}}, \bibinfo {author} {\bibfnamefont
-  {D.}~\bibnamefont {Twitchen}},\ and\ \bibinfo {author} {\bibfnamefont
-  {T.~H.}\ \bibnamefont {Taminiau}},\ }\bibfield  {title} {\bibinfo {title} {A
-  ten-qubit solid-state spin register with quantum memory up to one minute},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
-  X}\ }\textbf {\bibinfo {volume} {9}},\ \bibinfo {pages} {031045} (\bibinfo
-  {year} {2019})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Vorobyov}\ \emph {et~al.}(2021)\citenamefont
-  {Vorobyov}, \citenamefont {Zaiser}, \citenamefont {Abt}, \citenamefont
-  {Meinel}, \citenamefont {Dasari}, \citenamefont {Neumann},\ and\
-  \citenamefont {Wrachtrup}}]{vorobyov2021quantum}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
-  {Vorobyov}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Zaiser}},
-  \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Abt}}, \bibinfo {author}
-  {\bibfnamefont {J.}~\bibnamefont {Meinel}}, \bibinfo {author} {\bibfnamefont
-  {D.}~\bibnamefont {Dasari}}, \bibinfo {author} {\bibfnamefont
-  {P.}~\bibnamefont {Neumann}},\ and\ \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {Wrachtrup}},\ }\bibfield  {title} {\bibinfo {title}
-  {Quantum fourier transform for nanoscale quantum sensing},\ }\href@noop {}
-  {\bibfield  {journal} {\bibinfo  {journal} {npj Quantum Information}\
-  }\textbf {\bibinfo {volume} {7}},\ \bibinfo {pages} {124} (\bibinfo {year}
-  {2021})}\BibitemShut {NoStop}%
-  %7
-\bibitem [{\citenamefont {Hesselmeier}\ \emph {et~al.}(2023)\citenamefont
-  {Hesselmeier}, \citenamefont {Kuna}, \citenamefont {Tak{\'a}cs},
-  \citenamefont {Iv{\'a}dy}, \citenamefont {Knolle}, \citenamefont {Ghezellou},
-  \citenamefont {Ul-Hassan}, \citenamefont {Dasari}, \citenamefont {Kaiser},
-  \citenamefont {Vorobyov} \emph {et~al.}}]{hesselmeier2023measuring}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
-  {Hesselmeier}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Kuna}},
-  \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Tak{\'a}cs}}, \bibinfo
-  {author} {\bibfnamefont {V.}~\bibnamefont {Iv{\'a}dy}}, \bibinfo {author}
-  {\bibfnamefont {W.}~\bibnamefont {Knolle}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Ghezellou}}, \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {Ul-Hassan}}, \bibinfo {author} {\bibfnamefont
-  {D.}~\bibnamefont {Dasari}}, \bibinfo {author} {\bibfnamefont
-  {F.}~\bibnamefont {Kaiser}}, \bibinfo {author} {\bibfnamefont
-  {V.}~\bibnamefont {Vorobyov}}, \emph {et~al.},\ }\bibfield  {title} {\bibinfo
-  {title} {Measuring nuclear spin qubits by qudit-enhanced spectroscopy in
-  silicon carbide},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {arXiv preprint arXiv:2310.15557}\ } (\bibinfo {year} {2023})}\BibitemShut
-  {NoStop}%
-%8
-\bibitem [{\citenamefont {Hesselmeier}\ \emph {et~al.}(2024)\citenamefont
-  {Hesselmeier}, \citenamefont {Kuna}, \citenamefont {Knolle}, \citenamefont
-  {Kaiser}, \citenamefont {Son}, \citenamefont {Ghezellou}, \citenamefont
-  {Ul-Hassan}, \citenamefont {Vorobyov},\ and\ \citenamefont
-  {Wrachtrup}}]{hesselmeier2024high}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
-  {Hesselmeier}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Kuna}},
-  \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Knolle}}, \bibinfo
-  {author} {\bibfnamefont {F.}~\bibnamefont {Kaiser}}, \bibinfo {author}
-  {\bibfnamefont {N.~T.}\ \bibnamefont {Son}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Ghezellou}}, \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {Ul-Hassan}}, \bibinfo {author} {\bibfnamefont
-  {V.}~\bibnamefont {Vorobyov}},\ and\ \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {Wrachtrup}},\ }\bibfield  {title} {\bibinfo {title} {High
-  fidelity optical readout of a nuclear spin qubit in silicon carbide},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review Letters}\ } (\bibinfo {year} {2024})}\BibitemShut {NoStop}%
-%9
-\bibitem [{\citenamefont {Reiner}\ \emph {et~al.}(2024)\citenamefont {Reiner},
-  \citenamefont {Chung}, \citenamefont {Misha}, \citenamefont {Lehner},
-  \citenamefont {Moehle}, \citenamefont {Poulos}, \citenamefont {Monir},
-  \citenamefont {Charde}, \citenamefont {Macha}, \citenamefont {Kranz} \emph
-  {et~al.}}]{reiner2024high}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Reiner}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Chung}},
-  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Misha}}, \bibinfo
-  {author} {\bibfnamefont {C.}~\bibnamefont {Lehner}}, \bibinfo {author}
-  {\bibfnamefont {C.}~\bibnamefont {Moehle}}, \bibinfo {author} {\bibfnamefont
-  {D.}~\bibnamefont {Poulos}}, \bibinfo {author} {\bibfnamefont
-  {S.}~\bibnamefont {Monir}}, \bibinfo {author} {\bibfnamefont
-  {K.}~\bibnamefont {Charde}}, \bibinfo {author} {\bibfnamefont
-  {P.}~\bibnamefont {Macha}}, \bibinfo {author} {\bibfnamefont
-  {L.}~\bibnamefont {Kranz}}, \emph {et~al.},\ }\bibfield  {title} {\bibinfo
-  {title} {High-fidelity initialization and control of electron and nuclear
-  spins in a four-qubit register},\ }\href@noop {} {\bibfield  {journal}
-  {\bibinfo  {journal} {Nature Nanotechnology}\ ,\ \bibinfo {pages} {1}}
-  (\bibinfo {year} {2024})}\BibitemShut {NoStop}%
-%10
-\bibitem [{\citenamefont {Vorobyov}\ \emph {et~al.}(2023)\citenamefont
-  {Vorobyov}, \citenamefont {Meinel}, \citenamefont {Sumiya}, \citenamefont
-  {Onoda}, \citenamefont {Isoya}, \citenamefont {Gulinsky},\ and\ \citenamefont
-  {Wrachtrup}}]{vorobyov2023transition}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.~V.}\ \bibnamefont
-  {Vorobyov}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Meinel}},
-  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Sumiya}}, \bibinfo
-  {author} {\bibfnamefont {S.}~\bibnamefont {Onoda}}, \bibinfo {author}
-  {\bibfnamefont {J.}~\bibnamefont {Isoya}}, \bibinfo {author} {\bibfnamefont
-  {O.}~\bibnamefont {Gulinsky}},\ and\ \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {Wrachtrup}},\ }\bibfield  {title} {\bibinfo {title}
-  {Transition from quantum to classical dynamics in weak measurements and
-  reconstruction of quantum correlation},\ }\href@noop {} {\bibfield  {journal}
-  {\bibinfo  {journal} {Physical Review A}\ }\textbf {\bibinfo {volume}
-  {107}},\ \bibinfo {pages} {042212} (\bibinfo {year} {2023})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Bradley}\ \emph {et~al.}(2022)\citenamefont
-  {Bradley}, \citenamefont {de~Bone}, \citenamefont {M{\"o}ller}, \citenamefont
-  {Baier}, \citenamefont {Degen}, \citenamefont {Loenen}, \citenamefont
-  {Bartling}, \citenamefont {Markham}, \citenamefont {Twitchen}, \citenamefont
-  {Hanson} \emph {et~al.}}]{bradley2022robust}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
-  {Bradley}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {de~Bone}},
-  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {M{\"o}ller}}, \bibinfo
-  {author} {\bibfnamefont {S.}~\bibnamefont {Baier}}, \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Degen}}, \bibinfo {author} {\bibfnamefont
-  {S.}~\bibnamefont {Loenen}}, \bibinfo {author} {\bibfnamefont
-  {H.}~\bibnamefont {Bartling}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Markham}}, \bibinfo {author} {\bibfnamefont
-  {D.}~\bibnamefont {Twitchen}}, \bibinfo {author} {\bibfnamefont
-  {R.}~\bibnamefont {Hanson}}, \emph {et~al.},\ }\bibfield  {title} {\bibinfo
-  {title} {Robust quantum-network memory based on spin qubits in isotopically
-  engineered diamond},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-  {journal} {npj Quantum Information}\ }\textbf {\bibinfo {volume} {8}},\
-  \bibinfo {pages} {122} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Abobeih}\ \emph {et~al.}(2019)\citenamefont
-  {Abobeih}, \citenamefont {Randall}, \citenamefont {Bradley}, \citenamefont
-  {Bartling}, \citenamefont {Bakker}, \citenamefont {Degen}, \citenamefont
-  {Markham}, \citenamefont {Twitchen},\ and\ \citenamefont
-  {Taminiau}}]{abobeih2019atomic}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Abobeih}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Randall}},
-  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Bradley}}, \bibinfo
-  {author} {\bibfnamefont {H.}~\bibnamefont {Bartling}}, \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Bakker}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Degen}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Markham}}, \bibinfo {author} {\bibfnamefont
-  {D.}~\bibnamefont {Twitchen}},\ and\ \bibinfo {author} {\bibfnamefont
-  {T.}~\bibnamefont {Taminiau}},\ }\bibfield  {title} {\bibinfo {title}
-  {Atomic-scale imaging of a 27-nuclear-spin cluster using a quantum sensor},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nature}\ }\textbf
-  {\bibinfo {volume} {576}},\ \bibinfo {pages} {411} (\bibinfo {year}
-  {2019})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {van~de Stolpe}\ \emph {et~al.}(2023)\citenamefont
-  {van~de Stolpe}, \citenamefont {Kwiatkowski}, \citenamefont {Bradley},
-  \citenamefont {Randall}, \citenamefont {Breitweiser}, \citenamefont
-  {Bassett}, \citenamefont {Markham}, \citenamefont {Twitchen},\ and\
-  \citenamefont {Taminiau}}]{van2023mapping}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-  {van~de Stolpe}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
-  {Kwiatkowski}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
-  {Bradley}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Randall}},
-  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Breitweiser}}, \bibinfo
-  {author} {\bibfnamefont {L.}~\bibnamefont {Bassett}}, \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Markham}}, \bibinfo {author} {\bibfnamefont
-  {D.}~\bibnamefont {Twitchen}},\ and\ \bibinfo {author} {\bibfnamefont
-  {T.}~\bibnamefont {Taminiau}},\ }\bibfield  {title} {\bibinfo {title}
-  {Mapping a 50-spin-qubit network through correlated sensing},\ }\href@noop {}
-  {\bibfield  {journal} {\bibinfo  {journal} {arXiv preprint arXiv:2307.06939}\
-  } (\bibinfo {year} {2023})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Dr{\'e}au}(2012)}]{Dreau:2012aa}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Dr{\'e}au}},\ }\bibfield  {title} {\bibinfo {title} {High-resolution
-  spectroscopy of single nv defects coupled with nearby $^{13}$c nuclear spins
-  in diamond},\ }\bibfield  {journal} {\bibinfo  {journal} {Physical Review B}\
-  }\textbf {\bibinfo {volume} {85}},\ \href
-  {https://doi.org/10.1103/PhysRevB.85.134107} {10.1103/PhysRevB.85.134107}
-  (\bibinfo {year} {2012})\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Childress}\ \emph {et~al.}(2006)\citenamefont
-  {Childress}, \citenamefont {Gurudev~Dutt}, \citenamefont {Taylor},
-  \citenamefont {Zibrov}, \citenamefont {Jelezko}, \citenamefont {Wrachtrup},
-  \citenamefont {Hemmer},\ and\ \citenamefont {Lukin}}]{childress2006coherent}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Childress}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Gurudev~Dutt}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Taylor}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Zibrov}},
-  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Jelezko}}, \bibinfo
-  {author} {\bibfnamefont {J.}~\bibnamefont {Wrachtrup}}, \bibinfo {author}
-  {\bibfnamefont {P.}~\bibnamefont {Hemmer}},\ and\ \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Lukin}},\ }\bibfield  {title} {\bibinfo
-  {title} {Coherent dynamics of coupled electron and nuclear spin qubits in
-  diamond},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Science}\ }\textbf {\bibinfo {volume} {314}},\ \bibinfo {pages} {281}
-  (\bibinfo {year} {2006})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Laraoui}\ \emph {et~al.}(2013)\citenamefont
-  {Laraoui}, \citenamefont {Dolde}, \citenamefont {Burk}, \citenamefont
-  {Reinhard}, \citenamefont {Wrachtrup},\ and\ \citenamefont
-  {Meriles}}]{laraoui2013high}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Laraoui}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Dolde}},
-  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Burk}}, \bibinfo {author}
-  {\bibfnamefont {F.}~\bibnamefont {Reinhard}}, \bibinfo {author}
-  {\bibfnamefont {J.}~\bibnamefont {Wrachtrup}},\ and\ \bibinfo {author}
-  {\bibfnamefont {C.~A.}\ \bibnamefont {Meriles}},\ }\bibfield  {title}
-  {\bibinfo {title} {High-resolution correlation spectroscopy of 13c spins near
-  a nitrogen-vacancy centre in diamond},\ }\href@noop {} {\bibfield  {journal}
-  {\bibinfo  {journal} {Nature communications}\ }\textbf {\bibinfo {volume}
-  {4}},\ \bibinfo {pages} {1651} (\bibinfo {year} {2013})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Vorobyov}\ \emph {et~al.}(2022)\citenamefont
-  {Vorobyov}, \citenamefont {Javadzade}, \citenamefont {Joliffe}, \citenamefont
-  {Kaiser},\ and\ \citenamefont {Wrachtrup}}]{vorobyov2022addressing}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
-  {Vorobyov}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Javadzade}},
-  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Joliffe}}, \bibinfo
-  {author} {\bibfnamefont {F.}~\bibnamefont {Kaiser}},\ and\ \bibinfo {author}
-  {\bibfnamefont {J.}~\bibnamefont {Wrachtrup}},\ }\bibfield  {title} {\bibinfo
-  {title} {Addressing single nuclear spins quantum memories by a central
-  electron spin},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Applied Magnetic Resonance}\ }\textbf {\bibinfo {volume} {53}},\ \bibinfo
-  {pages} {1317} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Taminiau}\ \emph {et~al.}(2012)\citenamefont
-  {Taminiau}, \citenamefont {Wagenaar}, \citenamefont {Van~der Sar},
-  \citenamefont {Jelezko}, \citenamefont {Dobrovitski},\ and\ \citenamefont
-  {Hanson}}]{taminiau2012detection}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Taminiau}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Wagenaar}},
-  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Van~der Sar}}, \bibinfo
-  {author} {\bibfnamefont {F.}~\bibnamefont {Jelezko}}, \bibinfo {author}
-  {\bibfnamefont {V.~V.}\ \bibnamefont {Dobrovitski}},\ and\ \bibinfo {author}
-  {\bibfnamefont {R.}~\bibnamefont {Hanson}},\ }\bibfield  {title} {\bibinfo
-  {title} {Detection and control of individual nuclear spins using a weakly
-  coupled electron spin},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-  {journal} {Physical review letters}\ }\textbf {\bibinfo {volume} {109}},\
-  \bibinfo {pages} {137602} (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Zhao}(2014)}]{Zhao:2014aa}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-  {Zhao}},\ }\bibfield  {title} {\bibinfo {title} {Dynamical decoupling design
-  for identifying weakly coupled nuclear spins in a bath},\ }\bibfield
-  {journal} {\bibinfo  {journal} {Physical Review A}\ }\textbf {\bibinfo
-  {volume} {90}},\ \href {https://doi.org/10.1103/PhysRevA.90.032319}
-  {10.1103/PhysRevA.90.032319} (\bibinfo {year} {2014})\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Neumann}\ \emph {et~al.}(2010)\citenamefont
-  {Neumann}, \citenamefont {Beck}, \citenamefont {Steiner}, \citenamefont
-  {Rempp}, \citenamefont {Fedder}, \citenamefont {Hemmer}, \citenamefont
-  {Wrachtrup},\ and\ \citenamefont {Jelezko}}]{neumann2010single}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Neumann}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Beck}},
-  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Steiner}}, \bibinfo
-  {author} {\bibfnamefont {F.}~\bibnamefont {Rempp}}, \bibinfo {author}
-  {\bibfnamefont {H.}~\bibnamefont {Fedder}}, \bibinfo {author} {\bibfnamefont
-  {P.~R.}\ \bibnamefont {Hemmer}}, \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {Wrachtrup}},\ and\ \bibinfo {author} {\bibfnamefont
-  {F.}~\bibnamefont {Jelezko}},\ }\bibfield  {title} {\bibinfo {title}
-  {Single-shot readout of a single nuclear spin},\ }\href@noop {} {\bibfield
-  {journal} {\bibinfo  {journal} {science}\ }\textbf {\bibinfo {volume}
-  {329}},\ \bibinfo {pages} {542} (\bibinfo {year} {2010})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Bradley}(2019)}]{Bradley:2019aa}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
-  {Bradley}},\ }\bibfield  {title} {\bibinfo {title} {A ten-qubit solid-state
-  spin register with quantum memory up to one minute},\ }\bibfield  {journal}
-  {\bibinfo  {journal} {Physical Review X}\ }\textbf {\bibinfo {volume} {9}},\
-  \href {https://doi.org/10.1103/PhysRevX.9.031045} {10.1103/PhysRevX.9.031045}
-  (\bibinfo {year} {2019})\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Zaiser}\ \emph {et~al.}(2016)\citenamefont {Zaiser},
-  \citenamefont {Rendler}, \citenamefont {Jakobi}, \citenamefont {Wolf},
-  \citenamefont {Lee}, \citenamefont {Wagner}, \citenamefont {Bergholm},
-  \citenamefont {Schulte-Herbr{\"u}ggen}, \citenamefont {Neumann},\ and\
-  \citenamefont {Wrachtrup}}]{zaiser2016enhancing}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Zaiser}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Rendler}},
-  \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Jakobi}}, \bibinfo
-  {author} {\bibfnamefont {T.}~\bibnamefont {Wolf}}, \bibinfo {author}
-  {\bibfnamefont {S.-Y.}\ \bibnamefont {Lee}}, \bibinfo {author} {\bibfnamefont
-  {S.}~\bibnamefont {Wagner}}, \bibinfo {author} {\bibfnamefont
-  {V.}~\bibnamefont {Bergholm}}, \bibinfo {author} {\bibfnamefont
-  {T.}~\bibnamefont {Schulte-Herbr{\"u}ggen}}, \bibinfo {author} {\bibfnamefont
-  {P.}~\bibnamefont {Neumann}},\ and\ \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {Wrachtrup}},\ }\bibfield  {title} {\bibinfo {title}
-  {Enhancing quantum sensing sensitivity by a quantum memory},\ }\href@noop {}
-  {\bibfield  {journal} {\bibinfo  {journal} {Nature communications}\ }\textbf
-  {\bibinfo {volume} {7}},\ \bibinfo {pages} {12279} (\bibinfo {year}
-  {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Kasumaj}\ and\ \citenamefont
-  {Stoll}(2008)}]{kasumaj20085}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
-  {Kasumaj}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Stoll}},\ }\bibfield  {title} {\bibinfo {title} {5-and 6-pulse electron spin
-  echo envelope modulation (eseem) of multi-nuclear spin systems},\ }\href@noop
-  {} {\bibfield  {journal} {\bibinfo  {journal} {Journal of Magnetic
-  Resonance}\ }\textbf {\bibinfo {volume} {190}},\ \bibinfo {pages} {233}
-  (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Stoll}\ \emph {et~al.}(2005)\citenamefont {Stoll},
-  \citenamefont {Calle}, \citenamefont {Mitrikas},\ and\ \citenamefont
-  {Schweiger}}]{stoll2005peak}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Stoll}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Calle}},
-  \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Mitrikas}},\ and\
-  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Schweiger}},\ }\bibfield
-  {title} {\bibinfo {title} {Peak suppression in eseem spectra of multinuclear
-  spin systems},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Journal of Magnetic Resonance}\ }\textbf {\bibinfo {volume} {177}},\
-  \bibinfo {pages} {93} (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Schweiger}\ and\ \citenamefont
-  	{Jeschke}(2001)}]{schweiger2001principles}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  		{Schweiger}}\ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-  		{Jeschke}},\ }\bibfield  {title} {\bibinfo {title} {Principles of pulse electron paramagnetic resonance} }\href@noop
-  {} {\bibfield  {book} {\bibinfo  {book} {Oxford university press}\ }
-  	(\bibinfo {year} {2001})}\BibitemShut {NoStop}%
-\end{thebibliography}%
+\bibliography{references_review}% Produces the bibliography via BibTeX.
+
+%\begin{thebibliography}{24}%
+%\makeatletter
+%\providecommand \@ifxundefined [1]{%
+% \@ifx{#1\undefined}
+%}%
+%\providecommand \@ifnum [1]{%
+% \ifnum #1\expandafter \@firstoftwo
+% \else \expandafter \@secondoftwo
+% \fi
+%}%
+%\providecommand \@ifx [1]{%
+% \ifx #1\expandafter \@firstoftwo
+% \else \expandafter \@secondoftwo
+% \fi
+%}%
+%\providecommand \natexlab [1]{#1}%
+%\providecommand \enquote  [1]{``#1''}%
+%\providecommand \bibnamefont  [1]{#1}%
+%\providecommand \bibfnamefont [1]{#1}%
+%\providecommand \citenamefont [1]{#1}%
+%\providecommand \href@noop [0]{\@secondoftwo}%
+%\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
+%\providecommand \@href[1]{\@@startlink{#1}\@@href}%
+%\providecommand \@@href[1]{\endgroup#1\@@endlink}%
+%\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
+%  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
+%\providecommand \@@startlink[1]{}%
+%\providecommand \@@endlink[0]{}%
+%\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
+%\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
+%\providecommand \urlprefix  [0]{URL }%
+%\providecommand \Eprint [0]{\href }%
+%\providecommand \doibase [0]{https://doi.org/}%
+%\providecommand \selectlanguage [0]{\@gobble}%
+%\providecommand \bibinfo  [0]{\@secondoftwo}%
+%\providecommand \bibfield  [0]{\@secondoftwo}%
+%\providecommand \translation [1]{[#1]}%
+%\providecommand \BibitemOpen [0]{}%
+%\providecommand \bibitemStop [0]{}%
+%\providecommand \bibitemNoStop [0]{.\EOS\space}%
+%\providecommand \EOS [0]{\spacefactor3000\relax}%
+%\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
+%\let\auto@bib@innerbib\@empty
+%%</preamble>
+%\bibitem [{\citenamefont {Awschalom}\ \emph {et~al.}(2018)\citenamefont
+%  {Awschalom}, \citenamefont {Hanson}, \citenamefont {Wrachtrup},\ and\
+%  \citenamefont {Zhou}}]{awschalom2018quantum}%
+%  \BibitemOpen
+%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~D.}\ \bibnamefont
+%  {Awschalom}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Hanson}},
+%  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Wrachtrup}},\ and\
+%  \bibinfo {author} {\bibfnamefont {B.~B.}\ \bibnamefont {Zhou}},\ }\bibfield
+%  {title} {\bibinfo {title} {Quantum technologies with optically interfaced
+%  solid-state spins},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+%  {journal} {Nature Photonics}\ }\textbf {\bibinfo {volume} {12}},\ \bibinfo
+%  {pages} {516} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
+%\bibitem [{\citenamefont {Pompili}\ \emph {et~al.}(2021)\citenamefont
+%  {Pompili}, \citenamefont {Hermans}, \citenamefont {Baier}, \citenamefont
+%  {Beukers}, \citenamefont {Humphreys}, \citenamefont {Schouten}, \citenamefont
+%  {Vermeulen}, \citenamefont {Tiggelman}, \citenamefont {dos Santos~Martins},
+%  \citenamefont {Dirkse} \emph {et~al.}}]{pompili2021realization}%
+%  \BibitemOpen
+%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+%  {Pompili}}, \bibinfo {author} {\bibfnamefont {S.~L.}\ \bibnamefont
+%  {Hermans}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Baier}},
+%  \bibinfo {author} {\bibfnamefont {H.~K.}\ \bibnamefont {Beukers}}, \bibinfo
+%  {author} {\bibfnamefont {P.~C.}\ \bibnamefont {Humphreys}}, \bibinfo {author}
+%  {\bibfnamefont {R.~N.}\ \bibnamefont {Schouten}}, \bibinfo {author}
+%  {\bibfnamefont {R.~F.}\ \bibnamefont {Vermeulen}}, \bibinfo {author}
+%  {\bibfnamefont {M.~J.}\ \bibnamefont {Tiggelman}}, \bibinfo {author}
+%  {\bibfnamefont {L.}~\bibnamefont {dos Santos~Martins}}, \bibinfo {author}
+%  {\bibfnamefont {B.}~\bibnamefont {Dirkse}}, \emph {et~al.},\ }\bibfield
+%  {title} {\bibinfo {title} {Realization of a multinode quantum network of
+%  remote solid-state qubits},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+%  {journal} {Science}\ }\textbf {\bibinfo {volume} {372}},\ \bibinfo {pages}
+%  {259} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
+%\bibitem [{\citenamefont {Degen}\ \emph {et~al.}(2017)\citenamefont {Degen},
+%  \citenamefont {Reinhard},\ and\ \citenamefont
+%  {Cappellaro}}]{degen2017quantum}%
+%  \BibitemOpen
+%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~L.}\ \bibnamefont
+%  {Degen}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Reinhard}},\
+%  and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Cappellaro}},\
+%  }\bibfield  {title} {\bibinfo {title} {Quantum sensing},\ }\href@noop {}
+%  {\bibfield  {journal} {\bibinfo  {journal} {Reviews of modern physics}\
+%  }\textbf {\bibinfo {volume} {89}},\ \bibinfo {pages} {035002} (\bibinfo
+%  {year} {2017})}\BibitemShut {NoStop}%
+%\bibitem [{\citenamefont {Meinel}\ \emph {et~al.}(2023)\citenamefont {Meinel},
+%  \citenamefont {Kwon}, \citenamefont {Maier}, \citenamefont {Dasari},
+%  \citenamefont {Sumiya}, \citenamefont {Onoda}, \citenamefont {Isoya},
+%  \citenamefont {Vorobyov},\ and\ \citenamefont {Wrachtrup}}]{meinel2023high}%
+%  \BibitemOpen
+%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+%  {Meinel}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Kwon}},
+%  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Maier}}, \bibinfo
+%  {author} {\bibfnamefont {D.}~\bibnamefont {Dasari}}, \bibinfo {author}
+%  {\bibfnamefont {H.}~\bibnamefont {Sumiya}}, \bibinfo {author} {\bibfnamefont
+%  {S.}~\bibnamefont {Onoda}}, \bibinfo {author} {\bibfnamefont
+%  {J.}~\bibnamefont {Isoya}}, \bibinfo {author} {\bibfnamefont
+%  {V.}~\bibnamefont {Vorobyov}},\ and\ \bibinfo {author} {\bibfnamefont
+%  {J.}~\bibnamefont {Wrachtrup}},\ }\bibfield  {title} {\bibinfo {title}
+%  {High-resolution nanoscale nmr for arbitrary magnetic fields},\ }\href@noop
+%  {} {\bibfield  {journal} {\bibinfo  {journal} {Communications Physics}\
+%  }\textbf {\bibinfo {volume} {6}},\ \bibinfo {pages} {302} (\bibinfo {year}
+%  {2023})}\BibitemShut {NoStop}%
+%\bibitem [{\citenamefont {Bradley}\ \emph {et~al.}(2019)\citenamefont
+%  {Bradley}, \citenamefont {Randall}, \citenamefont {Abobeih}, \citenamefont
+%  {Berrevoets}, \citenamefont {Degen}, \citenamefont {Bakker}, \citenamefont
+%  {Markham}, \citenamefont {Twitchen},\ and\ \citenamefont
+%  {Taminiau}}]{bradley2019ten}%
+%  \BibitemOpen
+%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~E.}\ \bibnamefont
+%  {Bradley}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Randall}},
+%  \bibinfo {author} {\bibfnamefont {M.~H.}\ \bibnamefont {Abobeih}}, \bibinfo
+%  {author} {\bibfnamefont {R.}~\bibnamefont {Berrevoets}}, \bibinfo {author}
+%  {\bibfnamefont {M.}~\bibnamefont {Degen}}, \bibinfo {author} {\bibfnamefont
+%  {M.~A.}\ \bibnamefont {Bakker}}, \bibinfo {author} {\bibfnamefont
+%  {M.}~\bibnamefont {Markham}}, \bibinfo {author} {\bibfnamefont
+%  {D.}~\bibnamefont {Twitchen}},\ and\ \bibinfo {author} {\bibfnamefont
+%  {T.~H.}\ \bibnamefont {Taminiau}},\ }\bibfield  {title} {\bibinfo {title} {A
+%  ten-qubit solid-state spin register with quantum memory up to one minute},\
+%  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
+%  X}\ }\textbf {\bibinfo {volume} {9}},\ \bibinfo {pages} {031045} (\bibinfo
+%  {year} {2019})}\BibitemShut {NoStop}%
+%\bibitem [{\citenamefont {Vorobyov}\ \emph {et~al.}(2021)\citenamefont
+%  {Vorobyov}, \citenamefont {Zaiser}, \citenamefont {Abt}, \citenamefont
+%  {Meinel}, \citenamefont {Dasari}, \citenamefont {Neumann},\ and\
+%  \citenamefont {Wrachtrup}}]{vorobyov2021quantum}%
+%  \BibitemOpen
+%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
+%  {Vorobyov}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Zaiser}},
+%  \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Abt}}, \bibinfo {author}
+%  {\bibfnamefont {J.}~\bibnamefont {Meinel}}, \bibinfo {author} {\bibfnamefont
+%  {D.}~\bibnamefont {Dasari}}, \bibinfo {author} {\bibfnamefont
+%  {P.}~\bibnamefont {Neumann}},\ and\ \bibinfo {author} {\bibfnamefont
+%  {J.}~\bibnamefont {Wrachtrup}},\ }\bibfield  {title} {\bibinfo {title}
+%  {Quantum fourier transform for nanoscale quantum sensing},\ }\href@noop {}
+%  {\bibfield  {journal} {\bibinfo  {journal} {npj Quantum Information}\
+%  }\textbf {\bibinfo {volume} {7}},\ \bibinfo {pages} {124} (\bibinfo {year}
+%  {2021})}\BibitemShut {NoStop}%
+%  %7
+%\bibitem [{\citenamefont {Hesselmeier}\ \emph {et~al.}(2023)\citenamefont
+%  {Hesselmeier}, \citenamefont {Kuna}, \citenamefont {Tak{\'a}cs},
+%  \citenamefont {Iv{\'a}dy}, \citenamefont {Knolle}, \citenamefont {Ghezellou},
+%  \citenamefont {Ul-Hassan}, \citenamefont {Dasari}, \citenamefont {Kaiser},
+%  \citenamefont {Vorobyov} \emph {et~al.}}]{hesselmeier2023measuring}%
+%  \BibitemOpen
+%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+%  {Hesselmeier}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Kuna}},
+%  \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Tak{\'a}cs}}, \bibinfo
+%  {author} {\bibfnamefont {V.}~\bibnamefont {Iv{\'a}dy}}, \bibinfo {author}
+%  {\bibfnamefont {W.}~\bibnamefont {Knolle}}, \bibinfo {author} {\bibfnamefont
+%  {M.}~\bibnamefont {Ghezellou}}, \bibinfo {author} {\bibfnamefont
+%  {J.}~\bibnamefont {Ul-Hassan}}, \bibinfo {author} {\bibfnamefont
+%  {D.}~\bibnamefont {Dasari}}, \bibinfo {author} {\bibfnamefont
+%  {F.}~\bibnamefont {Kaiser}}, \bibinfo {author} {\bibfnamefont
+%  {V.}~\bibnamefont {Vorobyov}}, \emph {et~al.},\ }\bibfield  {title} {\bibinfo
+%  {title} {Measuring nuclear spin qubits by qudit-enhanced spectroscopy in
+%  silicon carbide},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+%  {arXiv preprint arXiv:2310.15557}\ } (\bibinfo {year} {2023})}\BibitemShut
+%  {NoStop}%
+%%8
+%\bibitem [{\citenamefont {Hesselmeier}\ \emph {et~al.}(2024)\citenamefont
+%  {Hesselmeier}, \citenamefont {Kuna}, \citenamefont {Knolle}, \citenamefont
+%  {Kaiser}, \citenamefont {Son}, \citenamefont {Ghezellou}, \citenamefont
+%  {Ul-Hassan}, \citenamefont {Vorobyov},\ and\ \citenamefont
+%  {Wrachtrup}}]{hesselmeier2024high}%
+%  \BibitemOpen
+%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+%  {Hesselmeier}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Kuna}},
+%  \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Knolle}}, \bibinfo
+%  {author} {\bibfnamefont {F.}~\bibnamefont {Kaiser}}, \bibinfo {author}
+%  {\bibfnamefont {N.~T.}\ \bibnamefont {Son}}, \bibinfo {author} {\bibfnamefont
+%  {M.}~\bibnamefont {Ghezellou}}, \bibinfo {author} {\bibfnamefont
+%  {J.}~\bibnamefont {Ul-Hassan}}, \bibinfo {author} {\bibfnamefont
+%  {V.}~\bibnamefont {Vorobyov}},\ and\ \bibinfo {author} {\bibfnamefont
+%  {J.}~\bibnamefont {Wrachtrup}},\ }\bibfield  {title} {\bibinfo {title} {High
+%  fidelity optical readout of a nuclear spin qubit in silicon carbide},\
+%  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review Letters}\ } (\bibinfo {year} {2024})}\BibitemShut {NoStop}%
+%%9
+%\bibitem [{\citenamefont {Reiner}\ \emph {et~al.}(2024)\citenamefont {Reiner},
+%  \citenamefont {Chung}, \citenamefont {Misha}, \citenamefont {Lehner},
+%  \citenamefont {Moehle}, \citenamefont {Poulos}, \citenamefont {Monir},
+%  \citenamefont {Charde}, \citenamefont {Macha}, \citenamefont {Kranz} \emph
+%  {et~al.}}]{reiner2024high}%
+%  \BibitemOpen
+%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+%  {Reiner}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Chung}},
+%  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Misha}}, \bibinfo
+%  {author} {\bibfnamefont {C.}~\bibnamefont {Lehner}}, \bibinfo {author}
+%  {\bibfnamefont {C.}~\bibnamefont {Moehle}}, \bibinfo {author} {\bibfnamefont
+%  {D.}~\bibnamefont {Poulos}}, \bibinfo {author} {\bibfnamefont
+%  {S.}~\bibnamefont {Monir}}, \bibinfo {author} {\bibfnamefont
+%  {K.}~\bibnamefont {Charde}}, \bibinfo {author} {\bibfnamefont
+%  {P.}~\bibnamefont {Macha}}, \bibinfo {author} {\bibfnamefont
+%  {L.}~\bibnamefont {Kranz}}, \emph {et~al.},\ }\bibfield  {title} {\bibinfo
+%  {title} {High-fidelity initialization and control of electron and nuclear
+%  spins in a four-qubit register},\ }\href@noop {} {\bibfield  {journal}
+%  {\bibinfo  {journal} {Nature Nanotechnology}\ ,\ \bibinfo {pages} {1}}
+%  (\bibinfo {year} {2024})}\BibitemShut {NoStop}%
+%%10
+%\bibitem [{\citenamefont {Vorobyov}\ \emph {et~al.}(2023)\citenamefont
+%  {Vorobyov}, \citenamefont {Meinel}, \citenamefont {Sumiya}, \citenamefont
+%  {Onoda}, \citenamefont {Isoya}, \citenamefont {Gulinsky},\ and\ \citenamefont
+%  {Wrachtrup}}]{vorobyov2023transition}%
+%  \BibitemOpen
+%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.~V.}\ \bibnamefont
+%  {Vorobyov}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Meinel}},
+%  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Sumiya}}, \bibinfo
+%  {author} {\bibfnamefont {S.}~\bibnamefont {Onoda}}, \bibinfo {author}
+%  {\bibfnamefont {J.}~\bibnamefont {Isoya}}, \bibinfo {author} {\bibfnamefont
+%  {O.}~\bibnamefont {Gulinsky}},\ and\ \bibinfo {author} {\bibfnamefont
+%  {J.}~\bibnamefont {Wrachtrup}},\ }\bibfield  {title} {\bibinfo {title}
+%  {Transition from quantum to classical dynamics in weak measurements and
+%  reconstruction of quantum correlation},\ }\href@noop {} {\bibfield  {journal}
+%  {\bibinfo  {journal} {Physical Review A}\ }\textbf {\bibinfo {volume}
+%  {107}},\ \bibinfo {pages} {042212} (\bibinfo {year} {2023})}\BibitemShut
+%  {NoStop}%
+%\bibitem [{\citenamefont {Bradley}\ \emph {et~al.}(2022)\citenamefont
+%  {Bradley}, \citenamefont {de~Bone}, \citenamefont {M{\"o}ller}, \citenamefont
+%  {Baier}, \citenamefont {Degen}, \citenamefont {Loenen}, \citenamefont
+%  {Bartling}, \citenamefont {Markham}, \citenamefont {Twitchen}, \citenamefont
+%  {Hanson} \emph {et~al.}}]{bradley2022robust}%
+%  \BibitemOpen
+%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+%  {Bradley}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {de~Bone}},
+%  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {M{\"o}ller}}, \bibinfo
+%  {author} {\bibfnamefont {S.}~\bibnamefont {Baier}}, \bibinfo {author}
+%  {\bibfnamefont {M.}~\bibnamefont {Degen}}, \bibinfo {author} {\bibfnamefont
+%  {S.}~\bibnamefont {Loenen}}, \bibinfo {author} {\bibfnamefont
+%  {H.}~\bibnamefont {Bartling}}, \bibinfo {author} {\bibfnamefont
+%  {M.}~\bibnamefont {Markham}}, \bibinfo {author} {\bibfnamefont
+%  {D.}~\bibnamefont {Twitchen}}, \bibinfo {author} {\bibfnamefont
+%  {R.}~\bibnamefont {Hanson}}, \emph {et~al.},\ }\bibfield  {title} {\bibinfo
+%  {title} {Robust quantum-network memory based on spin qubits in isotopically
+%  engineered diamond},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+%  {journal} {npj Quantum Information}\ }\textbf {\bibinfo {volume} {8}},\
+%  \bibinfo {pages} {122} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
+%\bibitem [{\citenamefont {Abobeih}\ \emph {et~al.}(2019)\citenamefont
+%  {Abobeih}, \citenamefont {Randall}, \citenamefont {Bradley}, \citenamefont
+%  {Bartling}, \citenamefont {Bakker}, \citenamefont {Degen}, \citenamefont
+%  {Markham}, \citenamefont {Twitchen},\ and\ \citenamefont
+%  {Taminiau}}]{abobeih2019atomic}%
+%  \BibitemOpen
+%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+%  {Abobeih}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Randall}},
+%  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Bradley}}, \bibinfo
+%  {author} {\bibfnamefont {H.}~\bibnamefont {Bartling}}, \bibinfo {author}
+%  {\bibfnamefont {M.}~\bibnamefont {Bakker}}, \bibinfo {author} {\bibfnamefont
+%  {M.}~\bibnamefont {Degen}}, \bibinfo {author} {\bibfnamefont
+%  {M.}~\bibnamefont {Markham}}, \bibinfo {author} {\bibfnamefont
+%  {D.}~\bibnamefont {Twitchen}},\ and\ \bibinfo {author} {\bibfnamefont
+%  {T.}~\bibnamefont {Taminiau}},\ }\bibfield  {title} {\bibinfo {title}
+%  {Atomic-scale imaging of a 27-nuclear-spin cluster using a quantum sensor},\
+%  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nature}\ }\textbf
+%  {\bibinfo {volume} {576}},\ \bibinfo {pages} {411} (\bibinfo {year}
+%  {2019})}\BibitemShut {NoStop}%
+%\bibitem [{\citenamefont {van~de Stolpe}\ \emph {et~al.}(2023)\citenamefont
+%  {van~de Stolpe}, \citenamefont {Kwiatkowski}, \citenamefont {Bradley},
+%  \citenamefont {Randall}, \citenamefont {Breitweiser}, \citenamefont
+%  {Bassett}, \citenamefont {Markham}, \citenamefont {Twitchen},\ and\
+%  \citenamefont {Taminiau}}]{van2023mapping}%
+%  \BibitemOpen
+%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+%  {van~de Stolpe}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+%  {Kwiatkowski}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+%  {Bradley}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Randall}},
+%  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Breitweiser}}, \bibinfo
+%  {author} {\bibfnamefont {L.}~\bibnamefont {Bassett}}, \bibinfo {author}
+%  {\bibfnamefont {M.}~\bibnamefont {Markham}}, \bibinfo {author} {\bibfnamefont
+%  {D.}~\bibnamefont {Twitchen}},\ and\ \bibinfo {author} {\bibfnamefont
+%  {T.}~\bibnamefont {Taminiau}},\ }\bibfield  {title} {\bibinfo {title}
+%  {Mapping a 50-spin-qubit network through correlated sensing},\ }\href@noop {}
+%  {\bibfield  {journal} {\bibinfo  {journal} {arXiv preprint arXiv:2307.06939}\
+%  } (\bibinfo {year} {2023})}\BibitemShut {NoStop}%
+%\bibitem [{\citenamefont {Dr{\'e}au}(2012)}]{Dreau:2012aa}%
+%  \BibitemOpen
+%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+%  {Dr{\'e}au}},\ }\bibfield  {title} {\bibinfo {title} {High-resolution
+%  spectroscopy of single nv defects coupled with nearby $^{13}$c nuclear spins
+%  in diamond},\ }\bibfield  {journal} {\bibinfo  {journal} {Physical Review B}\
+%  }\textbf {\bibinfo {volume} {85}},\ \href
+%  {https://doi.org/10.1103/PhysRevB.85.134107} {10.1103/PhysRevB.85.134107}
+%  (\bibinfo {year} {2012})\BibitemShut {NoStop}%
+%\bibitem [{\citenamefont {Childress}\ \emph {et~al.}(2006)\citenamefont
+%  {Childress}, \citenamefont {Gurudev~Dutt}, \citenamefont {Taylor},
+%  \citenamefont {Zibrov}, \citenamefont {Jelezko}, \citenamefont {Wrachtrup},
+%  \citenamefont {Hemmer},\ and\ \citenamefont {Lukin}}]{childress2006coherent}%
+%  \BibitemOpen
+%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+%  {Childress}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+%  {Gurudev~Dutt}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+%  {Taylor}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Zibrov}},
+%  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Jelezko}}, \bibinfo
+%  {author} {\bibfnamefont {J.}~\bibnamefont {Wrachtrup}}, \bibinfo {author}
+%  {\bibfnamefont {P.}~\bibnamefont {Hemmer}},\ and\ \bibinfo {author}
+%  {\bibfnamefont {M.}~\bibnamefont {Lukin}},\ }\bibfield  {title} {\bibinfo
+%  {title} {Coherent dynamics of coupled electron and nuclear spin qubits in
+%  diamond},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+%  {Science}\ }\textbf {\bibinfo {volume} {314}},\ \bibinfo {pages} {281}
+%  (\bibinfo {year} {2006})}\BibitemShut {NoStop}%
+%\bibitem [{\citenamefont {Laraoui}\ \emph {et~al.}(2013)\citenamefont
+%  {Laraoui}, \citenamefont {Dolde}, \citenamefont {Burk}, \citenamefont
+%  {Reinhard}, \citenamefont {Wrachtrup},\ and\ \citenamefont
+%  {Meriles}}]{laraoui2013high}%
+%  \BibitemOpen
+%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+%  {Laraoui}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Dolde}},
+%  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Burk}}, \bibinfo {author}
+%  {\bibfnamefont {F.}~\bibnamefont {Reinhard}}, \bibinfo {author}
+%  {\bibfnamefont {J.}~\bibnamefont {Wrachtrup}},\ and\ \bibinfo {author}
+%  {\bibfnamefont {C.~A.}\ \bibnamefont {Meriles}},\ }\bibfield  {title}
+%  {\bibinfo {title} {High-resolution correlation spectroscopy of 13c spins near
+%  a nitrogen-vacancy centre in diamond},\ }\href@noop {} {\bibfield  {journal}
+%  {\bibinfo  {journal} {Nature communications}\ }\textbf {\bibinfo {volume}
+%  {4}},\ \bibinfo {pages} {1651} (\bibinfo {year} {2013})}\BibitemShut
+%  {NoStop}%
+%\bibitem [{\citenamefont {Vorobyov}\ \emph {et~al.}(2022)\citenamefont
+%  {Vorobyov}, \citenamefont {Javadzade}, \citenamefont {Joliffe}, \citenamefont
+%  {Kaiser},\ and\ \citenamefont {Wrachtrup}}]{vorobyov2022addressing}%
+%  \BibitemOpen
+%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
+%  {Vorobyov}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Javadzade}},
+%  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Joliffe}}, \bibinfo
+%  {author} {\bibfnamefont {F.}~\bibnamefont {Kaiser}},\ and\ \bibinfo {author}
+%  {\bibfnamefont {J.}~\bibnamefont {Wrachtrup}},\ }\bibfield  {title} {\bibinfo
+%  {title} {Addressing single nuclear spins quantum memories by a central
+%  electron spin},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+%  {Applied Magnetic Resonance}\ }\textbf {\bibinfo {volume} {53}},\ \bibinfo
+%  {pages} {1317} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
+%\bibitem [{\citenamefont {Taminiau}\ \emph {et~al.}(2012)\citenamefont
+%  {Taminiau}, \citenamefont {Wagenaar}, \citenamefont {Van~der Sar},
+%  \citenamefont {Jelezko}, \citenamefont {Dobrovitski},\ and\ \citenamefont
+%  {Hanson}}]{taminiau2012detection}%
+%  \BibitemOpen
+%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+%  {Taminiau}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Wagenaar}},
+%  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Van~der Sar}}, \bibinfo
+%  {author} {\bibfnamefont {F.}~\bibnamefont {Jelezko}}, \bibinfo {author}
+%  {\bibfnamefont {V.~V.}\ \bibnamefont {Dobrovitski}},\ and\ \bibinfo {author}
+%  {\bibfnamefont {R.}~\bibnamefont {Hanson}},\ }\bibfield  {title} {\bibinfo
+%  {title} {Detection and control of individual nuclear spins using a weakly
+%  coupled electron spin},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+%  {journal} {Physical review letters}\ }\textbf {\bibinfo {volume} {109}},\
+%  \bibinfo {pages} {137602} (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
+%\bibitem [{\citenamefont {Zhao}(2014)}]{Zhao:2014aa}%
+%  \BibitemOpen
+%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+%  {Zhao}},\ }\bibfield  {title} {\bibinfo {title} {Dynamical decoupling design
+%  for identifying weakly coupled nuclear spins in a bath},\ }\bibfield
+%  {journal} {\bibinfo  {journal} {Physical Review A}\ }\textbf {\bibinfo
+%  {volume} {90}},\ \href {https://doi.org/10.1103/PhysRevA.90.032319}
+%  {10.1103/PhysRevA.90.032319} (\bibinfo {year} {2014})\BibitemShut {NoStop}%
+%\bibitem [{\citenamefont {Neumann}\ \emph {et~al.}(2010)\citenamefont
+%  {Neumann}, \citenamefont {Beck}, \citenamefont {Steiner}, \citenamefont
+%  {Rempp}, \citenamefont {Fedder}, \citenamefont {Hemmer}, \citenamefont
+%  {Wrachtrup},\ and\ \citenamefont {Jelezko}}]{neumann2010single}%
+%  \BibitemOpen
+%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+%  {Neumann}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Beck}},
+%  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Steiner}}, \bibinfo
+%  {author} {\bibfnamefont {F.}~\bibnamefont {Rempp}}, \bibinfo {author}
+%  {\bibfnamefont {H.}~\bibnamefont {Fedder}}, \bibinfo {author} {\bibfnamefont
+%  {P.~R.}\ \bibnamefont {Hemmer}}, \bibinfo {author} {\bibfnamefont
+%  {J.}~\bibnamefont {Wrachtrup}},\ and\ \bibinfo {author} {\bibfnamefont
+%  {F.}~\bibnamefont {Jelezko}},\ }\bibfield  {title} {\bibinfo {title}
+%  {Single-shot readout of a single nuclear spin},\ }\href@noop {} {\bibfield
+%  {journal} {\bibinfo  {journal} {science}\ }\textbf {\bibinfo {volume}
+%  {329}},\ \bibinfo {pages} {542} (\bibinfo {year} {2010})}\BibitemShut
+%  {NoStop}%
+%\bibitem [{\citenamefont {Bradley}(2019)}]{Bradley:2019aa}%
+%  \BibitemOpen
+%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+%  {Bradley}},\ }\bibfield  {title} {\bibinfo {title} {A ten-qubit solid-state
+%  spin register with quantum memory up to one minute},\ }\bibfield  {journal}
+%  {\bibinfo  {journal} {Physical Review X}\ }\textbf {\bibinfo {volume} {9}},\
+%  \href {https://doi.org/10.1103/PhysRevX.9.031045} {10.1103/PhysRevX.9.031045}
+%  (\bibinfo {year} {2019})\BibitemShut {NoStop}%
+%\bibitem [{\citenamefont {Zaiser}\ \emph {et~al.}(2016)\citenamefont {Zaiser},
+%  \citenamefont {Rendler}, \citenamefont {Jakobi}, \citenamefont {Wolf},
+%  \citenamefont {Lee}, \citenamefont {Wagner}, \citenamefont {Bergholm},
+%  \citenamefont {Schulte-Herbr{\"u}ggen}, \citenamefont {Neumann},\ and\
+%  \citenamefont {Wrachtrup}}]{zaiser2016enhancing}%
+%  \BibitemOpen
+%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+%  {Zaiser}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Rendler}},
+%  \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Jakobi}}, \bibinfo
+%  {author} {\bibfnamefont {T.}~\bibnamefont {Wolf}}, \bibinfo {author}
+%  {\bibfnamefont {S.-Y.}\ \bibnamefont {Lee}}, \bibinfo {author} {\bibfnamefont
+%  {S.}~\bibnamefont {Wagner}}, \bibinfo {author} {\bibfnamefont
+%  {V.}~\bibnamefont {Bergholm}}, \bibinfo {author} {\bibfnamefont
+%  {T.}~\bibnamefont {Schulte-Herbr{\"u}ggen}}, \bibinfo {author} {\bibfnamefont
+%  {P.}~\bibnamefont {Neumann}},\ and\ \bibinfo {author} {\bibfnamefont
+%  {J.}~\bibnamefont {Wrachtrup}},\ }\bibfield  {title} {\bibinfo {title}
+%  {Enhancing quantum sensing sensitivity by a quantum memory},\ }\href@noop {}
+%  {\bibfield  {journal} {\bibinfo  {journal} {Nature communications}\ }\textbf
+%  {\bibinfo {volume} {7}},\ \bibinfo {pages} {12279} (\bibinfo {year}
+%  {2016})}\BibitemShut {NoStop}%
+%\bibitem [{\citenamefont {Kasumaj}\ and\ \citenamefont
+%  {Stoll}(2008)}]{kasumaj20085}%
+%  \BibitemOpen
+%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
+%  {Kasumaj}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+%  {Stoll}},\ }\bibfield  {title} {\bibinfo {title} {5-and 6-pulse electron spin
+%  echo envelope modulation (eseem) of multi-nuclear spin systems},\ }\href@noop
+%  {} {\bibfield  {journal} {\bibinfo  {journal} {Journal of Magnetic
+%  Resonance}\ }\textbf {\bibinfo {volume} {190}},\ \bibinfo {pages} {233}
+%  (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
+%\bibitem [{\citenamefont {Stoll}\ \emph {et~al.}(2005)\citenamefont {Stoll},
+%  \citenamefont {Calle}, \citenamefont {Mitrikas},\ and\ \citenamefont
+%  {Schweiger}}]{stoll2005peak}%
+%  \BibitemOpen
+%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+%  {Stoll}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Calle}},
+%  \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Mitrikas}},\ and\
+%  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Schweiger}},\ }\bibfield
+%  {title} {\bibinfo {title} {Peak suppression in eseem spectra of multinuclear
+%  spin systems},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+%  {Journal of Magnetic Resonance}\ }\textbf {\bibinfo {volume} {177}},\
+%  \bibinfo {pages} {93} (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
+%\bibitem [{\citenamefont {Schweiger}\ and\ \citenamefont
+%  	{Jeschke}(2001)}]{schweiger2001principles}%
+%  \BibitemOpen
+%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+%  		{Schweiger}}\ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+%  		{Jeschke}},\ }\bibfield  {title} {\bibinfo {title} {Principles of pulse electron paramagnetic resonance} }\href@noop
+%  {} {\bibfield  {book} {\bibinfo  {book} {Oxford university press}\ }
+%  	(\bibinfo {year} {2001})}\BibitemShut {NoStop}%
+%\end{thebibliography}%
 

### 2024-06-03 PRB - revision reply/main_revision_bbl.tex
resubmitted

--- 2024-03-27 arxiv/arxiv_main.tex
@@
 \usepackage{hyperref}% add hypertext capabilities
+\usepackage{soul}
 %\usepackage[mathlines]{lineno}% Enable numbering of text and display math
 %\linenumbers\relax % Commence numbering lines
-\newcommand{\vvv}[1]{\textcolor{blue}{#1}}
+\newcommand{\vvv}[1]{\textcolor{black}{#1}}
+\newcommand{\kb}[2]{\vert #1 \rangle \langle #2 \vert}
+\newcommand{\caver}[1]{\overline{#1}}
+\setlength{\jot}{8pt}
+%\newcommand{\abs}[1]{\vert #1 \vert}
+\let\oldsubref\subref
+%\renewcommand{\subref}[1]{(\oldsubref{#1})}
+\renewcommand{\vec}[1]{\overrightarrow{#1}}
+\newcommand{\tq}[1]{\textquote{#1}}
 %\usepackage[showframe,%Uncomment any one of the following lines to test 
@@
 These two spin sublevels are separated due to the Zeeman effect and/or zero-field splitting, forming a two-level subsystem with an energy splitting of $\omega_a$.
-The Hamiltonian of the system in the secular approximation and in the rotating frame of the applied microwave $\omega_{mw}$ can be written as:
+The Hamiltonian of the system in the secular approximation and in the rotating frame of the applied microwave $\omega_{mw}$ can be written as \textcolor{black}{(derivation in \ref{app:Hamiltonian})}:
 \begin{align}
@@
 	(\vec{n_0}\cdot \vec{n_1})\sin(\frac{\omega_0 \tau}{2}) \sin(\frac{\omega_1 \tau}{2}) \Big]^{(j)}
-	\textcolor{gray}{e^{-(\frac{\tau}{T_2^\ast})^m}}
+	%\textcolor{gray}{e^{-(\frac{\tau}{T_2^\ast})^m}}
 \end{gather}	
-The exponential decay is introduced to note the Ramsey signal decays with the electron spin $T_2^\ast$ since the formalism does not account for any relaxation processes.
-The Ramsey sequence is sensitive to detuning since the electron spin is not refocused; however, it is possible to sense nuclear spins with vanishing perpendicular hyperfine coupling.\\
+%\st{The exponential decay is introduced to note the Ramsey signal decays with the electron spin $T_2^\ast$ since the formalism does not account for any relaxation processes.} 
+ \textcolor{black}{We note the expressions do not account for any relaxation processes.} The Ramsey sequence is sensitive to detuning since the electron spin is not refocused \textcolor{black}{and it decays with the electron spin $T_2^\ast$}; however, it is possible to sense nuclear spins with vanishing perpendicular hyperfine coupling.\\
 
@@
 \end{gather}
-Where $\vec{n}_0 \cdot \vec{n}_1 = \frac{\omega_L^2+(s_0+s_1)A_{zz}+s_0 s_1 (A_{zz}^2+A_{zx}^2)}{\omega_0 \omega_1}$.
+Where $\vec{n}_0 \cdot \vec{n}_1 = \frac{\omega_L^2+(s_0+s_1)A_{zz}+s_0 s_1 (A_{zz}^2+A_{zx}^2)}{\omega_0 \omega_1}$, \textcolor{black}{which is the inner product of precession axes of a nuclear spin condition on the electron spin sublevel.
+This expression indicates the advantage of using DD sequence for sublevels where either $s_0$ or $s_1$ is zero, only first order parallel hyperfine coupling $\frac{A_{zz}}{\omega_L}$ play a role.
+On the other hand, in spin-1/2 systems ($s_0=-\frac{1}{2}$ and $s_1=\frac{1}{2}$), the first order perturbation correction with respect to hyperfine coupling vanishes and only second order perturbation term with respect to parallel $(\frac{A_{zz}}{\omega_L})^2$  and perpendicular coupling $(\frac{A_{zx}}{\omega_L})^2$ remain present.
+This indicates weak sensitivity of DD sequence on different nuclear spins}.
 At this point, it should be clear that the number of pulses can be used as an additional parameter to modify the modulation depth of each nuclear spin.
@@
 $\tau$ is set to the Larmor bright spot.
-Simulated Fisher information for the case of the electron spin c.
+Simulated  \textcolor{black}{5pESEEM} Fisher Information 56 by 56 matrix for the case of the electron spin c.
 $S=1$ d.
 $S=1/2$ system.
-The first 23 hyperfine parameters are $A_{zz}$ and the second 23 parameters are $A_{zx}$ of the nuclear spin register.}
+The first 23 hyperfine parameters are $A_{zz}$ and the second 23 parameters are $A_{zx}$ of the nuclear spin register.
+\textcolor{black}{It indicates the covariance between two parameters.
+The main diagonal appears as each parameter is correlated with itself.
+The side-diagonals indicate the two hyperfine parameters that belong to the same nuclei.}}
 		\label{fig:ddeseem}
@@
 In this work, we consider the 23-nuclear spin cluster characterized previously \cite{abobeih2019atomic} as a realistic case for our comparison.
-First, we apply this to the dynamical decoupling sequence and visualize the obtained results.
+\textcolor{black}{Each nuclear spin is identified with two hyperfine parameters $A_{zz}$ and $A_{zx}$, which shows coupling to the central electron spin.
+Hence, characterizing this 23-nuclear spins requires identifying 56 hyperfine coupling parameters.}
+First, we apply the Dynamical Decoupling (DD) sequence to this nuclear spin register and visualize the obtained results.
 Fig \ref{fig:3} compares the DD signal for the same nuclear spin register but different defects in diamond.
@@
 \end{equation}
+\textcolor{black}{the summation is over $\tau$, the pulse timing used in the sequence, and $A$ is the array including all hyperfine coupling parameters.
+For the considered nuclear spin register, $A$ includes 56 hyperfine coupling parameters, the first 23 parameters are $A_{zz}$ of different nuclear spins and the second 23 parameters are $A_{zx}$ respectively, resulting in the Fisher information as a 56 by 56 Matrix.
+Fig.
+\ref{fig:3}c,d visualize Fisher Information matrix element for DD sequence in spin 1 and 1/2 systems.}
 For the typical case of an NV center with $S=1$, since all the nuclear spin resonances are clearly resolved, the Fisher Information Matrix takes a diagonal shape, revealing low covariances between the various nuclear spin resonances.
@@
 
+\section{Hamiltonian}
+\label{app:Hamiltonian}
+The spin Hamiltonian for many color centers can be written as\cite{Schweiger2001Principles}:
+\begin{gather}
+	H = \mathbf{D}^\intercal \mathbf{S} \mathbf{D} + \beta_e \mathbf{B}^\intercal \mathbf{g} \mathbf{S} + \beta_n \sum_{k=1}^m g_n^{(k)}  \mathbf{B}^\intercal \mathbf{I}^{(k)} \notag \\
+	+ \sum_{I_k>1/2} (\mathbf{I}^{\intercal} \mathbf{P} \mathbf{I})^{(k)} + \sum_{k=1}^m g_n^{(k)} (\mathbf{S}^\intercal \mathbf{A} \mathbf{I})^{(k)}
+\end{gather}
+Where $\mathbf{S}$ and $\mathbf{I}^{(k)}$ are electron and nuclear spin vector operators, $\mathbf{D}$ is zero field splitting tensor, $\mathbf{B}$ is magnetic field vector, $\mathbf{P}$ is nuclear quadrupole tensor, $\mathbf{A}$ is the hyperfine interaction tensor, $\beta_e = \frac{e \hbar}{2m_e}$ and $\beta_n = \frac{-e \hbar}{2m_n}$ are electron and nuclear Bohr magneton.
+Here, we neglected  nuclear-nuclear interactions.
+Also, due to axial symmetry, the zero field splitting can be simplified.
+We assume the magnetic field is only along the symmetry axis, which we denote as z direction.
+Moreover, the secular terms ($S_zI_x, S_zI_y, S_zI_z$) are just a shift of the energy level that are relevant up to first order, while the non-secular terms ($S_xI_x, S_yI_x, S_zI_z, S_xI_y, S_yI_y, S_zI_y$) mix the electron spin levels, which are largely detuned due to the large zero field splitting.
+Hence, the non-secular terms of Hamiltonian are neglected.
+Furthermore, for each nuclear spin, one can go to the xy frame such that $A_{zy}$ term is zero.
+All in all, the spin Hamiltonian with mentioned considerations can be simplified to:
+\begin{gather}
+	H = D_z S_z^2 + \gamma_e B S_z + \gamma_n B I_z^{(k)} + P_z^{(k)} I_z^{2(k)} \notag \\
+	+ A_{zz}^{(k)} S_z I_z^{(k)} + A_{zx}^{(k)} S_z I_x^{(k)}
+\end{gather}
+The summation over k is omitted due to convenience!
+The coefficient $\gamma_e$ and $\gamma_n$ are electron and nuclear gyromagnetic ratios.
+The coefficients' values for the case of NV center in diamond are $D_z= 2.87$ GHz, $\gamma_e= -2.802$ MHz/G, $\gamma_n^{(^{13}C)}= 1.07$ kHz/G, $\gamma_n^{(^{14}N)}= 0.31$ kHz/G, $P_z^{(^{14}N)}= -5.04$ MHz.
+\\
+
+The electron spin in general can take any value, however resonant microwave pulses are applied only for two of the sublevels.
+Hence, the electron spin is effectively a two-level system.
+The electron spin occupies two of its sublevels that are denoted as $\ket{0} = \ket{m_s=s_0}$ and $\ket{1} = \ket{m_s=s_1}$; in other words:
+\begin{gather}
+	S_z= \begin{pmatrix} s_1 & 0 \\ 0 & s_0\end{pmatrix}
+\end{gather}
+One can show that $S_z^2 = (s_1+s_0)S_z-s_1s_0 \mathds{1}$. 
+We define the transition frequency between two spin sub-levels of the electron spin as $\omega_a = D_z (s_1+s_0)+\gamma_e B $.
+Moreover, we note that since we consider nuclei with spin of one half in the system, the nuclear quadrupole term vanishes.
+The Hamiltonian can be written in terms of Pauli matrices:
+\begin{align}
+	H =\omega_aS_z+ \gamma_n B I_z^{(k)} + A_{zz}^{(k)} S_z I_z^{(k)} + A_{zx}^{(k)} S_z I_x^{(k)}
+\end{align}
+
+The Hamiltonian presented so far does not include the microwave drive field.
+Indeed, the microwave pulses are assumed to be instantaneous, but considering the drive field, the Hamiltonian  should be written in the rotating frame and assume rotating wave approximation.
+This frame should be respected for the rest of sequence.
+Since the rotating frame unitary operator commutes with the $\sigma_z$, the expectation value of this operator in the rotating frame is the same as in the lab frame.
+Eventually, free evolution Hamiltonian in the rotating frame is written as follows:
+\begin{align}
+	H = \Delta S_z + \sum_k (\omega_L^{(k)}  + A_{zz}^{(k)} S_z) I_z^{(k)} + A_{zx}^{(k)} S_z I_x^{(k)}
+\end{align}
+Where $\Delta = \omega_a - \omega_{mw}$ is the detuning.
+
 \section{5pESEEM formula}
@@
 
-The blind spot term shows that how this sequence can be engineered to increase or reduce the signal amplitude of one nuclear spin from the spectrum.
-The bright and blind spots of a frequency in the spectrum are as follows:
+The blind spot term, B, shows that how this sequence can be engineered to increase or reduce the signal amplitude of one nuclear spin from the spectrum. 
+%\st{The bright and blind spots of a frequency in the spectrum are as follows} 
+\textcolor{black}{The Eq. \ref{eq:BS} suggests the bright and blind spots of a frequency can be obtained as follows}:
 \begin{align}
@@
 \end{align}
-The blind spots does not depend only on one frequency but on the nuclear spin.
+%\st{The blind spots does not depend only on one frequency but on the nuclear spin.
 It means if one resonant frequency is blinded, the other resonant frequency and all the multiple quantum resonances also vanishes.
@@
 Also, This is very helpful especially in the presence of strongly coupled nuclear spin that suppress other nuclei.
-By sweeping $\tau_1$ and $\tau_2$, one can go through different bright and blind spots of each nuclear spin, observe which two peaks are correlated.
+By sweeping $\tau_1$ and $\tau_2$, one can go through different bright and blind spots of each nuclear spin, observe which two peaks are correlated.}
+
+\textcolor{black}{The blind spot term depends on both $\tau_1$ and $\tau_2$.
+It means if one resonant frequency is blinded, the other resonant frequency and all the multiple quantum resonances also vanishes.
+This can be used as a manifestation that which two peaks in the frequency spectrum are originating from the same nuclei.
+In other words, choosing $\tau$ such that a particular resonant frequency in the spectrum is blinded, the other resonant frequency of the same nuclear spin will also be blinded and both of them disappear from the frequency spectrum together.
+Moreover, this is very helpful especially in the presence of strongly coupled nuclear spin that suppress other nuclei.
+By sweeping $\tau_1$ and $\tau_2$, one can go through different bright and blind spots of each nuclear spin, and observe correlations between different peaks.}
 
@@
 %pass
-%\bibliography{references}% Produces the bibliography via BibTeX.
+%\bibliography{references_review}% Produces the bibliography via BibTeX.
+%apsrev4-2.bst 2019-01-14 (MD) hand-edited version of apsrev4-1.bst
+%Control: key (0)
+%Control: author (8) initials jnrlst
+%Control: editor formatted (1) identically to author
+%Control: production of article title (0) allowed
+%Control: page (0) single
+%Control: year (1) truncated
+%Control: production of eprint (0) enabled
 \begin{thebibliography}{24}%
@@
   \bibinfo {author} {\bibfnamefont {M.~H.}\ \bibnamefont {Abobeih}}, \bibinfo
-  {author} {\bibfnamefont {R.}~\bibnamefont {Berrevoets}}, \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Degen}}, \bibinfo {author} {\bibfnamefont
-  {M.~A.}\ \bibnamefont {Bakker}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Markham}}, \bibinfo {author} {\bibfnamefont
-  {D.}~\bibnamefont {Twitchen}},\ and\ \bibinfo {author} {\bibfnamefont
+  {author} {\bibfnamefont {R.~C.}\ \bibnamefont {Berrevoets}}, \bibinfo
+  {author} {\bibfnamefont {M.~J.}\ \bibnamefont {Degen}}, \bibinfo {author}
+  {\bibfnamefont {M.~A.}\ \bibnamefont {Bakker}}, \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Markham}}, \bibinfo {author} {\bibfnamefont
+  {D.~J.}\ \bibnamefont {Twitchen}},\ and\ \bibinfo {author} {\bibfnamefont
   {T.~H.}\ \bibnamefont {Taminiau}},\ }\bibfield  {title} {\bibinfo {title} {A
@@
   {2021})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Hesselmeier}\ \emph {et~al.}(2023)\citenamefont
-  {Hesselmeier}, \citenamefont {Kuna}, \citenamefont {Tak{\'a}cs},
-  \citenamefont {Iv{\'a}dy}, \citenamefont {Knolle}, \citenamefont {Ghezellou},
-  \citenamefont {Ul-Hassan}, \citenamefont {Dasari}, \citenamefont {Kaiser},
-  \citenamefont {Vorobyov} \emph {et~al.}}]{hesselmeier2023measuring}%
+\bibitem [{\citenamefont {Hesselmeier}\ \emph
+  {et~al.}(2024{\natexlab{a}})\citenamefont {Hesselmeier}, \citenamefont
+  {Kuna}, \citenamefont {Tak{\'a}cs}, \citenamefont {Iv{\'a}dy}, \citenamefont
+  {Knolle}, \citenamefont {Son}, \citenamefont {Ghezellou}, \citenamefont
+  {Ul-Hassan}, \citenamefont {Dasari}, \citenamefont {Kaiser} \emph
+  {et~al.}}]{hesselmeier2024qudit}%
   \BibitemOpen
@@
   {\bibfnamefont {W.}~\bibnamefont {Knolle}}, \bibinfo {author} {\bibfnamefont
+  {N.~T.}\ \bibnamefont {Son}}, \bibinfo {author} {\bibfnamefont
   {M.}~\bibnamefont {Ghezellou}}, \bibinfo {author} {\bibfnamefont
@@
   {D.}~\bibnamefont {Dasari}}, \bibinfo {author} {\bibfnamefont
-  {F.}~\bibnamefont {Kaiser}}, \bibinfo {author} {\bibfnamefont
-  {V.}~\bibnamefont {Vorobyov}}, \emph {et~al.},\ }\bibfield  {title} {\bibinfo
-  {title} {Measuring nuclear spin qubits by qudit-enhanced spectroscopy in
-  silicon carbide},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {arXiv preprint arXiv:2310.15557}\ } (\bibinfo {year} {2023})}\BibitemShut
+  {F.}~\bibnamefont {Kaiser}}, \emph {et~al.},\ }\bibfield  {title} {\bibinfo
+  {title} {Qudit-based spectroscopy for measurement and control of nuclear-spin
+  qubits in silicon carbide},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+  {journal} {Physical Review Letters}\ }\textbf {\bibinfo {volume} {132}},\
+  \bibinfo {pages} {090601} (\bibinfo {year} {2024}{\natexlab{a}})}\BibitemShut
   {NoStop}%
-\bibitem [{\citenamefont {Hesselmeier}\ \emph {et~al.}(2024)\citenamefont
-  {Hesselmeier}, \citenamefont {Kuna}, \citenamefont {Knolle}, \citenamefont
-  {Kaiser}, \citenamefont {Son}, \citenamefont {Ghezellou}, \citenamefont
-  {Ul-Hassan}, \citenamefont {Vorobyov},\ and\ \citenamefont
-  {Wrachtrup}}]{hesselmeier2024high}%
+\bibitem [{\citenamefont {Hesselmeier}\ \emph
+  {et~al.}(2024{\natexlab{b}})\citenamefont {Hesselmeier}, \citenamefont
+  {Kuna}, \citenamefont {Knolle}, \citenamefont {Kaiser}, \citenamefont {Son},
+  \citenamefont {Ghezellou}, \citenamefont {Ul-Hassan}, \citenamefont
+  {Vorobyov},\ and\ \citenamefont {Wrachtrup}}]{hesselmeier2024high}%
   \BibitemOpen
@@
   {V.}~\bibnamefont {Vorobyov}},\ and\ \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {Wrachtrup}},\ }\bibfield  {title} {\bibinfo {title} {High
-  fidelity optical readout of a nuclear spin qubit in silicon carbide},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {arXiv preprint
-  arXiv:2401.04465}\ } (\bibinfo {year} {2024})}\BibitemShut {NoStop}%
+  {J.}~\bibnamefont {Wrachtrup}},\ }\bibfield  {title} {\bibinfo {title}
+  {High-fidelity optical readout of a nuclear-spin qubit in silicon carbide},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
+  Letters}\ }\textbf {\bibinfo {volume} {132}},\ \bibinfo {pages} {180804}
+  (\bibinfo {year} {2024}{\natexlab{b}})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Reiner}\ \emph {et~al.}(2024)\citenamefont {Reiner},
@@
   {2019})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {van~de Stolpe}\ \emph {et~al.}(2023)\citenamefont
-  {van~de Stolpe}, \citenamefont {Kwiatkowski}, \citenamefont {Bradley},
-  \citenamefont {Randall}, \citenamefont {Breitweiser}, \citenamefont
-  {Bassett}, \citenamefont {Markham}, \citenamefont {Twitchen},\ and\
-  \citenamefont {Taminiau}}]{van2023mapping}%
+\bibitem [{\citenamefont {Van~de Stolpe}\ \emph {et~al.}(2024)\citenamefont
+  {Van~de Stolpe}, \citenamefont {Kwiatkowski}, \citenamefont {Bradley},
+  \citenamefont {Randall}, \citenamefont {Abobeih}, \citenamefont
+  {Breitweiser}, \citenamefont {Bassett}, \citenamefont {Markham},
+  \citenamefont {Twitchen},\ and\ \citenamefont {Taminiau}}]{van2024mapping}%
   \BibitemOpen
   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-  {van~de Stolpe}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Van~de Stolpe}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
   {Kwiatkowski}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
   {Bradley}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Randall}},
-  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Breitweiser}}, \bibinfo
-  {author} {\bibfnamefont {L.}~\bibnamefont {Bassett}}, \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Markham}}, \bibinfo {author} {\bibfnamefont
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Abobeih}}, \bibinfo
+  {author} {\bibfnamefont {S.}~\bibnamefont {Breitweiser}}, \bibinfo {author}
+  {\bibfnamefont {L.}~\bibnamefont {Bassett}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Markham}}, \bibinfo {author} {\bibfnamefont
   {D.}~\bibnamefont {Twitchen}},\ and\ \bibinfo {author} {\bibfnamefont
@@
   {Mapping a 50-spin-qubit network through correlated sensing},\ }\href@noop {}
-  {\bibfield  {journal} {\bibinfo  {journal} {arXiv preprint arXiv:2307.06939}\
-  } (\bibinfo {year} {2023})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Dr{\'e}au}(2012)}]{Dreau:2012aa}%
+  {\bibfield  {journal} {\bibinfo  {journal} {Nature Communications}\ }\textbf
+  {\bibinfo {volume} {15}},\ \bibinfo {pages} {2006} (\bibinfo {year}
+  {2024})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Dr{\'e}au}\ \emph {et~al.}(2012)\citenamefont
+  {Dr{\'e}au}, \citenamefont {Maze}, \citenamefont {Lesik}, \citenamefont
+  {Roch},\ and\ \citenamefont {Jacques}}]{dreau2012high}%
   \BibitemOpen
   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Dr{\'e}au}},\ }\bibfield  {title} {\bibinfo {title} {High-resolution
-  spectroscopy of single nv defects coupled with nearby $^{13}$c nuclear spins
-  in diamond},\ }\bibfield  {journal} {\bibinfo  {journal} {Physical Review B}\
-  }\textbf {\bibinfo {volume} {85}},\ \href
-  {https://doi.org/10.1103/PhysRevB.85.134107} {10.1103/PhysRevB.85.134107}
-  (\bibinfo {year} {2012})\BibitemShut {NoStop}%
+  {Dr{\'e}au}}, \bibinfo {author} {\bibfnamefont {J.-R.}\ \bibnamefont {Maze}},
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Lesik}}, \bibinfo
+  {author} {\bibfnamefont {J.-F.}\ \bibnamefont {Roch}},\ and\ \bibinfo
+  {author} {\bibfnamefont {V.}~\bibnamefont {Jacques}},\ }\bibfield  {title}
+  {\bibinfo {title} {High-resolution spectroscopy of single nv defects coupled
+  with nearby 13 c nuclear spins in diamond},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Physical Review B}\ }\textbf {\bibinfo
+  {volume} {85}},\ \bibinfo {pages} {134107} (\bibinfo {year}
+  {2012})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Childress}\ \emph {et~al.}(2006)\citenamefont
@@
   {\bibfnamefont {C.~A.}\ \bibnamefont {Meriles}},\ }\bibfield  {title}
-  {\bibinfo {title} {High-resolution correlation spectroscopy of 13c spins near
-  a nitrogen-vacancy centre in diamond},\ }\href@noop {} {\bibfield  {journal}
-  {\bibinfo  {journal} {Nature communications}\ }\textbf {\bibinfo {volume}
-  {4}},\ \bibinfo {pages} {1651} (\bibinfo {year} {2013})}\BibitemShut
+  {\bibinfo {title} {High-resolution correlation spectroscopy of 13{C} spins
+  near a nitrogen-vacancy centre in diamond},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Nature communications}\ }\textbf {\bibinfo
+  {volume} {4}},\ \bibinfo {pages} {1651} (\bibinfo {year} {2013})}\BibitemShut
   {NoStop}%
@@
   \bibinfo {pages} {137602} (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Zhao}(2014)}]{Zhao:2014aa}%
+\bibitem [{\citenamefont {Zhao}\ \emph {et~al.}(2014)\citenamefont {Zhao},
+  \citenamefont {Wrachtrup},\ and\ \citenamefont {Liu}}]{zhao2014dynamical}%
   \BibitemOpen
   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-  {Zhao}},\ }\bibfield  {title} {\bibinfo {title} {Dynamical decoupling design
-  for identifying weakly coupled nuclear spins in a bath},\ }\bibfield
-  {journal} {\bibinfo  {journal} {Physical Review A}\ }\textbf {\bibinfo
-  {volume} {90}},\ \href {https://doi.org/10.1103/PhysRevA.90.032319}
-  {10.1103/PhysRevA.90.032319} (\bibinfo {year} {2014})\BibitemShut {NoStop}%
+  {Zhao}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Wrachtrup}},\
+  and\ \bibinfo {author} {\bibfnamefont {R.-B.}\ \bibnamefont {Liu}},\
+  }\bibfield  {title} {\bibinfo {title} {Dynamical decoupling design for
+  identifying weakly coupled nuclear spins in a bath},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Physical Review A}\ }\textbf
+  {\bibinfo {volume} {90}},\ \bibinfo {pages} {032319} (\bibinfo {year}
+  {2014})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Neumann}\ \emph {et~al.}(2010)\citenamefont
@@
   {NoStop}%
-\bibitem [{\citenamefont {Bradley}(2019)}]{Bradley:2019aa}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
-  {Bradley}},\ }\bibfield  {title} {\bibinfo {title} {A ten-qubit solid-state
-  spin register with quantum memory up to one minute},\ }\bibfield  {journal}
-  {\bibinfo  {journal} {Physical Review X}\ }\textbf {\bibinfo {volume} {9}},\
-  \href {https://doi.org/10.1103/PhysRevX.9.031045} {10.1103/PhysRevX.9.031045}
-  (\bibinfo {year} {2019})\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Zaiser}\ \emph {et~al.}(2016)\citenamefont {Zaiser},
@@
   (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Schweiger}\ and\ \citenamefont
+  {Jeschke}(2001)}]{Schweiger2001Principles}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Schweiger}}\ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Jeschke}},\ }\href@noop {} {\emph {\bibinfo {title} {Principles of pulse
+  electron paramagnetic resonance}}}\ (\bibinfo  {publisher} {Oxford University
+  Press},\ \bibinfo {year} {2001})\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Stoll}\ \emph {et~al.}(2005)\citenamefont {Stoll},
@@
 
-% The \nocite command causes all entries in a bibliography to be printed out
-% whether or not they are actually referenced in the text. This is appropriate
-% for the sample file to show the different styles of references, but authors
-% most likely will not want to use it.
-%\nocite{*}
 \end{document}
